### 2024-02-21 paper/main.tex
merging paper to the main repo

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{deps/usenix-2020-09}

% The preceding line is only needed to identify funding in the first footnote.
% If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%-------------------------------------------------------------------------------
% INCLUDES
%-------------------------------------------------------------------------------

\input{deps/pkgs}    % all additional packages.
\input{deps/macros}  % all macro definitions.

%-------------------------------------------------------------------------------
% FINE-TUNING 
%-------------------------------------------------------------------------------

%\floatsetup[table]{capposition=top}

%save space with section spacing
%\usepackage{titlesec}
%\titlespacing*{\section}{0pt}{8pt}{8pt}
%\titlespacing*{\subsection}{0pt}{7pt}{7pt}

%\renewcommand\floatpagefraction{.9}
%\renewcommand\topfraction{.9}
%\renewcommand\bottomfraction{.9}
%\renewcommand\textfraction{.1}   
%\setcounter{totalnumber}{50}
%\setcounter{topnumber}{50}
%\setcounter{bottomnumber}{50}

%-------------------------------------------------------------------------------
% START OF DOCUMENT
%-------------------------------------------------------------------------------

\begin{document}

\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\title{A Comparative Quality Metric for Fuzzing with Logic State Coverage}
\author{
  {\rm Gwangmu Lee} \\ {EPFL}
}

% NOTE: for page numbering. will be removed at submission.
\thispagestyle{plain}
\pagestyle{plain}

\maketitle

%-------------------------------------------------------------------------------
% ABSTRACT
%-------------------------------------------------------------------------------

\begin{abstract}

  While fuzzing is widely accepted as an efficient program testing technique, it
  is still unclear how to measure the \emph{comparative quality} of different
  fuzzers. The current de facto quality metrics are edge coverage and the
  number of discovered bugs, but they are frequently discredited by
  inconclusive, exaggerated, or even counter-intuitive results.

  To establish a more reliable quality metric, we first note that fuzzing 
  aims to reduce the number of unknown \emph{abnormal} behaviors by observing
  more \emph{interesting} (i.e., relating to unknown abnormal) behaviors. This
  suggests that the number of observed interesting behaviors should directly
  indicate how well the fuzzer achieved its aim (i.e., the quality).

  In this work, we propose \emph{logic state coverage} as a proxy metric to
  count observed interesting behaviors. A logic state distinguishes interesting
  behaviors in a finer granularity than the less interesting ones, making the
  amount of logic state coverage (i.e., observed logic states) directly
  proportional to the number of observed interesting behaviors.

  We implemented logic state coverage using a bloom filter and reevaluated
  \textsc{FuzzBench} and indecisive-to-subjective fuzzer comparisons in
  hypervisor and grammar fuzzing. 
  % TODO: (The result summary will come here)

\end{abstract}

\section{Introduction}
%
% current practice: two metrics: # of found bugs & edge coverage.
%  - # of found bugs: direct metric, but too few to compare. depends on versions and SW quality.
%  - edge cov: popular proxy metric, but weak correlation to # of found bugs.
%    - e.g., same max coverage, marginal difference, seed influence.

% subject: fuzzing
%  - effective dynamic software testing method
Since AFL \cite{afl} gained popularity, fuzzing has been widely regarded as
one of the most effective software testing methods.
%
The most basic form is \emph{untargeted} fuzzing, which investigates a whole
program by executing randomly mutated inputs indefinitely without any target
code.
%
It has shown promising effectiveness on simple software despite its simplicity,  
motivating researchers to further improve it by incorporating various
techniques
\cite{liu2023dsfuzz,deng2023nestfuzz,zheng2023fishfuzz,wu2022strategy,aschermann2019redqueen,rawat2017vuzzer,fioraldi2020aflpp}
and applying it to complex software, such as hypervisors
\cite{liu2023videzzo,myung2022mundofuzz,sergej2021nyx,schumilo2020hypercube} and
language interpreters
\cite{wang2023fuzzjit,wu2023jitfuzz,gross2023fuzzilli,srivastava2021gramatron,chen2021polyglot}.\footnote{In
this paper, we call  \emph{untargeted} fuzzing simply fuzzing if not specified.}

% problem raising: evaluating fuzzing
%  - edge coverage has been subject to many debates.
%    - agreed: weak indicator of program-testing capability
%    - shortcoming: hard-to-judge moments (e.g., not-so-big difference)
%    - shortcoming: counter-intuitive situations (e.g., AI fuzzing - large edge cov, smaller bug discovery)
Meanwhile, there have been ever-existing debates on measuring the
\emph{comparative quality} of fuzzing as more research has been done
\cite{wang2020notallcov,wang2019impactcov,bohme2022reliability,klees2018eval,li2021unifuzz}.
While some researchers proposed alternative ways to measure quality
\cite{bohme2021residual,bohme2022reliability,li2021unifuzz}, the
current de facto standard quality metrics are \emph{edge coverage} (i.e., how
many control-flow edges were triggered) and \emph{the number of discovered bugs}
(i.e., how many bugs were discovered). Generally, either larger edge coverage or
more discovered bugs is deemed as a positive indicator of the fuzzing quality.

However, both metrics have been consistently refuted as unreliable. Edge
coverage has long been discredited as a \emph{weak} proxy metric as it
often leads to indecisive measurements; it is common to see the edge coverage
comparisons offering little difference (e.g., equally saturated edge coverage in
hypervisor virtual devices \cite{myung2022mundofuzz,sergej2021nyx}) or
influenced by initial inputs (e.g., different requirements for initial inputs in
grammar fuzzing \cite{chen2021polyglot}).
%, in which cases researchers should resort to another way for demonstrating effectiveness.  
Furthermore, some experiments yield counter-intuitive results where a code
coverage increment does not necessarily translate to more discovered bugs so
well \cite{google-ai}.

The number of discovered bugs, on the other hand, is a direct metric as it
counts the very objects (i.e., bugs) that fuzzing aims to reveal. However, it is
commonly known to be heavily sensitive to side factors such as bug
deduplication, initial inputs, and the implementation details of both the fuzzer
and the software under test \cite{klees2018evaluating}. It gets worse because
the number of total bugs is usually only a handful,
%regardless of the software under test, 
where unclear factors can introduce a measurement bias that significantly
exaggerates the result in certain software.

% clarification: fuzzing as software testing method
%  - "testing": minimize unknown abnormal behaviors.
%  - in line with that, approach of "untargeted fuzzing": observing many
%    interesting (i.e., likely-abnormal) behaviors to minimize them.
%  - rationale: more observation of interesting prog behavior -> less unknown
%    abnormal behavior expected.
In pursuit of a more reliable quality metric for fuzzing, we first note that the
goal of fuzzing, from the software testing perspective, is \emph{minimizing
unknown abnormal program behaviors} (i.e., bugs). Fuzzing approaches this goal
by observing as many \emph{interesting} program behaviors as possible that 
likely reveal abnormal behaviors; the more such behaviors it checks, the fewer
unknown abnormal behaviors are expected to be left.
%
% proposal: logic state coverage
%  - following the rationale of untargeted fuzzing,
%  - the metric to measure such a rationale, hence more directly measuring the
%    quality of untargeted fuzzing as a software testing method.
%  - what is it: define logic state => set of satisfied branches,
%    inversely-weighted by hit counts.
%  - what it is: define logic state coverage => covered logic state during fuzzing
%  - why to use: (we argue that) the number of covered logic states (hence
%    coverage) captures covered interesting behaviors.
%    - meaning more cov ==> less expected unknown abnormal behaviors.
This rationale suggests that \emph{comparing the number of observed interesting
program behaviors between fuzzers} must indicate its \emph{comparative
quality}, as a larger number offers a greater guarantee of fewer unknown
abnormal behaviors. 
%We argue that this should be a \emph{stronger quality metric}.

As it is challenging to directly count interesting program behaviors when
fuzzing produces hundreds of them every second, we propose \emph{logic state
coverage} as a feasible proxy metric of interesting behaviors. A logic state is
a set of all satisfied branches during one execution, bucketed by their hit
counts (larger buckets for higher hit counts). Logic state coverage then
\emph{individually counts} all observed distinct logic states.  One logic state
represents \emph{fewer} program behaviors if they are \emph{more interesting}
(i.e., likely relating to unknown abnormal behaviors), meaning that observing
more interesting behaviors is strongly reflected on larger logic state coverage.

% design: edge bitmap rehashing
%  - idea
%    - i) generate a hash of the entire edge bitmap (=logic state).
%    - ii) put it to a bloom filter large enough to reasonably avoid hash
%      collisions throughout a long fuzzing campaign.
%    - iii) periodically calculate the number of distinct hashes (=logic states)
% TODO

% evaluation
%  - i) FuzzBench
%  - ii) grammar fuzzing
%  - iii) hypervisor fuzzing
%  - summary
% TODO

\section{Formalizing Fuzzing}

In this section, we formalize the fuzzing procedure to derive a strong quality
metric. We first start with defining a program
behavior (\autoref{s:fuzz:behave}) and, based on the definition, formalize the
procedure of untargeted fuzzing (\autoref{s:fuzz:unfuzz}).

\pp{Notation and assumption}
%
We denote a set and its element in bold and lowercase, respectively.  For
example, $\mathbb{I}$ and $\mathbb{O}$ denote a set of all inputs and outputs
respectively, where $i$ and $o$ are the element of each set (i.e., an input and
an output). If not specified, all arguments assume single-thread programs.

\subsection{Program Behavior}
\label{s:fuzz:behave}

% definition
%  - the space that comprises all combinations of logical outcomes from conditionals (e.g., if).
%  - equivalent to the terminal symbolic program states in symbex.
%  - example with a toy program.

A program $p$ is a map that cast an input $i$ to an observable output $o$ and
a \emph{program behavior} $h$, which can be defined as a stream of executed
instructions. Formally, if $\mathbb{H}$ is a \emph{program behavior space}, 
a set of all possible program behaviors,
%
\begin{equation}
  p(i) = (o, h) \iff p: \mathbb{I} \rightarrow \mathbb{O} \times \mathbb{H}.
\end{equation}

%\pp{Normality of program behaviors}
%
Program behaviors can be divided into two classes depending on their
\emph{normality}: normal and abnormal. Normal program behaviors are determined
by a regular control flow and terminate at program exit points.  Abnormal
program behaviors, on the other hand, are terminated unexpectedly by
exceptions.\footnote{Sanitization can be seen as bringing (potentially) silent
\emph{unintended} behaviors (e.g., integer-overflow or use-after-free) to the
\emph{abnormal} territory.}

\pp{Special case: single-thread programs}
%
For a single-thread program where every basic block always executes the
contained instructions atomically, program behaviors are exclusively
determined by the history of two kinds of conditions: branch and exceptional.
Branch conditions (or \emph{branches}) decide the regular control flow between
basic blocks. Exceptional conditions (or \emph{exceptions}), on the other hand,
interrupt the control flow and abnormally terminate the
program.\footnote{C++-style exceptions, despite its name, can be regarded as a
form of branch conditions as they transfer the control flow to another basic
block.} Notice that exceptions may be implicit and not specified in the
program (e.g., $\mathrm{divisor}=0$ in divide-by-zero).

%Notice that exceptions may be implicit, unlike branches that are always explicit
%in the program; exceptions such as assertions are explicitly specified in
%the program, but others such as divide-by-zero (i.e., $\mathrm{divisor}=0$) or
%buffer-overflow (i.e., $\mathrm{offset} \ge \mathrm{size}$) are implicit and
%only enforced by the system.

Formally, let $\mathcal{T}_b$ and $\mathcal{T}_e$ be the history of branches and
exceptions. Then, for a single-thread program, there exists a function
$f(\mathcal{T}_b, \mathcal{T}_e) = h$ that one-to-one maps a pair
$(\mathcal{T}_b, \mathcal{T}_e)$ to a certain program behavior $h$.
%
%\begin{equation}
%  f(\mathcal{T}_b, \mathcal{T}_e) = h \iff f: \mathbb{T}_b \times \mathbb{T}_e \rightarrow \mathbb{H}.
%\end{equation}

% (s, o) ==> (\mathcal{T}_e, \mathcal{T}_i). \mathcal{T}_i containing all s-altering or o-altering conds.
%  - including semantic errors (i.e., error in the output).
% \mathcal{T}_i partially subsumed by \mathcal{T}_e, because data conditions for \mathcal{T}_i are created through \mathcal{T}_e.
%  - ex1) uaf - reference counting
%  - ex2) bo - integer underflow

\subsection{Untargeted Fuzzing}
\label{s:fuzz:unfuzz}

Fuzzing, as a form of software testing, aims at minimizing the number of unknown
abnormal program behaviors. \emph{Untargeted} fuzzing addresses this goal by:
(i) investigating as many \emph{new} program behaviors as possible and (ii)
keeping the new behaviors \emph{more interesting} (i.e., more likely revealing
unknown abnormal behaviors).

\pp{Formal justification}
%
The approach can be described formally as follows. Let the
\emph{interestingness} of a program behavior be $P(\mathrm{abnormal})$, the
expectation of a certain program behavior being abnormal before observing
it.\footnote{See \autoref{s:disc} for the compatibility of this definition and
the conventional meaning of interestingness in untargeted fuzzing.} Furthermore,
let $P(\mathrm{new})$ be the probability of a new behavior in the next
execution.  Then, the probability of discovering unknown abnormal behavior in
the next execution is
%
\begin{equation}
  P(\mathrm{new} \cap \mathrm{abnormal}) = P(\mathrm{new}) \times P(\mathrm{abnormal} \mid \mathrm{new}).
\end{equation}

In this formulation, untargeted fuzzing attempts to (i) increase
$P(\mathrm{new})$ to investigate more program behaviors while (ii) keep 
$P(\mathrm{abnormal} \mid \mathrm{new})$ as high as possible to ensure new
behaviors interesting.
%
Notice that executing more inputs is not the same as observing more distinct
behaviors, as inputs can exhibit the same behavior (e.g., the same
early-termination).

\pp{Interestingness in practice}
%
As the interestingness $P(\mathrm{abnormal})$ depends on the expectation of an
\emph{unobserved} behavior, there is no direct way to measure or formalize
interestingness. However, the practice of untargeted fuzzing in recent years
suggests that abnormal behaviors get increasingly unlikely to require a
large number of branch hit when it gets larger.
%
The prime example is the branch hit count bucketing in AFL \cite{afl}, where the
bucket size gets larger roughly by the power of 2 (i.e., 1, 2, 3, 4-7, 8-15,
...).
%; all hit counts are treated the same within a bucket.
%
%This is also intuitive because if a certain abnormal behavior can manifest at a
%low loop count, such a behavior is not \emph{unknown} anymore by when it reaches
%a higher loop count.

To formalize this, let $X=n$ denote when a program behavior takes a 
branch $X$ $n$ times ($n \ge 1$). Then, the interestingness of a program
behavior when $X=n$ is;
%
\begin{equation}
  P(\mathrm{abnormal} \mid X=n) \propto 1/n.
\end{equation}

%Notice that this formulation only holds when $n \ge 1$, meaning that it does not
%suggest anything when a loop was untaken.

% what's the meaning of "testing"?
%  - ensuring no more unknown flaws.
%  - "the more rigorous, the less probable the tested parts still have flaws."

\pp{Completeness of untargeted fuzzing}
%
As the procedure of untargeted fuzzing can be seen as maximizing observed
interesting behaviors in the program behavior space, the portion of such 
behaviors in the space directly indicates the \emph{completeness} of the
procedure: the more it checks such behaviors, the less the unknown
abnormal behaviors are expected to be left.

Based on this, we can define the \emph{relative completeness} between
different untargeted fuzzing techniques as follows: given the same amount of
time and computing resource, \textbf{how many more interesting program behaviors
has it observed than others?} We argue that relative completeness is a
\emph{strong quality metric} for untargeted fuzzing as it closely indicates how
much more a fuzzer reduces the expectation of unknown abnormal behaviors than
others.

%Notice that, in contrast, it is hard to measure \emph{absolute} completeness
%because the total number of behaviors is unknown.  \autoref{s:disc} discusses
%this in detail.

\section{Logic State Coverage}
\label{s:lscov}

In theory, relative completeness can be naively measured by counting distinctive
program behaviors. However, this naive approach is infeasible as fuzzing
produces hundreds of arbitrarily long instruction streams \emph{every second}.
%
In this section, we propose \emph{logic state coverage} as a proxy of relative
completeness that indirectly counts interesting program behaviors.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/prog-to-logic.pdf}
  \caption{The program behavior space and the logic space. Red indicates
  abnormal program behaviors or logic states}.
  \label{f:prog-to-logic}
\end{figure}

\pp{Logic state and logic space}
%
A \emph{logic state} $l$ is a set of all satisfied branches during execution,
each of which is paired with the integer logarithm of the corresponding branch
hit count. Formally, given a branch history $\mathcal{T}_b$ of an execution,
%
\begin{equation}
\label{e:ls}
  l := \{(b, n(b)) \mid b \in \mathcal{T}_b\},
\end{equation}

\noindent where $n(b) = \lfloor \log_2{m(b)} \rfloor$ and $m(b)$ is the hit
count of a branch $b$ in $\mathcal{T}_b$.  Notice that, as it gets larger, a
branch hit count $m(b)$ shares the same integer "bucket" $n(b)$ with
exponentially more hit counts (i.e., $n(b)=x \iff m(b) \in \{2^x, ...,
2^{x+1}-1\}$).

A \emph{logic space} $\mathbb{L}$, then, is a set of all possible logic states
of a given program. 
%
It is possible to see a logic space as the \emph{subdivision} of a program
behavior space along logic states. \autoref{f:prog-to-logic} shows the
relationship between a program behavior space and a logic space, where each
\emph{partition} of a subdivided program behavior space corresponds to one logic
state.

\pp{Logic state coverage}
%
\emph{Logic state coverage} is \emph{the count of observed distinctive logic
states during fuzzing}, where a logic state is called \emph{covered} when
fuzzing observed a program behavior from the logic state (i.e., triggering all
and only the branches in the logic state). 
%
Analogically, logic state coverage represents the \emph{covered area} of a logic
space.

Logic state coverage is crucially distinguished from edge coverage in that, 
while edge coverage merges all observed edge traces into one, logic state
coverage distinguishes every logic state and counts them individually. This
enables logic state coverage to count underlying program behaviors independent 
of what has been observed before, while edge coverage unpredictably ignores some
of them as it is heavily affected by the previous observation.

As shown in \autoref{f:prog-to-logic}, a logic state (i.e., a partition in the
program behavior space) may contain various program behaviors, suggesting a
single covered logic state may encompass several different behaviors. However,
in \autoref{s:prop}, we argue that a logic state is representative of
interesting program behaviors as it (i) weighs interesting program behaviors
over uninteresting ones and (ii) only contains the program behaviors of the same
normality.

\section{Representativeness of Logic States}
\label{s:prop}

In this section, we discuss the desirable properties of logic states to
represent interesting program behaviors (\autoref{s:prop:prop}). Then, we
continue to discuss how logic states have such properties
(\autoref{s:prop:repr} and \ref{s:prop:local}).

\subsection{Desirable Properties}% as a Proxy Metric}
\label{s:prop:prop}

\pp{Interestingness}
%
Logic states should be sufficiently representative of the \emph{interesting}
program behaviors. Specifically, it should distinguish most program behaviors
deemed interesting while not over-representing less interesting ones.

\pp{Normality}
%
The \emph{normality} of all program behaviors should be uniform (i.e., the same)
within a logic state. Otherwise, the normality of one observed program behavior
cannot represent that of other behaviors in the same logic state.
%
%\pp{Feasibility}
%%
%Measuring logic state coverage should be \emph{feasible} to implement. In other
%words, the measurement mechanism should be clear and the implementation
%requirement should not be unrealistic.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/repr.pdf}
  \caption{Example control flow graph and the number of program behaviors
  (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
  of the branch $b$. Dotted lines demarcate the start of a new power-of-2 branch
  hit count.}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:repr}
\end{figure}

\subsection{Interestingness}
\label{s:prop:repr}

Logic states distinguish the program behaviors with smaller branch hit counts
in finer details (i.e., distinguishing \emph{interesting} behaviors) but
coalesce the behaviors with larger hit counts (i.e., avoiding
over-representation of \emph{uninteresting} behaviors). This results in a larger
number of covered logic states (i.e., larger logic state coverage) when the
observed program behaviors are more interesting.

%This is because logic
%states lump together larger hit counts into fewer integer buckets
%(\autoref{e:ls}).

\autoref{f:repr} shows an example control-flow graph and the number of possible
program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
count of the branch $b$. For example, there are 
two possible program behaviors, $b_2$ after $b_1$ or $b_1$ after
$b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
%Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
%
The dotted lines demarcate the beginning of a new power-of-2 branch hit count
(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
bucket. Each region surrounded by dotted lines constitutes \emph{one logic
state}, as all contained program behaviors fall into the same integer bucket
in every branch.

%Notice that a program behavior is deemed more interesting as it exhibits
%smaller branch hit counts (\autoref{s:fuzz:unfuzz}). 
As shown, a logic state distinguishes more interesting program behaviors in a
finer granularity, representing fewer behaviors with smaller branch hit counts
(i.e., bottom left). On the other hand, it coalesces more behaviors when
the branch hit counts get larger, where individual behaviors are deemed less
interesting. 
%
This results in a larger number of covered logic states when the observed
behaviors are more interesting (e.g., three program behaviors result in
three different logic states when $m(b_3)<2$) while the opposite happens when
they are not (e.g., a total of 11,950 behaviors fall into \emph{one} logic state
when $4 \le m(b_1) < 8$ and $4 \le m(b_2) < 8$).

%\autoref{f:repr} reveals two important properties of logic states. First, a
%logic state distinguishes interesting program behaviors with smaller branch hit
%counts in a finer granularity. For example, a logic state represents
%exponentially fewer program behaviors as $m(b_1)$ and $m(b_2)$ approach to 1.
%Second, a logic state coalesces less interesting program behaviors that require
%high branch hit counts or exhibit specific branch ordering, avoiding
%over-representation of them. For example, all 11,950 program behaviors
%exhibiting different branch ordering with $4 \le m(A) \le 7$ and $4 \le m(B) \le
%7$ are lumped into \emph{one} logic state.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/local.pdf}
  \caption{Example control flow graph and program behaviors. The exceptional
  condition $e$ is satisfied when $\mathrm{mem}(q)$ is a freed memory. $l(X)$
  denotes the logic state of a program behavior $X$ (hit count omitted).}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:local}
\end{figure}

\subsection{Normality}
\label{s:prop:local}

In one logic state, \emph{all} program behaviors are either normal or abnormal
altogether. 
%
This is because normal behaviors trigger \emph{exit branches} before
reaching program exit points, while abnormal behaviors do not. Since the logic
states of two behaviors differ by exit branches, they cannot have the same set
of satisfied branches, hence the same logic state.

\autoref{f:local} shows an example program that contains a use-after-free
exception $e$, which is satisfied when $\mathrm{mem}(q)$ belongs to freed
memories. Three example program behaviors and their logic states are shown on
the side. Since normal behaviors (Behaviors A and B) terminate at the program
exit, their logic states contain the exit branch $b_x$ that directly leads to
the program exit. On the other hand, since the abnormal behavior (Behavior C)
triggers the exception $e$ that crashes the execution before reaching the
program exit, its logic state does not contain any exit branch unlike normal
behaviors.

%
%\subsection{Feasibility of Measurement}
%\label{s:prop:feasi}
%
%% concerns: space and time.
%%  - time: less important, unless the overheads are too prohibitive for real-time usage.
%%    - reason: this measurement is only for evaluation, not for practical use.
%%  - space: main concern, because a program behavior space is presumably large (i.e., a
%%    huge number of program behaviors expected). shouldn't be unrealistic.
%% step-by-step procedure
%%  1. record the logic state of an execution
%%  2. add it to the observed set
%%  3. count the number of elements in the set
%% feasibility of steps
%%  1. (space) exactly the same as the overheads of coverage instrumentation.
%%  2. (space) rough upper bound of the number of logic states is manageable.
%%     - set implementations proportional to the number of elements.
%%  3. (space) wouldn't require more non-trivial space (compared to the set itself).
%
%% TODO: "unrealistic?"
%
%Measuring logic state coverage has a clearly defined procedure to follow, which 
%does not require any unrealistic implementation. Two main concerns regarding 
%implementation are \emph{temporal} and \emph{memory} overheads, but we note
%that temporal overheads are relatively unimportant as the purpose of the
%measurement is \emph{evaluation} (i.e., comparing fuzzers), not for the actual
%fuzzing campaign. Memory overheads, on the other hands, are the actual concern
%as the size of a logic space is expected to be huge (i.e., massive number of
%possible logic states). However, we show that the memory requirement is also not
%prohibitive in the following.
%
%\pp{Step-by-step procedure}
%%

\section{Measuring Logic State Coverage}
\label{s:measure}

In this section, we first summarize the high-level procedure of logic space
coverage measurement and its subsequent requirements 
%to ensure fairness across different fuzzers 
(\autoref{s:measure:req}). Then, we introduce a \emph{bloom filter} as an
effective way to achieve the requirements (\autoref{s:measure:bloom}).

\subsection{High-level Procedure}
\label{s:measure:req}

% - minimal computation overhead 
% - constant computation overhead 
% - feasible memory overhead

%\pp{Procedure}
%
%At a high level, measuring logic state coverage can be described with the
%following procedure:
At a high level, the measurement can be described as follows:

\begin{enumerate}[noitemsep,label=\arabic*)]
  \item \emph{Record} a logic state per execution.
  \item \emph{Add} the logic state to a set of observed logic states.
  \item \emph{Count} the size of the set, yielding logic state coverage.
\end{enumerate}

In this procedure, recording a logic state (1) is technically identical to edge
tracing in coverage-guided fuzzers \cite{afl,fioraldi2020aflpp,libfuzzer}.
Managing logic state coverage (2 and 3), on the other hand, poses an extra
challenge as fuzzers are expected to observe a myriad of distinct logic states
during a campaign.

\pp{Requirements}
%
As the purpose of logic state coverage is comparing (i.e., evaluating) different
fuzzers, the measurement should not induce any bias to certain fuzzers. To this
end, it should satisfy the following requirements.

\begin{itemize}
%  \item \textbf{R0. Measurement accuracy.}
%    The measurement should yield a reliable number that properly captures logic
%    state coverage without a significant error.

  \item \textbf{R1. Light computation overheads.}
    %Although the coverage measurement is only for evaluation, 
    The computation overheads should not be heavy. Otherwise, it would overshadow
    the benefit of fast fuzzing executions, penalizing high-speed fuzzer designs
    \cite{sergej2021nyx,schumilo2020hypercube,song2020agamotto}.
    % NOTE: "heavy" not well defined.

  \item \textbf{R2. Constant computation overheads.}
    The measurement overheads should not increase as logic state coverage
    expands. Otherwise, it would penalize the fuzzers with larger logic space
    coverage.

  \item \textbf{R3. Feasible memory overheads.}
    The memory requirement for the measurement should be feasible for commodity
    evaluation settings for practical reasons.
    % NOTE: "feasible" not well defined.
\end{itemize}

\subsection{Leveraging a Bloom Filter}
\label{s:measure:bloom}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/bloom.pdf}
  \caption{Operation illustration of a bloom filter.}
  \label{f:bloom}
\end{figure}

% why bloom filter
% introduction

For logic state coverage management, we employ a \emph{bloom filter} that 
offers an %computationally and spatially 
efficient set implementation at the cost of manageable inaccuracy (i.e., false
positives).
%
%\pp{Operation summary}
%
\autoref{f:bloom} illustrates the basic operations of a bloom filter. Starting
from an array of 0s, it \emph{adds} an element by setting the hash indices to 1
and \emph{counts} the number of elements by tallying 1s in the filter and
applying it to the counting formula (\autoref{e:count}).

% usage: logic state (element), a set of observed logic states (filter)
% tight error bounds, which can further be suppressed by parameters (R0)
% hash and formula calculation (R1)
% constant-time adding / counting (R2)
% irrelevant to the actual size of an element (R3)
%
\pp{Usage and benefit}
%
In the measurement, a bloom filter represents \emph{a set of observed logic
states}, which accepts a logic state every execution and yields logic state
coverage via the number of elements in the set. It only requires a few
computations for hashes and the counting formula (\textbf{R1}), both of which
are nearly $O(1)$ as the number of hashes and the filter size are fixed
(\textbf{R2}). Furthermore, the filter size is entirely agnostic to the size of
a logic state thanks to hashing (\textbf{R3}).

\pp{Deciding parameters}
%
A bloom filter may introduce some inaccuracy by construction. However, it can
be reliably suppressed by the choice of data structure parameters, namely the
filter size (i.e., the number of bits) $n_b$ and the number of hashes $n_h$.
They can be optimally determined by the maximum expected number of elements
$n_e$ and the desired false positive probability $\epsilon$ by the following
equations \cite{tarkoma2012bloom}:
%
\begin{equation}
  n_b = -n_e\ln{\epsilon}/(\ln{2})^2, \enspace n_h = -\log_2{\epsilon},
  \label{e:param}
\end{equation}

In our setting, $n_e$ corresponds to the upper bound of \emph{observable
distinct logic states} during a fuzzing campaign. To conservatively estimate
$n_e$, we adopt three premises in ideal evaluation : (i) fuzzing continues for
the maximum 24 hours, (ii) a fuzzer executes the maximum 1,000 inputs per
second, and (iii) \emph{every} execution yields a distinctive logic state. Then, 
%
\begin{align}
  n_e &= \SI{24}{\hour} \times \SI[per-mode=symbol]{3600}{\second\per\hour}
         \times \SI[per-mode=symbol]{1000}{\exec\per\second} 
         \times \SI[per-mode=symbol]{1}{\state\per\exec} \nonumber \\
      &= \SI{86.4e+6}{\state} 
         \approx \SI[parse-numbers=false]{84 \times 2^{20}}{\state}. \nonumber
\end{align}

Assigning the upper bound $n_e$ and a reasonable false positive probability
$\epsilon=0.05$ to \autoref{e:param} yields:
%
\begin{equation}
  n_b = \SI{538e+6}{\bit}\approx\,\SI{512}{\mbit}=\SI{64}{\mb}, \enspace n_h = 4.32 \approx 4. \nonumber
\end{equation}

Notice that adding a logic state only requires calculating four hashes per
execution (\textbf{R1} and \textbf{R2}) and the memory overhead ($\SI{64}{\mb})$
is also marginal to a commodity setup (\textbf{R3}).

\pp{Counting elements}
%
Along with data structure parameters, a counting formula that estimates the
number of elements may also affect the accuracy of logic state coverage.
Papapetrou et al. \cite{papapetrou2010cardinality} proposed a high-accuracy
counting formula that calculates the estimated number of elements
$\tilde{n}_e(X)$ when the number of 1s in the filter is $X$ as follows:
%
\begin{equation}
  \tilde{n}_e(X) = \frac{\ln{(1-X/n_b)}}{n_h \ln{(1-1/n_b)}}.
  \label{e:count}
\end{equation}

\autoref{e:count} comes with three major benefits. First, it offers one of the
best accuracy among all alternatives 
\cite{harmouch2017cardinality}. 
%, while its error rate is \emph{inversely proportional} to the actual number of
%elements in the set (i.e., even \emph{less} error as logic state coverage
%grows) \cite{harmouch2017cardinality}. 
%
Second, it allows for a near-constant-time calculation as it only requires the
number of 1s apart from the formula calculation, as well as empirically shown in
\cite{harmouch2017cardinality} (\textbf{R2}). 
%
Finally, it presents a calculable error bound that the actual number of elements
likely falls within given a confidence probability \cite{papapetrou2010cardinality}.

% TODO: fast logarithm calculation? or empirical?
% TODO: error bound formula.

\section{Design and Implementation}
\label{s:design}

%To satisfy the requirements, we incorporate a \emph{bloom filter} to manage a
%set of observed logic states. 
In this section, we first present the design overview (\autoref{s:design:over})
and elaborate on details (\autoref{s:design:rec} and \ref{s:design:count}).

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/design.pdf}
  \caption{Logic state coverage measurement overview.}
  \label{f:design}
\end{figure}

\subsection{Overview}
\label{s:design:over}

% basics: record distinct logic states to a bloom filter, and estimate # later.
%  - (1) for each execution, edge trace -> N hash(edge trace)'s
%  - (2) insert N hash(edge trace)'s to the bloom filter.
%  - (3) periodically estimate the # of distinct edge traces = logic states.

\autoref{f:design} illustrates the workflow of logic state coverage
measurement. Similar to edge coverage, it first records and buckets the branch
hit counts of every execution, yielding a \emph{logic state} as a result 
(\autoref{s:design:rec}). Then, it adds the recorded logic state to a 
\emph{bloom filter}, representing a set of observed logic states, by setting the
hashed indices (\autoref{s:design:up}).  Finally, the measurement periodically
reads off the bloom filter to count the number of observed logic states
(\autoref{s:design:count}).

\subsection{Recording a Logic State}
\label{s:design:rec}

% summary: similar to the conventional edge tracing in coverage-guided fuzzing.
%  - create a edge hash combining two consecutive basic block hashes.
%  - increase the hit count of each each hash whenever it visits it.
%  - bucket the hit counts into their integer logarithms.
% meaning
%  - edge hash --> branch in a logic state
%  - bucketed hit count --> bucket of the corresponding branch
%  - entire bucketed edge trace --> logic state
% overheads
%  - (R1) proven by practice.
%  - (R3) minimal memory requirement -- around 64KB.

\subsection{Updating Logic State Coverage}
\label{s:design:up}

% intro: bloom filter
% summary
%  - create hashes of a logic space.
%  - set the indices of the bloom filter, indicated by the hashes.
% determining bloom filter parameters
%  -

\subsection{Counting Logic State Coverage}
\label{s:design:count}

\section{Experiment}

\subsection{Experiment Setup}

\subsection{Measurement Overheads}

\subsection{General-purpose Fuzzing}

\subsection{Hypervisor Fuzzing}

% same cov: what can we learn more from logic state cov?

\subsection{Grammar Fuzzing}

% init corpus cov: what can we learn more from logic state cov?

\section{Discussion}
\label{s:disc}

\pp{Absolute completeness of untargeted fuzzing}
%
Unlike relative completeness, it is difficult to measure the \emph{absolute}
completeness of untargeted fuzzing because the total number of program behaviors
is unknown: if it can be known, then we would already know which abnormal
behaviors are possible, precluding the necessity of fuzzing in the first place.

One possible compromise is performing preliminary static analysis to
\emph{estimate} the total number of program behaviors, including abnormal ones.
However, it would pose a potential problem that the estimated 100\% completeness
does not necessarily mean the actual 100\% completeness, which would defeat the
major benefit of absolute completeness.

\pp{Generalization to multi-thread programs}
%
Unlike single-thread programs, \emph{multi-thread} programs may concurrently
execute multiple basic blocks. In this case, a program behavior (i.e., a stream
of executed instructions) also depends on the thread interleaving in
addition to the branch and exception histories, which breaks the proxy
properties of a logic space (i.e., interestingness and normality).
An alternative proxy of relative completeness may be proposed by either
extending logic state coverage or devising yet another coverage metric.

\pp{Normality of a partial logic state}
%
It is crucial to notice that an abnormal behavior \emph{still follows the
regular control flow up until any exception happens}. In \autoref{f:local}, the
abnormal behavior (Behavior C) follows the same control flow to a normal
behavior (Behavior B) until a use-after-free happens, which makes the behavior
eventually abnormal unlike its normal counterpart. This means that, even though
a behavior is known to be normal, it does not suggest much about the normality
of other behaviors \emph{on course for} such.

%At a high level, this can manifest when multiple inputs trigger the same
%branches but only some of them satisfy exceptions (e.g., due to different data
%values).

\pp{Interestingness: definition vs. convention}
%
Although the \emph{interestingness} has been widely discussed in recent
untargeted fuzzing, it has never been clearly defined. The conventional
understanding is a property of an \emph{input} having \emph{new
execution paths} in its resulting behavior. In comparison, this work
defines interestingness as a property of a \emph{program behavior} indicating 
the \emph{expectation} of being an abnormal behavior.

Despite an apparent difference between them, the definition \emph{subsumes} the
convention because if an input discovered a new path (conventional
interesting), its behavior would have a higher expectation to be abnormal than
the ones only exhibiting previously checked paths (defined interesting). 
%
Still, there are some disagreements between the definition and the convention,
such as when a behavior \emph{contains} another known abnormal behavior without
discovering any new path. The definition may be refined to resolve such
disagreements.

\pp{Completeness of targeted fuzzing}
%
The completeness of untargeted fuzzing hinges on the observation that the more
program behavior it checks, the less abnormal program behaviors are expected to
be left. This roughly translates to $P(\mathrm{abnormal} \mid \mathrm{new})$
being equal throughout a fuzzing campaign.
%, whereby $P(\mathrm{new} \cap
%\mathrm{abnormal})$ then majorly depends on how high $P(\mathrm{new})$ is;
%proportional to the number of observed program behaviors per time.
%
However, targeted fuzzing (e.g., directed or regression fuzzing)
\emph{prioritizes} code that likely leads to abnormal behaviors, which may result
in a larger $P(\mathrm{abnormal} \mid \mathrm{new})$ at the beginning that slowly
decreases over time.

This affects the fundamental observation for completeness because targeted
fuzzers may reveal more abnormal behaviors even after observing fewer program
behaviors.
%
One possible remedy is refining interestingness to incorporate a complete set of
factors that affects $P(\mathrm{abnormal})$ (e.g., freshness of code).  A
further investigation on interestingness is required.

\pp{Alternative ways to manage logic state coverage}
%
There has been much research work regarding how to estimate the cardinality
(i.e., the number of elements) in a set in an efficient way
\cite{papapetrou2010cardinality,harmouch2017cardinality}, where using a bloom
filter is just one of the approaches. Harmouch et al.
\cite{harmouch2017cardinality} evaluated different cardinality approximation
approaches and compared their accuracy with various benchmarks.  Although using
a bloom filter is the most recent approach compared in the paper, other
alternative approaches can be incorporated to manage logic state coverage as it
is not always the optimum solution.

\section{Related Work}

\pp{Reliability of conventional metrics}
%
Since the advent of popular fuzzing, researchers have consistently
called into question a method to evaluate fuzzers. Klees et al.
\cite{klees2018evaluating} evaluated then state-of-the-art fuzzers and raised an
issue about using edge coverage and the number of discovered bugs as quality
metrics. \textsc{UniFuzz} \cite{li2021unifuzz} also pointed out that such
metrics are incomprehensible and lead to incomplete assessment. B\"{o}hme et al.
\cite{bohme2022reliability} also noted that edge coverage does not strongly
represent the comparative quality between fuzzers.  While they all suggest the
necessity of an alternative quality metric, it has yet to be proposed and widely
accepted in practice.

\pp{Alternative metrics}
%
Some researchers did propose alternative metrics for coverage-guided fuzzing
\cite{wang2020notallcov,wang2019impactcov,yan2020pathafl,gan2020greyone,gan2018collafl}.
However, they are commonly meant for \emph{performance} (e.g., more bugs or edge
coverage), not for \emph{comparison}, which makes using such metrics for
comparison likely yield an unjustified advantage toward certain fuzzers.
%
\textsc{Sand} \cite{kong2024sand} proposed \emph{execution patterns}
(conceptually similar to logic states) to enable fuzzing without sanitization.
However, similar to other alternative metrics, it was never meant for
comparative evaluation nor correlated to the fuzzing quality. 
%designed for them.

\pp{Evaluation methods and platforms}
%
%Similar to the relative completeness argument (\autoref{s:fuzz:unfuzz}),
B\"{o}hme et al. \cite{bohme2021residual} proposed a technique to estimate the
probability of discovering more bugs,
%using its edge coverage trend.  However, the expected maximum number of bugs
%highly depends on the capability of individual fuzzers, which makes it
%impossible to directly compare the estimated probabilities between fuzzers.
but the probability cannot be directly compared between fuzzers as it highly
depends on the capability of individual fuzzers.
% to each other.
%
\textsc{UniFuzz} \cite{li2021unifuzz} and \textsc{FuzzBench}
\cite{metzman2021fuzzbench} presents a platform to comparatively evaluate
fuzzers in multiple metrics. 
%including edge coverage and the number of bugs, 
%While the use of multiple metrics is susceptible to an interpretation bias,
%and does not provide a reliable agreed-upon quality measure.
%
Logic state coverage can be readily incorporated into the platform as a quality
metric.

\section{Conclusion}

%-------------------------------------------------------------------------------
% BIBLIOGRAPHY
%-------------------------------------------------------------------------------

% NOTE: Commented out just until I make the first citation.
\bibliographystyle{plain}
\bibliography{main}

%-------------------------------------------------------------------------------
% APPENDIX
%-------------------------------------------------------------------------------

\begin{appendix}

\end{appendix}

\end{document}

### 2024-02-21 lscov/lscov-llvm-pass.so.cc
some housekeeping

@@ -17,8 +17,7 @@
 #include "llvm/Support/FileSystem.h"
 #include "llvm/Transforms/IPO/PassManagerBuilder.h"
 
-#include <cstdlib>
-#include "debug.h"
+#include "stuff.h"
 
 using namespace llvm;
 
@@ -56,7 +55,7 @@ PreservedAnalyses IRTestbed::run(Module &M, ModuleAnalysisManager &MAM) {
       IRBuilder<> IRB(&(*IP));
 
       /* Make up cur_loc */
-      unsigned int cur_loc = random() % LSTATE_SIZE;
+      unsigned int cur_loc = RANDOM(LSTATE_SIZE);
       ConstantInt *CurLoc = ConstantInt::get(Int32Ty, cur_loc);
 
       /* Load prev_loc */

### 2024-02-21 lscov/stuff.h

@@ -1,41 +1,28 @@
 /*
-  Copyright 2013 Google LLC All rights reserved.
-
-  Licensed under the Apache License, Version 2.0 (the "License");
-  you may not use this file except in compliance with the License.
-  You may obtain a copy of the License at:
-
-    http://www.apache.org/licenses/LICENSE-2.0
-
-  Unless required by applicable law or agreed to in writing, software
-  distributed under the License is distributed on an "AS IS" BASIS,
-  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-  See the License for the specific language governing permissions and
-  limitations under the License.
-*/
-
-/*
-   american fuzzy lop - debug / error handling macros
-   --------------------------------------------------
-
-   Written and maintained by Michal Zalewski <lcamtuf@google.com>
-*/
-
-/*
- * lscov - debug macros 
- * --------------------
- * 
- * Blatantly stolen from AFL. (https://github.com/google/AFL)
+ * lscov - stuff 
+ * -------------
+ *
+ * Constants, debug macros, and stuff.
+ * Debug macros blatantly stolen from AFL. (https://github.com/google/AFL)
  * See "debug.h" in AFL for the original implementation.
  */
 
-#ifndef _HAVE_DEBUG_H
-#define _HAVE_DEBUG_H
+/* We're living in 2024 and still recommended to implement header guards
+   with 'ifndef...endif'. I'll just use 'pragma once' because I have little
+   regard to the de-jure standard (and it's no network software either). */
+#pragma once
 
 #include <errno.h>
+#include <stdlib.h>
 
-#include "types.h"
-#include "config.h"
+/* Version string */
+
+#define VERSION "0.01"
+
+/* Logic state size: simply following MAP_SIZE in AFL. */
+
+#define LSTATE_SIZE_POW2 16
+#define LSTATE_SIZE      (1 << LSTATE_SIZE_POW2)
 
 /*******************
  * Terminal colors *
@@ -248,19 +235,6 @@
     if (res < 0) PFATAL(x); else FATAL(x); \
   } while (0)
 
-/* Error-checking versions of read() and write() that call RPFATAL() as
-   appropriate. */
+/* Random number */
 
-#define ck_write(fd, buf, len, fn) do { \
-    u32 _len = (len); \
-    s32 _res = write(fd, buf, _len); \
[…]

### 2024-02-21 lscov/lscov-llvm-rt.o.c
rt

@@ -1,0 +1,69 @@
+/*
+ * lscov - instrumentation runtime 
+ * -------------------------------
+ * 
+ * Runtime components responsible for setup and status update.
+ * Referred to AFL. (https://github.com/google/AFL)
+ * See "llvm_mode/afl-llvm-rt.o.c" for the reference implementation.
+ */
+
+#include "stuff.h"
+
+/* Constructor/destructor priority. Using some arbitrarily low priority. */
+
+#define CONST_PRIO 255 
+
+/* Globals for instrumentation */
+
+u8             __lscov_area_initial[LSTATE_SIZE + sizeof(lsrec_stat_t)];
+u8*            __lscov_area_ptr = __lscov_area_initial + sizeof(lsrec_stat_t);
+lsrec_stat_t*  __lscov_recstat_ptr = __lscov_area_initial; 
+
+__thread u32   __lscov_prev_loc;
+
+
+/* Initialization (per execution) */
+
+__attribute__((constructor(CONST_PRIO))) 
+void __lscov_init(void) {
+  u8 *id_str = getenv(SHM_ENV_VAR);
+
+  /* Same as AFL. If we're running with logic state coverage measurement, attach
+     to the appropriate region. SHM_ENV_VAR should be set in the measurement
+     daemon, of course. */
+
+  if (id_str) {
+    u32 shm_id = atoi(id_str);
+    __lscov_area_ptr = shmat(shm_id, NULL, 0);
+
+    if (__lscov_area_ptr == (void *)-1) {
+      WARNF("Shared memory not attached. Did you start the daemon?");
+      _exit(1);
+    }
+
+    /* Adjust pointers */
+    __lscov_recstat_ptr = __lscov_area_ptr;
+    __lscov_area_ptr += sizeof(lsrec_stat_t);
+
+    /* If the destructor was not called in the last execution (e.g., due to a
+       crash), mark it finished and let the daemon do its job. This hack will
+       make the daemon ignore the very last execution if it was a crash, but
+       it's just only *one* execution. */
+    if (*__lscov_recstat_ptr == LSREC_REC)
+      *__lscov_recstat_ptr = LSREC_FIN;
+
+    /* Wait until SHM is ready */
+    while (*__lscov_recstat_ptr != LSREC_RDY);
+  }
+
+  /* Start recording */
+  *__lscov_recstat_ptr = LSREC_REC;
+}
+
+/* Finalization (per execution) */
+
[…]

### 2024-02-21 lscov/stuff.h

@@ -14,10 +14,32 @@
 
 #include <errno.h>
 #include <stdlib.h>
+#include <stdint.h>
 
 /* Version string */
 
 #define VERSION "0.01"
+
+/* Standard integer types */
+
+typedef uint8_t  u8;
+typedef uint16_t u16;
+typedef uint32_t u32;
+typedef uint64_t u64;
+
+typedef int8_t   s8;
+typedef int16_t  s16;
+typedef int32_t  s32;
+typedef int64_t  s64;
+
+/* Memory barrier */
+
+#define MEM_BARRIER() \
+  __asm__ volatile("" ::: "memory")
+
+/* Environment variable used to pass SHM ID to the called program. */
+
+#define SHM_ENV_VAR "__LSCOV_SHM_ID"
 
 /* Logic state size: simply following MAP_SIZE in AFL. */
 
@@ -238,3 +260,11 @@
 /* Random number */
 
 #define RANDOM(x) (random() % (x))
+
+/* Logic state recording status */
+
+typedef uint8_t lsrec_stat_t;
+
+#define LSREC_RDY ((lsrec_stat_t)0)   // Ready for recording; SHM cleared
+#define LSREC_REC ((lsrec_stat_t)1)   // Now recording
+#define LSREC_FIN ((lsrec_stat_t)2)   // Recording finished

### 2024-02-21 lscov/testbed/stuff.h

@@ -1,0 +1,1 @@
+stuff.h

### 2024-02-21 lscov/lscov-clang.cc
lscov: build script

@@ -1,5 +1,6 @@
 /*
- * Executable clang wrapper with the testbed.
+ * lscov - clang wrapper
+ * ---------------------
  * 
  * Mostly based on AFL. (https://github.com/google/AFL)
  * See "llvm_mode/afl-clang-fast.c" for the original implementation.
@@ -29,7 +30,7 @@ int main(int argc, char** argv) {
   std::string basepath = exepath.substr(0, _name_pos);
 
   std::string real_exepath;
-  if (exename == "tb-clang++")
+  if (exename.length() >= 2 && exename.substr(exename.length() - 2) == "++")
     real_exepath = basepath + "/clang++";
   else
     real_exepath = basepath + "/clang";
@@ -41,24 +42,13 @@ int main(int argc, char** argv) {
     abort();
   }
 
-  std::string libpath = std::string(basepath + "/libLSCovLogicState.so");
-  std::string pass_plugin = "-fpass-plugin=" + libpath;
+  std::string _libpath = std::string(basepath + "/libLSCovPass.so");
+  std::string pass_plugin = "-fpass-plugin=" + _libpath;
+  std::string rt_obj = std::string(basepath + "/libLSCovRT.a");
 
   cc_params[cc_par_cnt++] = (char*)"-Xclang";
   cc_params[cc_par_cnt++] = (char*)pass_plugin.c_str();
-  
-  // TODO: uncomment the followings if needed.
-
-  /*  - if your analysis requires explicitly typed pointers in IR. 
-  cc_params[cc_par_cnt++] = (char*)"-Xclang";
-  cc_params[cc_par_cnt++] = (char*)"-no-opaque-pointers"; */
-
-  /*  - if your analysis precludes any inlining.
-  cc_params[cc_par_cnt++] = (char*)"-Xclang";
-  cc_params[cc_par_cnt++] = (char*)"-fno-inline"; */
-
-  /*  - if your analysis needs some debugging information by default.
-  cc_params[cc_par_cnt++] = (char*)"-g"; */
+  cc_params[cc_par_cnt++] = (char*)rt_obj.c_str();
 
   while (--argc) {
     char* cur = *(++argv);

### 2024-02-21 lscov/lscov-llvm-pass.so.cc

@@ -30,18 +30,16 @@ PreservedAnalyses IRTestbed::run(Module &M, ModuleAnalysisManager &MAM) {
   LLVMContext &C = M.getContext();
 
   IntegerType *Int8Ty  = IntegerType::getInt8Ty(C);
+  PointerType *Int8PtrTy = PointerType::get(Int8Ty, 0);
   IntegerType *Int32Ty = IntegerType::getInt32Ty(C);
 
   /* Show a banner */
   SAYF(cCYA "lscov-llvm-pass " cBRI VERSION cRST " by <iss300@gmail.com>\n");
 
   /* Get globals for the SHM region and the previous location */
-  // TODO: link __lscov_area_ptr to SHM (offset by a status field).
-  GlobalVariable *LSCovMapPtr =
-      new GlobalVariable(M, PointerType::get(Int8Ty, 0), false,
-                         GlobalValue::ExternalLinkage, 0, "__lscov_area_ptr");
+  GlobalVariable *LSCovMapPtr = new GlobalVariable(
+      M, Int8PtrTy, false, GlobalValue::ExternalLinkage, 0, "__lscov_area_ptr");
 
-  // TODO: create __lscov_prev_loc in lscov-llvm-rt.o.c.
   GlobalVariable *LSCovPrevLoc = new GlobalVariable(
       M, Int32Ty, false, GlobalValue::ExternalLinkage, 0, "__lscov_prev_loc",
       0, GlobalVariable::GeneralDynamicTLSModel, 0, false);
@@ -59,18 +57,18 @@ PreservedAnalyses IRTestbed::run(Module &M, ModuleAnalysisManager &MAM) {
       ConstantInt *CurLoc = ConstantInt::get(Int32Ty, cur_loc);
 
       /* Load prev_loc */
-      LoadInst *PrevLoc = IRB.CreateLoad(LSCovPrevLoc);
+      LoadInst *PrevLoc = IRB.CreateLoad(Int32Ty, LSCovPrevLoc);
       PrevLoc->setMetadata(M.getMDKindID("nosanitize"), MDNode::get(C, None));
       Value *PrevLocCasted = IRB.CreateZExt(PrevLoc, IRB.getInt32Ty());
 
       /* Load SHM pointer */
-      LoadInst *MapPtr = IRB.CreateLoad(LSCovMapPtr);
[…]

### 2024-02-21 lscov/lscov-llvm-rt.a.c

@@ -7,6 +7,8 @@
  * See "llvm_mode/afl-llvm-rt.o.c" for the reference implementation.
  */
 
+#include <sys/types.h>
+#include <sys/shm.h>
 #include "stuff.h"
 
 /* Constructor/destructor priority. Using some arbitrarily low priority. */
@@ -26,7 +28,7 @@ __thread u32   __lscov_prev_loc;
 
 __attribute__((constructor(CONST_PRIO))) 
 void __lscov_init(void) {
-  u8 *id_str = getenv(SHM_ENV_VAR);
+  char *id_str = getenv(SHM_ENV_VAR);
 
   /* Same as AFL. If we're running with logic state coverage measurement, attach
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
@@ -38,7 +40,7 @@ void __lscov_init(void) {
 
     if (__lscov_area_ptr == (void *)-1) {
       WARNF("Shared memory not attached. Did you start the daemon?");
-      _exit(1);
+      exit(1);
     }
 
     /* Adjust pointers */

### 2024-02-21 lscov/stuff.h

@@ -1,6 +1,6 @@
 /*
- * lscov - stuff 
- * -------------
+ * lscov - good stuff 
+ * ------------------
  *
  * Constants, debug macros, and stuff.
  * Debug macros blatantly stolen from AFL. (https://github.com/google/AFL)
@@ -9,12 +9,13 @@
 
 /* We're living in 2024 and still recommended to implement header guards
    with 'ifndef...endif'. I'll just use 'pragma once' because I have little
-   regard to the de-jure standard (and it's no network software either). */
+   regard to the de-jure standard (and it's no big code base anyway). */
 #pragma once
 
 #include <errno.h>
 #include <stdlib.h>
 #include <stdint.h>
+#include <stdio.h>
 
 /* Version string */
 

### 2024-02-21 lscov/testbed/stuff.h

@@ -1,1 +1,0 @@
-stuff.h

### 2024-02-21 lscov/lscov-clang.cc
lscov-daemon: sketch

@@ -31,9 +31,9 @@ int main(int argc, char** argv) {
 
   std::string real_exepath;
   if (exename.length() >= 2 && exename.substr(exename.length() - 2) == "++")
-    real_exepath = basepath + "/clang++";
+    real_exepath = basepath + "/wrap-clang++";
   else
-    real_exepath = basepath + "/clang";
+    real_exepath = basepath + "/wrap-clang";
   cc_params[0] = (char*)real_exepath.c_str();
 
   std::string clang_chk = "which " + real_exepath + " >/dev/null 2>&1";

### 2024-02-21 lscov/lscov-daemon.c

@@ -1,0 +1,53 @@
+/*
+ * lscov - measurement daemon 
+ * --------------------------
+ * 
+ * Collect logic states produced by an instrumented binary, and keep observed
+ * logic states with a bloom filter. Periodically tally the elements.
+ *
+ * Supposed to start before (and run parallely with) a fuzzer.
+ */
+
+// TODO: param: tallying period (default: 10 mins).
+// TODO: param: bloom filter size (default: 64MB).
+// TODO: param: output path (default: lscov.out).
+// TODO: param: error bound (default: 95%, disabled: 0%).
+
+#include <sys/mman.h>
+#include "stuff.h"
+
+// TODO: limiting caching? other core?
+u8* bloom_filter;
+
+// TODO: Murmur3 hashing.
+
+int main(int argc, char** argv) {
+  // TODO: create SHM.
+  // TODO: initialize SHM (status, zeroize).
+
+  // TODO: create a bloom filter.
+  // TODO: initialize the bloom filter (zeroize).
+
+  // TODO: set LSREC_RDY.
+  // TODO: call "loop". 
+}
+
+void loop() {
+  // TODO: set the next tallying time.
+  // TODO: wait for LSREC_FIN (or tallying time).
+
+  // TODO: if LSREC_FIN
+  // TODO:   bucketize the hit counts.
+  // TODO:   zeroize the logic state.
+  // TODO:   set LSREC_RDY.
+  
+  // TODO:   hash the logic state.
+  // TODO:   update the bloom filter.
+
+  // TODO: if tallying time
+  // TODO:   set the next tallying time (+start).
+  // TODO:   tally 1s in the bloom filter.
+  // TODO:   calculate the cardinality.
+  // TODO:   calculate the error bound.
+  // TODO:   append new lscov+err to the output.
+}

### 2024-02-21 lscov/lscov-daemon.c
lscov-daemon: functions

@@ -8,18 +8,188 @@
  * Supposed to start before (and run parallely with) a fuzzer.
  */
 
+#include <math.h>
+#include <sys/mman.h>
+#include "stuff.h"
+
 // TODO: param: tallying period (default: 10 mins).
 // TODO: param: bloom filter size (default: 64MB).
 // TODO: param: output path (default: lscov.out).
 // TODO: param: error bound (default: 95%, disabled: 0%).
 
-#include <sys/mman.h>
-#include "stuff.h"
+u32   tallying_period = 600;          // Tallying period (in seconds) 
+u32   bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
+u8    num_hashes = 4;                 // Number of hashes
+u8*   out_path = "lscov.out";         // Output path
+u8    error_percent = 95;             // Error bound (in percent)
 
 // TODO: limiting caching? other core?
-u8* bloom_filter;
+u8*         hit_counts;           // (SHM) Branch hit counts
+recstat_t*  rec_stat;             // (SHM) Branch hit count recording status
+u8*         bloom_filter;         // Bloom filter itself
+u32         start_time;           // Measurement start time (in unix time)
+u32         next_tallying_time;   // Next tallying time (in unix time)
 
-// TODO: Murmur3 hashing.
+// TODO: SIGINT handler; finalize daemon.
+
+inline int is_recording_finished() {
+  return (*rec_stat == RECSTAT_FIN);
+}
+
+u8 flp2(u8 x) {
+  x = x | (x >> 1);
+  x = x | (x >> 2);
+  x = x | (x >> 4);
+  x = x | (x >> 8);
+  x = x | (x >> 16);
+  return x - (x >> 1);
+}
+
+void bucket_hit_counts(u8* lstate) {
+  /* The bucket numbers are one-hot-encoded. In other words, Bucket 3 is encoded
+   * as 0x04 (0b00000100). Hit count 0 goes to Bucket 0. Anything else will go
+   * to Bucket [log_2(hit_count)] + 1, which is the previous power-of-2 integer
+   * interpreted as a one-hot-encoded bit vector. */
+
+  for (int i = 0; i < LSTATE_SIZE; i++) {
[…]

### 2024-02-21 lscov/lscov-llvm-rt.a.c

@@ -17,11 +17,11 @@
 
 /* Globals for instrumentation */
 
-u8             __lscov_area_initial[LSTATE_SIZE + sizeof(lsrec_stat_t)];
-u8*            __lscov_area_ptr = __lscov_area_initial + sizeof(lsrec_stat_t);
-lsrec_stat_t*  __lscov_recstat_ptr = __lscov_area_initial; 
+u8           __lscov_area_initial[LSTATE_SIZE + sizeof(recstat_t)];
+u8*          __lscov_area_ptr = __lscov_area_initial + sizeof(recstat_t);
+recstat_t*   __lscov_recstat_ptr = __lscov_area_initial; 
 
-__thread u32   __lscov_prev_loc;
+__thread u32 __lscov_prev_loc;
 
 
 /* Initialization (per execution) */
@@ -45,7 +45,7 @@ void __lscov_init(void) {
 
     /* Adjust pointers */
     __lscov_recstat_ptr = __lscov_area_ptr;
-    __lscov_area_ptr += sizeof(lsrec_stat_t);
+    __lscov_area_ptr += sizeof(recstat_t);
 
     /* If the destructor was not called in the last execution (e.g., due to a
        crash), mark it finished and let the daemon do its job. This hack will

### 2024-02-21 lscov/stuff.h

@@ -264,8 +264,8 @@ typedef int64_t  s64;
 
 /* Logic state recording status */
 
-typedef uint8_t lsrec_stat_t;
+typedef uint8_t recstat_t;
 
-#define LSREC_RDY ((lsrec_stat_t)0)   // Ready for recording; SHM cleared
-#define LSREC_REC ((lsrec_stat_t)1)   // Now recording
-#define LSREC_FIN ((lsrec_stat_t)2)   // Recording finished
+#define RECSTAT_RDY ((recstat_t)0)   // Ready for recording; SHM cleared
+#define RECSTAT_REC ((recstat_t)1)   // Now recording
+#define RECSTAT_FIN ((recstat_t)2)   // Recording finished

### 2024-02-26 paper/main.tex
minor

@@
   aims to reduce the number of unknown \emph{abnormal} behaviors by observing
-  more \emph{interesting} (i.e., relating to unknown abnormal) behaviors. This
-  suggests that the number of observed interesting behaviors should directly
-  indicate how well the fuzzer achieved its aim (i.e., the quality).
+  more \emph{interesting} (i.e., relating to unknown abnormal) behaviors. The
+  more interesting behaviors a fuzzer has observed, the stronger guarantee it
+  can provide about the absence of unknown abnormal behaviors. This suggests
+  that the number of observed interesting behaviors must directly indicate the
+  fuzzing quality.
 
@@
   proportional to the number of observed interesting behaviors.
-
+  % 
   We implemented logic state coverage using a bloom filter and reevaluated
@@
 suggests that abnormal behaviors get increasingly unlikely to require a
-large number of branch hit when it gets larger.
+larger number of branch hit.
 %
@@
 \autoref{e:count} comes with three major benefits. First, it offers one of the
-best accuracy among all alternatives 
-\cite{harmouch2017cardinality}. 
+best accuracy among all alternatives (c.f., only 4\% error even in an extreme
+filter density of 90\%) \cite{harmouch2017cardinality}. 
 %, while its error rate is \emph{inversely proportional} to the actual number of
@@
 (\autoref{s:design:rec}). Then, it adds the recorded logic state to a 
-\emph{bloom filter}, representing a set of observed logic states, by setting the
-hashed indices (\autoref{s:design:up}).  Finally, the measurement periodically
+\emph{bloom filter} that represents a set of observed logic states, by setting
+the hash indices (\autoref{s:design:up}).  Finally, the measurement periodically
 reads off the bloom filter to count the number of observed logic states

### 2024-02-26 paper/main.tex
discussion: semantic

@@
 
+\pp{Semantically abnormal behaviors}
+%
+While the definition of program behaviors is separated from the output, it can
+still incorporates \emph{semantically} abnormal behaviors (i.e., semantic bugs)
+by means of exceptions. To be specific, semantic error detection such as
+semantic sanitizers \cite{kim2019hydra,yun2016apisan} may capture semantic bugs
+on the fly and make the behavior abnormal by terminating it. The definition
+allows this as exceptions reference the data context before it is revealed to
+the output.
+
 \section{Related Work}

### 2024-02-26 lscov/lscov-daemon.c
lscov-daemon.c: filled TODOs

@@ -9,43 +9,68 @@
  */
 
 #include <math.h>
+#include <signal.h>
+#include <stdio.h>
+#include <sys/ipc.h>
 #include <sys/mman.h>
+#include <sys/shm.h>
+#include <sys/types.h>
+#include <time.h>
 #include "stuff.h"
 
-// TODO: param: tallying period (default: 10 mins).
-// TODO: param: bloom filter size (default: 64MB).
-// TODO: param: output path (default: lscov.out).
-// TODO: param: error bound (default: 95%, disabled: 0%).
+/* Parameters */
 
-u32   tallying_period = 600;          // Tallying period (in seconds) 
-u32   bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
-u8    num_hashes = 4;                 // Number of hashes
-u8*   out_path = "lscov.out";         // Output path
-u8    error_percent = 95;             // Error bound (in percent)
+u32       tallying_period = 600;          // Tallying period (in seconds) 
+u32       bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
+u8        num_hashes = 4;                 // Number of hashes
+const u8* out_path = "lscov.out";         // Output path
+u8        error_percent = 95;             // Error bound (0: disabled)
 
-// TODO: limiting caching? other core?
+/* State variables */
+
+s32         shm_id;               // (SHM) shared memory ID
 u8*         hit_counts;           // (SHM) Branch hit counts
 recstat_t*  rec_stat;             // (SHM) Branch hit count recording status
 u8*         bloom_filter;         // Bloom filter itself
-u32         start_time;           // Measurement start time (in unix time)
-u32         next_tallying_time;   // Next tallying time (in unix time)
+time_t      start_time;           // Measurement start time (in unix time)
+time_t      next_tallying_time;   // Next tallying time (in unix time)
 
-// TODO: SIGINT handler; finalize daemon.
+// FIXME: bloom_filter --> limiting caching? other core?
 
-inline int is_recording_finished() {
+void out_init() {
[…]

### 2024-02-26 lscov/stuff.h

@@ -38,10 +38,6 @@ typedef int64_t  s64;
 #define MEM_BARRIER() \
   __asm__ volatile("" ::: "memory")
 
-/* Environment variable used to pass SHM ID to the called program. */
-
-#define SHM_ENV_VAR "__LSCOV_SHM_ID"
-
 /* Logic state size: simply following MAP_SIZE in AFL. */
 
 #define LSTATE_SIZE_POW2 16
@@ -269,3 +265,8 @@ typedef uint8_t recstat_t;
 #define RECSTAT_RDY ((recstat_t)0)   // Ready for recording; SHM cleared
 #define RECSTAT_REC ((recstat_t)1)   // Now recording
 #define RECSTAT_FIN ((recstat_t)2)   // Recording finished
+
+/* SHM parameters */
+
+#define LSCOV_SHM_KEY    0xdead
+#define LSCOV_SHM_SIZE   (LSTATE_SIZE + sizeof(recstat_t))

### 2024-02-26 lscov/lscov-daemon.c
lscov-daemon.c: semaphore impl

@@ -20,7 +20,7 @@
 
 /* Parameters */
 
-u32       tallying_period = 600;          // Tallying period (in seconds) 
+time_t    tallying_period = 600;          // Tallying period (in seconds) 
 u32       bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
 u8        num_hashes = 4;                 // Number of hashes
 const u8* out_path = "lscov.out";         // Output path
@@ -28,12 +28,17 @@ u8        error_percent = 95;             // Error bound (0: disabled)
 
 /* State variables */
 
-s32         shm_id;               // (SHM) shared memory ID
+s32         shm_hcount_id;        // (SHM) ID for 'hit_count'
+s32         shm_sema_rd_id;
+s32         shm_sema_dr_id;
 u8*         hit_counts;           // (SHM) Branch hit counts
-recstat_t*  rec_stat;             // (SHM) Branch hit count recording status
+sem_t*      sema_rd;
+sem_t*      sema_dr;
 u8*         bloom_filter;         // Bloom filter itself
 time_t      start_time;           // Measurement start time (in unix time)
 time_t      next_tallying_time;   // Next tallying time (in unix time)
+struct timespec loop_timeout;
+
 
 // FIXME: bloom_filter --> limiting caching? other core?
 
@@ -62,12 +67,9 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 }
 
 
-inline void recstat_set_ready() {
-  *rec_stat = RECSTAT_RDY;
-}
-
-inline int recstat_is_finished() {
-  return (*rec_stat == RECSTAT_FIN);
+inline int hcount_wait_until_ready() {
+  // TODO: RT-side should post 'sema_rd'.
+  return sem_timedwait(sema_rd, loop_timeout);
 }
 
 void hcount_bucket_to_lstate(u8* lstate) {
@@ -93,26 +95,52 @@ void hcount_bucket_to_lstate(u8* lstate) {
 
 void hcount_nuke() {
   memset(hit_counts, 0, LSTATE_SIZE);
-  *rec_stat = RECSTAT_RDY;
+  sem_post(sema_dr);  // TODO: RT-side should wait for 'sema_dr'.
 }
 
[…]

### 2024-02-26 lscov/stuff.h

@@ -258,15 +258,8 @@ typedef int64_t  s64;
 
 #define RANDOM(x) (random() % (x))
 
-/* Logic state recording status */
-
-typedef uint8_t recstat_t;
-
-#define RECSTAT_RDY ((recstat_t)0)   // Ready for recording; SHM cleared
-#define RECSTAT_REC ((recstat_t)1)   // Now recording
-#define RECSTAT_FIN ((recstat_t)2)   // Recording finished
-
 /* SHM parameters */
 
-#define LSCOV_SHM_KEY    0xdead
-#define LSCOV_SHM_SIZE   (LSTATE_SIZE + sizeof(recstat_t))
+#define LSCOV_SHM_HCOUNT_KEY    0xdead
+#define LSCOV_SHM_SEMA_RD_KEY   0xbeef
+#define LSCOV_SHM_SEMA_DR_KEY   0x1ee7

### 2024-02-26 lscov/lscov-daemon.c
lscov-llvm-rt.a.c: semaphore impl

@@ -29,8 +29,6 @@ u8        error_percent = 95;             // Error bound (0: disabled)
 /* State variables */
 
 s32         shm_hcount_id;        // (SHM) ID for 'hit_count'
-s32         shm_sema_rd_id;
-s32         shm_sema_dr_id;
 u8*         hit_counts;           // (SHM) Branch hit counts
 sem_t*      sema_rd;
 sem_t*      sema_dr;
@@ -105,42 +103,29 @@ void hcount_init() {
   if (shm_hcount_id < 0) 
     PFATAL("shmget() for hit_count failed");
 
-  hit_counts = (u8 *)shmat(shm_id, NULL, 0);
+  hit_counts = (u8 *)shmat(shm_hcount_id, NULL, 0);
   if (hit_counts == (void *)-1) 
     PFATAL("shmat() for hit_count failed");
 
-  shm_sema_rd_id = shmget(LSCOV_SHM_SEMA_RD_KEY, sizeof(sem_t), 
-      IPC_CREAT | IPC_EXCL | 0666);
-  if (shm_sema_rd_id < 0) 
-    PFATAL("shmget() for sema_rd failed");
-
-  sema_rd = (sem_t *)shmat(shm_id, NULL, 0);
+  /* Initialize semaphores. */
+  sema_rd = sem_open(LSCOV_SEMA_RD_NAME, O_CREAT, 0644, 0);
   if (sema_rd == (void *)-1) 
-    PFATAL("shmat() for sema_rd failed");
+    PFATAL("sem_open() for sema_rd failed");
 
-  shm_sema_dr_id = shmget(LSCOV_SHM_SEMA_DR_KEY, sizeof(sem_t), 
-      IPC_CREAT | IPC_EXCL | 0666);
-  if (shm_sema_dr_id < 0) 
-    PFATAL("shmget() for sema_dr failed");
-
-  sema_dr = (sem_t *)shmat(shm_id, NULL, 0);
+  sema_dr = sem_open(LSCOV_SEMA_DR_NAME, O_CREAT, 0644, 1);
   if (sema_dr == (void *)-1) 
-    PFATAL("shmat() for sema_dr failed");
+    PFATAL("sem_open() for sema_dr failed");
 
-  /* Initialize 'hit_count' and semaphores. */
+  /* Initialize 'hit_count'. */
   hcount_nuke();
[…]

### 2024-02-26 lscov/lscov-llvm-rt.a.c

@@ -17,49 +17,58 @@
 
 /* Globals for instrumentation */
 
-u8           __lscov_area_initial[LSTATE_SIZE + sizeof(recstat_t)];
-u8*          __lscov_area_ptr = __lscov_area_initial + sizeof(recstat_t);
-recstat_t*   __lscov_recstat_ptr = __lscov_area_initial; 
-
+u8           __lscov_area_initial[LSTATE_SIZE];
+u8*          __lscov_area_ptr = __lscov_area_initial;
 __thread u32 __lscov_prev_loc;
+
+sem_t*       __lscov_sema_rd;
+sem_t*       __lscov_sema_dr;
 
 
 /* Initialization (per execution) */
 
 __attribute__((constructor(CONST_PRIO))) 
 void __lscov_init(void) {
-  char *id_str = getenv(SHM_ENV_VAR);
-
   /* Same as AFL. If we're running with logic state coverage measurement, attach
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
      daemon, of course. */
 
-  if (id_str) {
-    u32 shm_id = atoi(id_str);
-    __lscov_area_ptr = shmat(shm_id, NULL, 0);
+  s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 
+      IPC_CREAT | IPC_EXCL | 0600);
 
-    if (__lscov_area_ptr == (void *)-1) {
-      WARNF("Shared memory not attached. Did you start the daemon?");
-      exit(1);
-    }
+  if (shm_hcount_id >= 0) {
+    __lscov_area_ptr = (u8 *)shmat(shm_hcount_id, NULL, 0);
+    if (__lscov_area_ptr == (void *)-1) 
+      PFATAL("shmat() for hit_count failed");
 
-    /* Adjust pointers */
-    __lscov_recstat_ptr = __lscov_area_ptr;
-    __lscov_area_ptr += sizeof(recstat_t);
+    s32 shm_sema_rd_id = shmget(LSCOV_SHM_SEMA_RD_KEY, sizeof(sem_t), 
+        IPC_CREAT | IPC_EXCL | 0666);
+    if (shm_sema_rd_id < 0) 
+      PFATAL("shmget() for sema_rd failed");
+
+    /* Initialize semaphores. */
+    sema_rd = sem_open(LSCOV_SEMA_RD_NAME, 0, 0644, 0);
+    if (sema_rd == (void *)-1) 
[…]

### 2024-02-26 lscov/stuff.h

@@ -260,6 +260,6 @@ typedef int64_t  s64;
 
 /* SHM parameters */
 
-#define LSCOV_SHM_HCOUNT_KEY    0xdead
-#define LSCOV_SHM_SEMA_RD_KEY   0xbeef
-#define LSCOV_SHM_SEMA_DR_KEY   0x1ee7
+#define LSCOV_SHM_HCOUNT_KEY  0xdead
+#define LSCOV_SEMA_RD_NAME    "__lscov_sema_rd" 
+#define LSCOV_SEMA_DR_NAME    "__lscov_sema_dr"

### 2024-02-26 lscov/lscov-clang.cc
fixed compile errors

@@ -46,6 +46,7 @@ int main(int argc, char** argv) {
   std::string pass_plugin = "-fpass-plugin=" + _libpath;
   std::string rt_obj = std::string(basepath + "/libLSCovRT.a");
 
+  cc_params[cc_par_cnt++] = (char*)"-lpthread";
   cc_params[cc_par_cnt++] = (char*)"-Xclang";
   cc_params[cc_par_cnt++] = (char*)pass_plugin.c_str();
   cc_params[cc_par_cnt++] = (char*)rt_obj.c_str();

### 2024-02-26 lscov/lscov-daemon.c

@@ -8,23 +8,26 @@
  * Supposed to start before (and run parallely with) a fuzzer.
  */
 
+#include <fcntl.h>
 #include <math.h>
+#include <semaphore.h>
 #include <signal.h>
 #include <stdio.h>
 #include <sys/ipc.h>
 #include <sys/mman.h>
 #include <sys/shm.h>
+#include <sys/stat.h>
 #include <sys/types.h>
 #include <time.h>
 #include "stuff.h"
 
 /* Parameters */
 
-time_t    tallying_period = 600;          // Tallying period (in seconds) 
-u32       bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
-u8        num_hashes = 4;                 // Number of hashes
-const u8* out_path = "lscov.out";         // Output path
-u8        error_percent = 95;             // Error bound (0: disabled)
+time_t      tallying_period = 600;          // Tallying period (in seconds) 
+u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
+u8          num_hashes = 4;                 // Number of hashes
+const char* out_path = "lscov.out";         // Output path
+u8          error_percent = 95;             // Error bound (0: disabled)
 
 /* State variables */
 
@@ -55,9 +58,9 @@ void out_init() {
 void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
   FILE *fout = fopen(out_path, "a");
 
-  fprintf(fout, "%lu,%lu", time, cov);
+  fprintf(fout, "%u,%u", time, cov);
   if (error_percent > 0)
-    fprintf(fout, "%lu,%lu\n", lower_err, upper_err);
+    fprintf(fout, "%u,%u\n", lower_err, upper_err);
   else
     fprintf(fout, "\n");
 
@@ -65,9 +68,8 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 }
 
 
-inline int hcount_wait_until_ready() {
-  // TODO: RT-side should post 'sema_rd'.
-  return sem_timedwait(sema_rd, loop_timeout);
+static inline int hcount_wait_until_ready() {
+  return sem_timedwait(sema_rd, &loop_timeout);
 }
 
 void hcount_bucket_to_lstate(u8* lstate) {
[…]

### 2024-02-26 lscov/lscov-llvm-rt.a.c

@@ -7,6 +7,7 @@
  * See "llvm_mode/afl-llvm-rt.o.c" for the reference implementation.
  */
 
+#include <semaphore.h>
 #include <sys/types.h>
 #include <sys/shm.h>
 #include "stuff.h"
@@ -41,18 +42,13 @@ void __lscov_init(void) {
     if (__lscov_area_ptr == (void *)-1) 
       PFATAL("shmat() for hit_count failed");
 
-    s32 shm_sema_rd_id = shmget(LSCOV_SHM_SEMA_RD_KEY, sizeof(sem_t), 
-        IPC_CREAT | IPC_EXCL | 0666);
-    if (shm_sema_rd_id < 0) 
-      PFATAL("shmget() for sema_rd failed");
-
     /* Initialize semaphores. */
-    sema_rd = sem_open(LSCOV_SEMA_RD_NAME, 0, 0644, 0);
-    if (sema_rd == (void *)-1) 
+    __lscov_sema_rd = sem_open(LSCOV_SEMA_RD_NAME, 0, 0644, 0);
+    if (__lscov_sema_rd == (void *)-1) 
       PFATAL("sem_open() for sema_rd failed");
 
-    sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
-    if (sema_dr == (void *)-1) 
+    __lscov_sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
+    if (__lscov_sema_dr == (void *)-1) 
       PFATAL("sem_open() for sema_dr failed");
 
     /* If the destructor was not called in the last execution (e.g., due to a
@@ -60,14 +56,14 @@ void __lscov_init(void) {
        make the daemon ignore the very last execution if it was a crash, but
        it's just only *one* execution. */
     int _sema_rd_val, _sema_dr_val;
-    sem_getvalue(sema_rd, &_sema_rd_val);
-    sem_getvalue(sema_dr, &_sema_dr_val);
+    sem_getvalue(__lscov_sema_rd, &_sema_rd_val);
+    sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
 
     if (!_sema_dr_val && !_sema_rd_val)
-      sem_post(sema_rd);
+      sem_post(__lscov_sema_rd);
 
     /* Wait until SHM is ready */
-    sem_wait(sema_dr);
+    sem_wait(__lscov_sema_dr);
   }
 }
 
[…]

### 2024-02-26 lscov/stuff.h

@@ -16,6 +16,7 @@
 #include <stdlib.h>
 #include <stdint.h>
 #include <stdio.h>
+#include <string.h>
 
 /* Version string */
 

### 2024-02-26 lscov/lscov-daemon.c
lscov-daemon.c: sem_timedwait

@@ -23,7 +23,7 @@
 
 /* Parameters */
 
-time_t      tallying_period = 600;          // Tallying period (in seconds) 
+time_t      tallying_period = 2;          // Tallying period (in seconds) 
 u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
 u8          num_hashes = 4;                 // Number of hashes
 const char* out_path = "lscov.out";         // Output path
@@ -48,7 +48,7 @@ void out_init() {
 
   fprintf(fout, "Time,Coverage");
   if (error_percent > 0)
-    fprintf(fout, "(Lower),(Upper)\n");
+    fprintf(fout, ",(Lower),(Upper)\n");
   else
     fprintf(fout, "\n");
 
@@ -60,7 +60,7 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 
   fprintf(fout, "%u,%u", time, cov);
   if (error_percent > 0)
-    fprintf(fout, "%u,%u\n", lower_err, upper_err);
+    fprintf(fout, ",%u,%u\n", lower_err, upper_err);
   else
     fprintf(fout, "\n");
 
@@ -98,7 +98,24 @@ void hcount_nuke() {
   sem_post(sema_dr);
 }
 
+void hcount_stop() {
+  if (shm_hcount_id)
+    shmctl(shm_hcount_id, IPC_RMID, NULL);
+
+  if (sema_rd) {
+    sem_close(sema_rd);
+    sem_unlink(LSCOV_SEMA_RD_NAME);
+  }
+  
+  if (sema_dr) {
+    sem_close(sema_dr);
+    sem_unlink(LSCOV_SEMA_DR_NAME);
+  }
+}
+
 void hcount_init() {
+  atexit(hcount_stop);
+
   /* Initialize SHM. */
   shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 
       IPC_CREAT | IPC_EXCL | 0600);
@@ -120,14 +137,6 @@ void hcount_init() {
 
   /* Initialize 'hit_count'. */
   hcount_nuke();
-}
-
-void hcount_stop() {
-  shmctl(shm_hcount_id, IPC_RMID, NULL);
-  sem_close(sema_rd);
-  sem_close(sema_dr);
-  sem_unlink(LSCOV_SEMA_RD_NAME);
[…]

### 2024-02-27 lscov/emoji.h
lscov: minor

@@ -1,0 +1,82 @@
+/*
+ * lscov - emoji table 
+ * -------------------
+ *  
+ * Absolutely no reason. Just for sh*ts and giggles.
+ * Courtesy of ASCIImoji. (https://asciimoji.com)
+ */
+
+#pragma once
+
+#include <time.h>
+
+static const char* emoji[] = {
+  "( •_•)O*¯`·.¸.·´¯`°Q(•_• )",
+  "ʕ •́؈•̀)",
+  "(☝ ՞ਊ ՞)☝",
+  "O=('-'Q)",
+  "t(ಠ益ಠt)",
+  "(ノಠ益ಠ)ノ彡┻━┻",
+  "(=^･ｪ･^=))ﾉ彡☆",
+  "ò_ô",
+  "(◔_◔)",
+  "(╯°□°)╯",
+  "ε(´סּ︵סּ`)з",
+  "( ͡° ʖ̯ ͡°)",
+  "╚(•⌂•)╝",
+  "¯\\_(ツ)_/¯",
+  "ツ",
+  "☺︎",
+  "¬‿¬",
+  "(;´༎ຶД༎ຶ`)",
+  "ᕙ(⇀‸↼‶)ᕗ",
+  "(๑•́ ヮ •̀๑)",
+  "\\_(-_-)_/",
+  "(̿▀̿‿ ̿▀̿ ̿)",
+  "(ノ ゜Д゜)ノ ︵ ┻━┻",
+  "(ಥ﹏ಥ)",
+  "୧༼ಠ益ಠ༽︻╦╤─",
+  "\\(^-^)/",
+  "( ͡° ͜ʖ ͡°)_/¯",
+  "|=-(¤)-=|",
+  "(=____=)",
+  "ᕦ(òᴥó)ᕥ",
+  "(っ^з^)♪♬",
+  "(°o•)",
+  "WHΣИ $HΛLL WΣ †HЯΣΣ MΣΣ† ΛGΛ|И?",
+  "＼(＾O＾)／",
+  "(⊙＿⊙')",
+  "⊙ω⊙",
+  "\\( ﾟヮﾟ)/",
+  "(•̀ᴗ•́)و ̑̑",
+  "Yᵒᵘ Oᶰˡʸ Lᶤᵛᵉ Oᶰᶜᵉ",
+  "⊹╰(⌣ʟ⌣)╯⊹",
[…]

### 2024-02-27 lscov/lscov-daemon.c

@@ -8,6 +8,8 @@
  * Supposed to start before (and run parallely with) a fuzzer.
  */
 
+#define USE_COLOR   // Yes, please.
+
 #include <fcntl.h>
 #include <math.h>
 #include <semaphore.h>
@@ -19,7 +21,9 @@
 #include <sys/stat.h>
 #include <sys/types.h>
 #include <time.h>
+
 #include "stuff.h"
+#include "emoji.h"
 
 /* Parameters */
 
@@ -292,7 +296,7 @@ void lscov_report(int use_cur_time) {
   // TODO: calculate error bounds.
   out_append(prev_time, cov, 0, 0);
 
-  ACTF("Recorded new coverage (time: %u, cov: %u)", prev_time, cov); 
+  OKF("Recorded new coverage. (time: %u, cov: %u)", prev_time, cov); 
 }
 
 void lscov_loop() {
@@ -324,8 +328,9 @@ void lscov_loop() {
 }
 
 void lscov_stop(int sig) {
+  ACTF("Terminating lscov...");
   lscov_report(1);
-  OKF("Terminating lscov. Good luck!");
+  OKF("Good luck! %s", random_goody());
 
   exit(0);
 }

### 2024-02-27 lscov/lscov-llvm-pass.so.cc

@@ -21,12 +21,12 @@
 
 using namespace llvm;
 
-class IRTestbed : public PassInfoMixin<IRTestbed> {
+class LSCovPass : public PassInfoMixin<LSCovPass> {
 public:
   PreservedAnalyses run(Module &M, ModuleAnalysisManager &MAM);
 };
 
-PreservedAnalyses IRTestbed::run(Module &M, ModuleAnalysisManager &MAM) {
+PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
   LLVMContext &C = M.getContext();
 
   IntegerType *Int8Ty  = IntegerType::getInt8Ty(C);
@@ -92,11 +92,11 @@ PreservedAnalyses IRTestbed::run(Module &M, ModuleAnalysisManager &MAM) {
 
 extern "C" ::llvm::PassPluginLibraryInfo LLVM_ATTRIBUTE_WEAK
 llvmGetPassPluginInfo() {
-  return {LLVM_PLUGIN_API_VERSION, "IRTestbed", "v0.0",
+  return {LLVM_PLUGIN_API_VERSION, "LSCovPass", "v0.0",
     [](PassBuilder &PB) {
       PB.registerOptimizerLastEPCallback(
         [](ModulePassManager &MPM, OptimizationLevel OL) {
-          MPM.addPass(IRTestbed());
+          MPM.addPass(LSCovPass());
         });
     }};
 }

### 2024-02-27 lscov/emoji.h
lscov: minor

@@ -7,15 +7,12 @@
  */
 
 #pragma once
-
 #include <time.h>
 
 static const char* emoji[] = {
   "( •_•)O*¯`·.¸.·´¯`°Q(•_• )",
   "ʕ •́؈•̀)",
-  "(☝ ՞ਊ ՞)☝",
   "O=('-'Q)",
-  "t(ಠ益ಠt)",
   "(ノಠ益ಠ)ノ彡┻━┻",
   "(=^･ｪ･^=))ﾉ彡☆",
   "ò_ô",
@@ -77,6 +74,6 @@ static const char* emoji[] = {
   "⊂(◉‿◉)つ",
 };
 
-static const char* random_goody() { 
+static const char* random_emoji() { 
   return emoji[time(NULL) % (sizeof(emoji)/sizeof(const char *))];
 }

### 2024-02-27 lscov/lscov-daemon.c

@@ -225,6 +225,11 @@ void bfilter_set_1_by_index(u32 idx) {
 }
 
 u32 bfilter_calc_cardinality() {
+  /* DEBUG: Overhead measuring */
+  struct timespec t1, t2;
+  clock_gettime(CLOCK_MONOTONIC, &t1);
+  /* DEBUG */
+
   /* Tally 1s in the filter. */
   u32 num_1s = 0;
 
@@ -247,7 +252,16 @@ u32 bfilter_calc_cardinality() {
 
   // FIXME: replacing 'log' with a faster one?
   double dividend = log(1.0 - (double)num_1s/(bloom_filter_size << 3));
-  return (u32)(dividend / divisor);
+  u32 cov = (u32)(dividend / divisor);
+
+  /* DEBUG: Overhead measuring */
+  clock_gettime(CLOCK_MONOTONIC, &t2);
+  ACTF("Calculation time: %.5f", 
+      ((double)t2.tv_sec + 1.0e-9 * t2.tv_nsec) - 
+      ((double)t1.tv_sec + 1.0e-9 * t1.tv_nsec)); 
+  /* DEBUG */
+
+  return cov;
 }
 
 void bfilter_init() {
@@ -330,7 +344,7 @@ void lscov_loop() {
 void lscov_stop(int sig) {
   ACTF("Terminating lscov...");
   lscov_report(1);
-  OKF("Good luck! %s", random_goody());
+  OKF("Good luck! %s", random_emoji());
 
   exit(0);
 }

### 2024-02-27 lscov/lscov-daemon.c
lscov: minor

@@ -225,10 +225,11 @@ void bfilter_set_1_by_index(u32 idx) {
 }
 
 u32 bfilter_calc_cardinality() {
-  /* DEBUG: Overhead measuring */
+#ifdef DEBUG
+  /* Overhead measuring */
   struct timespec t1, t2;
   clock_gettime(CLOCK_MONOTONIC, &t1);
-  /* DEBUG */
+#endif
 
   /* Tally 1s in the filter. */
   u32 num_1s = 0;
@@ -254,12 +255,13 @@ u32 bfilter_calc_cardinality() {
   double dividend = log(1.0 - (double)num_1s/(bloom_filter_size << 3));
   u32 cov = (u32)(dividend / divisor);
 
-  /* DEBUG: Overhead measuring */
+#ifdef DEBUG
+  /* Overhead measuring */
   clock_gettime(CLOCK_MONOTONIC, &t2);
-  ACTF("Calculation time: %.5f", 
+  ACTF("Cardinality calculation time: %.5f", 
       ((double)t2.tv_sec + 1.0e-9 * t2.tv_nsec) - 
       ((double)t1.tv_sec + 1.0e-9 * t1.tv_nsec)); 
-  /* DEBUG */
+#endif
 
   return cov;
 }

### 2024-02-27 setup.sh
basic setup script

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+# Install LLVM 15.0.5
+
+LLVM_TAR_NAME=clang+llvm-15.0.5-x86_64-linux-gnu-ubuntu-18.04.tar.xz
+LLVM_URL=https://github.com/llvm/llvm-project/releases/download/llvmorg-15.0.5/$LLVM_TAR_NAME
+
+wget $LLVM_URL
+tar -xvf $LLVM_TAR_NAME llvm
+rm $LLVM_TAR_NAME

### 2024-02-27 setup.sh
fixed setup script

@@ -2,8 +2,11 @@
 
 # Install LLVM 15.0.5
 
-LLVM_TAR_NAME=clang+llvm-15.0.5-x86_64-linux-gnu-ubuntu-18.04.tar.xz
-LLVM_URL=https://github.com/llvm/llvm-project/releases/download/llvmorg-15.0.5/$LLVM_TAR_NAME
+LLVM_URL=https://github.com/llvm/llvm-project/releases/download/llvmorg-15.0.5/clang+llvm-15.0.5-x86_64-linux-gnu-ubuntu-18.04.tar.xz
+LLVM_TAR_NAME=${LLVM_URL##*/}
+
+echo $LLVM_TAR_NAME
+exit
 
 wget $LLVM_URL
 tar -xvf $LLVM_TAR_NAME llvm

### 2024-02-27 testbed/libxml2/SAX2.c
adding a testbed; should be removed eventually

@@ -1,0 +1,2795 @@
+/*
+ * SAX2.c : Default SAX2 handler to build a tree.
+ *
+ * See Copyright for the status of this software.
+ *
+ * Daniel Veillard <daniel@veillard.com>
+ */
+
+
+#define IN_LIBXML
+#include "libxml.h"
+#include <stdlib.h>
+#include <string.h>
+#include <limits.h>
+#include <stddef.h>
+#include <libxml/SAX2.h>
+#include <libxml/xmlmemory.h>
+#include <libxml/tree.h>
+#include <libxml/parser.h>
+#include <libxml/parserInternals.h>
+#include <libxml/valid.h>
+#include <libxml/entities.h>
+#include <libxml/xmlerror.h>
+#include <libxml/debugXML.h>
+#include <libxml/xmlIO.h>
+#include <libxml/uri.h>
+#include <libxml/valid.h>
+#include <libxml/HTMLtree.h>
+
+#include "private/error.h"
+#include "private/parser.h"
+#include "private/tree.h"
+
+#define XML_MAX_URI_LENGTH 2000
+
+/*
+ * xmlSAX2ErrMemory:
+ * @ctxt:  an XML validation parser context
+ * @msg:   a string to accompany the error message
+ */
+static void
+xmlSAX2ErrMemory(xmlParserCtxtPtr ctxt) {
+    xmlCtxtErrMemory(ctxt);
+}
+
+/**
+ * xmlValidError:
+ * @ctxt:  an XML validation parser context
+ * @error:  the error number
+ * @msg:  the error message
+ * @str1:  extra data
+ * @str2:  extra data
+ *
+ * Handle a validation error
+ */
+static void LIBXML_ATTR_FORMAT(3,0)
+xmlErrValid(xmlParserCtxtPtr ctxt, xmlParserErrors error,
+            const char *msg, const xmlChar *str1, const xmlChar *str2)
+{
+    xmlCtxtErr(ctxt, NULL, XML_FROM_DTD, error, XML_ERR_ERROR,
+               str1, str2, NULL, 0, msg, str1, str2);
+    if (ctxt != NULL)
+	ctxt->valid = 0;
+}
+
+/**
+ * xmlFatalErrMsg:
+ * @ctxt:  an XML parser context
+ * @error:  the error number
+ * @msg:  the error message
+ * @str1:  an error string
+ * @str2:  an error string
+ *
[…]

### 2024-02-27 testbed/libxml2/xmlreader.c

@@ -1,0 +1,5612 @@
+/*
+ * xmlreader.c: implements the xmlTextReader streaming node API
+ *
+ * NOTE:
+ *   XmlTextReader.Normalization Property won't be supported, since
+ *     it makes the parser non compliant to the XML recommendation
+ *
+ * See Copyright for the status of this software.
+ *
+ * daniel@veillard.com
+ */
+
+/*
+ * TODOs:
+ *   - XML Schemas validation
+ */
+#define IN_LIBXML
+#include "libxml.h"
+
+#ifdef LIBXML_READER_ENABLED
+#include <string.h> /* for memset() only ! */
+#include <stdarg.h>
+#include <ctype.h>
+#include <stdlib.h>
+
+#include <libxml/xmlmemory.h>
+#include <libxml/xmlIO.h>
+#include <libxml/xmlreader.h>
+#include <libxml/parserInternals.h>
+#ifdef LIBXML_SCHEMAS_ENABLED
+#include <libxml/relaxng.h>
+#include <libxml/xmlschemas.h>
+#endif
+#include <libxml/uri.h>
+#ifdef LIBXML_XINCLUDE_ENABLED
+#include <libxml/xinclude.h>
+#endif
+#ifdef LIBXML_PATTERN_ENABLED
+#include <libxml/pattern.h>
+#endif
+
+#include "private/buf.h"
+#include "private/tree.h"
+#include "private/parser.h"
+#ifdef LIBXML_XINCLUDE_ENABLED
+#include "private/xinclude.h"
+#endif
+
+#ifdef FUZZING_BUILD_MODE_UNSAFE_FOR_PRODUCTION
+/* Keeping free objects can hide memory errors. */
+#define MAX_FREE_NODES 1
+#else
+#define MAX_FREE_NODES 100
+#endif
+
+#ifndef va_copy
+  #ifdef __va_copy
+    #define va_copy(dest, src) __va_copy(dest, src)
+  #else
+    #define va_copy(dest, src) memcpy(dest, src, sizeof(va_list))
+  #endif
+#endif
+
+#define CHUNK_SIZE 512
+/************************************************************************
+ *									*
+ *	The parser: maps the Text Reader API on top of the existing	*
+ *		parsing routines building a tree			*
+ *									*
+ ************************************************************************/
+
+#define XML_TEXTREADER_INPUT	1
+#define XML_TEXTREADER_CTXT	2
+
+typedef enum {
+    XML_TEXTREADER_NONE = -1,
[…]

### 2024-02-28 setup.sh
setup.sh: fixed

@@ -5,9 +5,12 @@
 LLVM_URL=https://github.com/llvm/llvm-project/releases/download/llvmorg-15.0.5/clang+llvm-15.0.5-x86_64-linux-gnu-ubuntu-18.04.tar.xz
 LLVM_TAR_NAME=${LLVM_URL##*/}
 
-echo $LLVM_TAR_NAME
-exit
+if [[ -d llvm ]]; then
+  echo "error: directory 'llvm' already exists."
+  exit
+fi
 
-wget $LLVM_URL
-tar -xvf $LLVM_TAR_NAME llvm
-rm $LLVM_TAR_NAME
+wget $LLVM_URL && \
+  mkdir llvm && \
+  tar -xvf $LLVM_TAR_NAME -C llvm --strip-component 1 && \
+  rm $LLVM_TAR_NAME

### 2024-02-28 lscov/lscov-llvm-pass.so.cc
testbed: small_proj

@@ -6,6 +6,8 @@
  * See "llvm_mode/afl-llvm-pass.so.cc" for the original implementation.
  */
 
+#define USE_COLOR     // Yes, please.
+
 #include "llvm/Bitcode/BitcodeWriter.h"
 #include "llvm/IR/PassManager.h"
 #include "llvm/IR/Module.h"
@@ -34,7 +36,7 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
   IntegerType *Int32Ty = IntegerType::getInt32Ty(C);
 
   /* Show a banner */
-  SAYF(cCYA "lscov-llvm-pass " cBRI VERSION cRST " by <iss300@gmail.com>\n");
+  //SAYF(cCYA "lscov-llvm-pass " cBRI VERSION cRST " by <iss300@gmail.com>\n");
 
   /* Get globals for the SHM region and the previous location */
   GlobalVariable *LSCovMapPtr = new GlobalVariable(
@@ -85,7 +87,7 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
 
   /* Say something nice */
   if (!inst_blocks) WARNF("No instrumentation targets found.");
-  else OKF("Instrumented %u locations.", inst_blocks);
+  else OKF("(lscov) Instrumented %u locations.", inst_blocks);
 
   return PreservedAnalyses::all();
 }

### 2024-02-28 testbed/small_proj/main.c

@@ -1,0 +1,12 @@
+#include <stdio.h>
+
+int main(int argc, char **argv) {
+  if (argc == 1) {
+    printf("yeah");
+    if (argv[0] == "a") 
+      printf("what");
+    else
+      printf("whatup");
+  }
+  return 0;
+}

### 2024-02-28 paper/main.tex
discussion: semantic
lscov-llvm-pass: ignore uncond branches and sancov // lscov-llvm-rt: some reliability issues

@@
 best accuracy among all alternatives (c.f., only 4\% error even in an extreme
-filter density of 90\%) \cite{harmouch2017cardinality}. 
+filter density of 90\%)
+\cite{harmouch2017cardinality,papapetrou2010cardinality}. 
 %, while its error rate is \emph{inversely proportional} to the actual number of
@@
 on the fly and make the behavior abnormal by terminating it. The definition
-allows this as exceptions reference the data context before it is revealed to
-the output.
+allows this because the output is just an observable subset of the data context
+during the execution, which exceptions can reference at runtime.
 

### 2024-02-28 lscov/emoji.h

@@ -11,7 +11,6 @@
 
 static const char* emoji[] = {
   "( •_•)O*¯`·.¸.·´¯`°Q(•_• )",
-  "ʕ •́؈•̀)",
   "O=('-'Q)",
   "(ノಠ益ಠ)ノ彡┻━┻",
   "(=^･ｪ･^=))ﾉ彡☆",
@@ -29,7 +28,6 @@ static const char* emoji[] = {
   "ᕙ(⇀‸↼‶)ᕗ",
   "(๑•́ ヮ •̀๑)",
   "\\_(-_-)_/",
-  "(̿▀̿‿ ̿▀̿ ̿)",
   "(ノ ゜Д゜)ノ ︵ ┻━┻",
   "(ಥ﹏ಥ)",
   "୧༼ಠ益ಠ༽︻╦╤─",
@@ -40,19 +38,14 @@ static const char* emoji[] = {
   "ᕦ(òᴥó)ᕥ",
   "(っ^з^)♪♬",
   "(°o•)",
-  "WHΣИ $HΛLL WΣ †HЯΣΣ MΣΣ† ΛGΛ|И?",
   "＼(＾O＾)／",
   "(⊙＿⊙')",
   "⊙ω⊙",
   "\\( ﾟヮﾟ)/",
-  "(•̀ᴗ•́)و ̑̑",
-  "Yᵒᵘ Oᶰˡʸ Lᶤᵛᵉ Oᶰᶜᵉ",
   "⊹╰(⌣ʟ⌣)╯⊹",
   "[¬º-°]¬",
-  " (̿▀̿ ̿Ĺ̯̿̿▀̿ ̿)̄",
   "(-(-_-(-_(-_(-_-)_-)-_-)_-)_-)-)",
   "(◡_◡)ᕤ",
-  "вєωαяє, ι αм ƒαη¢у!",
   "(ง •̀_•́)ง",
   "ᕙ(`▽´)ᕗ",
   "ᕕ( ᐛ )ᕗ",
@@ -72,6 +65,10 @@ static const char* emoji[] = {
   "(•_•) ( •_•)>⌐■-■ (⌐■_■)",
   "(ㆆ _ ㆆ)",
   "⊂(◉‿◉)つ",
+  "WHΣИ $HΛLL WΣ †HЯΣΣ MΣΣ† ΛGΛ|И?",
+  "вєωαяє, ι αм ƒαη¢у!",
[…]

### 2024-02-28 lscov/lscov-clang.cc

@@ -46,15 +46,16 @@ int main(int argc, char** argv) {
   std::string pass_plugin = "-fpass-plugin=" + _libpath;
   std::string rt_obj = std::string(basepath + "/libLSCovRT.a");
 
-  cc_params[cc_par_cnt++] = (char*)"-lpthread";
   cc_params[cc_par_cnt++] = (char*)"-Xclang";
   cc_params[cc_par_cnt++] = (char*)pass_plugin.c_str();
-  cc_params[cc_par_cnt++] = (char*)rt_obj.c_str();
 
   while (--argc) {
     char* cur = *(++argv);
     cc_params[cc_par_cnt++] = cur;
   }
+
+  cc_params[cc_par_cnt++] = (char*)rt_obj.c_str();
+  cc_params[cc_par_cnt++] = (char*)"-lpthread";
   cc_params[cc_par_cnt] = NULL;
 
   execvp(cc_params[0], (char**)cc_params);

### 2024-02-28 lscov/lscov-daemon.c

@@ -8,7 +8,7 @@
  * Supposed to start before (and run parallely with) a fuzzer.
  */
 
-#define USE_COLOR   // Yes, please.
+#define USE_COLOR     // Yes, please.
 
 #include <fcntl.h>
 #include <math.h>
@@ -27,22 +27,23 @@
 
 /* Parameters */
 
-time_t      tallying_period = 2;          // Tallying period (in seconds) 
+time_t      tallying_period = 2;            // Tallying period (in seconds) 
 u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
 u8          num_hashes = 4;                 // Number of hashes
-const char* out_path = "lscov.out";         // Output path
+const char* out_path = "lscov.csv";         // Output path
 u8          error_percent = 95;             // Error bound (0: disabled)
 
 /* State variables */
 
 s32         shm_hcount_id;        // (SHM) ID for 'hit_count'
 u8*         hit_counts;           // (SHM) Branch hit counts
-sem_t*      sema_rd;
-sem_t*      sema_dr;
+sem_t*      sema_rd;              // (sema) RT to daemon - "que update"
+sem_t*      sema_dr;              // (sema) daemon to RT - "que execution"
+struct timespec loop_timeout;     // 'sema_rd' semaphore timeout
+
 u8*         bloom_filter;         // Bloom filter itself
 time_t      start_time;           // Measurement start time (in unix time)
 time_t      next_tallying_time;   // Next tallying time (in unix time)
-struct timespec loop_timeout;
 
 
 // FIXME: bloom_filter --> limiting caching? other core?
@@ -151,6 +152,7 @@ u32 bfilter_get_hash_index(const u8 *lstate, u32 seed) {
 
   const u8 *key = lstate;
 	const u32 len = LSTATE_SIZE;
+  
   u32 c1 = 0xcc9e2d51;
   u32 c2 = 0x1b873593;
   u32 r1 = 15;
@@ -291,6 +293,8 @@ time_t tally_update_next_time() {
 
   u32 prev_iter_num = (next_tallying_time - start_time) / tallying_period;
   next_tallying_time = start_time + (prev_iter_num + 1) * tallying_period;
+
+  /* Wait at most until the next tallying time. */
   loop_timeout.tv_sec = next_tallying_time;
 
   return prev_next_time;

### 2024-02-28 lscov/lscov-llvm-pass.so.cc

@@ -50,7 +50,18 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
   int inst_blocks = 0;
 
   for (auto &F : M) {
+    /* Dirty hack: if this function has anything to do with 'sancov', ignore. */
+    if (F.getName().contains("sancov"))
+      continue;
+
     for (auto &BB : F) {
+      /* Skip this basic block if it terminates with an unconditional branch. */
+      Instruction *TermI= BB.getTerminator();
+      BranchInst *TermBrI= TermI ? dyn_cast<BranchInst>(TermI) : nullptr;
+      
+      if (TermBrI&& TermBrI->isUnconditional())
+        continue;
+
       BasicBlock::iterator IP = BB.getFirstInsertionPt();
       IRBuilder<> IRB(&(*IP));
 
@@ -87,7 +98,7 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
 
   /* Say something nice */
   if (!inst_blocks) WARNF("No instrumentation targets found.");
-  else OKF("(lscov) Instrumented %u locations.", inst_blocks);
+  else OKF("Instrumented %u locations (lscov, ignoring SANCOV).", inst_blocks);
 
   return PreservedAnalyses::all();
 }

### 2024-02-28 lscov/lscov-llvm-rt.a.c

@@ -34,8 +34,7 @@ void __lscov_init(void) {
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
      daemon, of course. */
 
-  s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 
-      IPC_CREAT | IPC_EXCL | 0600);
+  s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 0600);
 
   if (shm_hcount_id >= 0) {
     __lscov_area_ptr = (u8 *)shmat(shm_hcount_id, NULL, 0);
@@ -71,6 +70,8 @@ void __lscov_init(void) {
 
 __attribute__((destructor(CONST_PRIO))) 
 void __lscov_fin(void) {
-  /* Mark the end of recording, if there was no crash. */
-  sem_post(__lscov_sema_rd);
+  if (__lscov_sema_rd) {
+    /* Mark the end of recording, if there was no crash. */
+    sem_post(__lscov_sema_rd);
+  }
 }

### 2024-02-28 testbed/small_proj/main.c

@@ -1,9 +1,10 @@
 #include <stdio.h>
+#include <string.h>
 
 int main(int argc, char **argv) {
   if (argc == 1) {
     printf("yeah");
-    if (argv[0] == "a") 
+    if (!strcmp(argv[0], "a")) 
       printf("what");
     else
       printf("whatup");

### 2024-02-28 lscov/lscov-clang.cc
lscov-clang: subtle requirement - it shouldn't matter when lscov-pass is called.

@@ -46,14 +46,13 @@ int main(int argc, char** argv) {
   std::string pass_plugin = "-fpass-plugin=" + _libpath;
   std::string rt_obj = std::string(basepath + "/libLSCovRT.a");
 
-  cc_params[cc_par_cnt++] = (char*)"-Xclang";
-  cc_params[cc_par_cnt++] = (char*)pass_plugin.c_str();
-
   while (--argc) {
     char* cur = *(++argv);
     cc_params[cc_par_cnt++] = cur;
   }
 
+  cc_params[cc_par_cnt++] = (char*)"-Xclang";
+  cc_params[cc_par_cnt++] = (char*)pass_plugin.c_str();
   cc_params[cc_par_cnt++] = (char*)rt_obj.c_str();
   cc_params[cc_par_cnt++] = (char*)"-lpthread";
   cc_params[cc_par_cnt] = NULL;

### 2024-02-28 lscov/lscov-daemon.c
checkpt

@@ -27,7 +27,7 @@
 
 /* Parameters */
 
-time_t      tallying_period = 2;            // Tallying period (in seconds) 
+time_t      tallying_period = 10;           // Tallying period (in seconds) 
 u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
 u8          num_hashes = 4;                 // Number of hashes
 const char* out_path = "lscov.csv";         // Output path
@@ -307,6 +307,9 @@ void tally_init() {
 
 
 void lscov_report(int use_cur_time) {
+  if (!start_time)
+    return;
+
   time_t prev_next_time = tally_update_next_time();
   if (use_cur_time)
     prev_next_time = time(NULL);
@@ -317,6 +320,15 @@ void lscov_report(int use_cur_time) {
   out_append(prev_time, cov, 0, 0);
 
   OKF("Recorded new coverage. (time: %u, cov: %u)", prev_time, cov); 
+}
+
+void lscov_wait() {
+  /* Wait for the instrumented binary to report that it started.
+   * We just busy-wait here because nobody is using computation resource in a
+   * meaningful way at this point (and it's cheap for the instrumented binary
+   * to do every execution) */
+  while (*((u32 *)hit_counts) != 0xbadcaffe)
+    continue;
 }
 
 void lscov_loop() {
@@ -370,18 +382,22 @@ void sig_init() {
 
 
 int main(int argc, char** argv) {
-  ACTF("Starting lscov... (v%s)", VERSION);
+  SAYF(cCYA "lscov-daemon v" VERSION cRST " by Gwangmu Lee <iss300@gmail.com>\n");
   
   /* Initialization */
+  ACTF("Initializating...");
   sig_init();
   out_init();
   hcount_init();
   bfilter_init();
-  tally_init();
 
-  OKF("Initialization complete.");
-  ACTF("Recording... (out: %s)", out_path);
+  /* Wait until when a fuzzer starts. */
+  ACTF("Waiting for a fuzzer...");
+  lscov_wait();
+  OKF("Fuzzer started.");
   
   /* Looping... */
+  ACTF("Recording... (out: %s)", out_path);
+  tally_init();
   lscov_loop();
 }

### 2024-02-28 lscov/lscov-llvm-rt.a.c

@@ -63,6 +63,10 @@ void __lscov_init(void) {
 
     /* Wait until SHM is ready */
     sem_wait(__lscov_sema_dr);
+
+    /* Signal the daemon that it's gonna start execution. */
+    *((u32 *)__lscov_area_ptr) = 0xbadcaffe;
+    *((u32 *)__lscov_area_ptr) = 0;
   }
 }
 
@@ -73,5 +77,10 @@ void __lscov_fin(void) {
   if (__lscov_sema_rd) {
     /* Mark the end of recording, if there was no crash. */
     sem_post(__lscov_sema_rd);
+
+    /* Cleanup, if needed. */
+    sem_close(__lscov_sema_rd);
+    sem_close(__lscov_sema_dr);
+    shmdt(__lscov_area_ptr);
   }
 }

### 2024-02-28 lscov/lscov-clang.cc
lscov-llvm-pass: fixed gep bug

@@ -45,6 +45,7 @@ int main(int argc, char** argv) {
   std::string _libpath = std::string(basepath + "/libLSCovPass.so");
   std::string pass_plugin = "-fpass-plugin=" + _libpath;
   std::string rt_obj = std::string(basepath + "/libLSCovRT.a");
+  //std::string rt_obj = std::string(basepath + "/CMakeFiles/LSCovRT.dir/lscov-llvm-rt.a.c.o");
 
   while (--argc) {
     char* cur = *(++argv);

### 2024-02-28 lscov/lscov-daemon.c

@@ -227,7 +227,7 @@ void bfilter_set_1_by_index(u32 idx) {
 }
 
 u32 bfilter_calc_cardinality() {
-#ifdef DEBUG
+#ifdef DEBUG_CARDINALITY_TIME
   /* Overhead measuring */
   struct timespec t1, t2;
   clock_gettime(CLOCK_MONOTONIC, &t1);
@@ -257,7 +257,7 @@ u32 bfilter_calc_cardinality() {
   double dividend = log(1.0 - (double)num_1s/(bloom_filter_size << 3));
   u32 cov = (u32)(dividend / divisor);
 
-#ifdef DEBUG
+#ifdef DEBUG_CARDINALITY_TIME
   /* Overhead measuring */
   clock_gettime(CLOCK_MONOTONIC, &t2);
   ACTF("Cardinality calculation time: %.5f", 
@@ -327,7 +327,7 @@ void lscov_wait() {
    * We just busy-wait here because nobody is using computation resource in a
    * meaningful way at this point (and it's cheap for the instrumented binary
    * to do every execution) */
-  while (*((u32 *)hit_counts) != 0xbadcaffe)
+  while (*hit_counts != 0xff)
     continue;
 }
 
@@ -337,6 +337,9 @@ void lscov_loop() {
 
     /* Update the filter. */
     if (!sem_rd_ret) {
+#ifdef DEBUG_RECEIVE_HCOUNT
+      ACTF("Received new hit counts.");
+#endif
       /* Bucketize the hit counts, making a logic state. */
       static u8* lstate;
       if (!lstate)

### 2024-02-28 lscov/lscov-llvm-pass.so.cc

@@ -77,7 +77,7 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
       /* Load SHM pointer */
       LoadInst *MapPtr = IRB.CreateLoad(Int8PtrTy, LSCovMapPtr);
       MapPtr->setMetadata(M.getMDKindID("nosanitize"), MDNode::get(C, None));
-      Value *MapPtrIdx = IRB.CreateGEP(Int8PtrTy, MapPtr, 
+      Value *MapPtrIdx = IRB.CreateGEP(Int8Ty, MapPtr, 
           IRB.CreateXor(PrevLocCasted, CurLoc));
 
       /* Update bitmap */

### 2024-02-28 lscov/lscov-llvm-rt.a.c

@@ -64,9 +64,10 @@ void __lscov_init(void) {
     /* Wait until SHM is ready */
     sem_wait(__lscov_sema_dr);
 
-    /* Signal the daemon that it's gonna start execution. */
-    *((u32 *)__lscov_area_ptr) = 0xbadcaffe;
-    *((u32 *)__lscov_area_ptr) = 0;
+    /* Signal the daemon that it's gonna start execution.
+     * Let's use one unlikely bit at the beginning. All logic states will have
+     * this bit, so it has zero implication for the coverage. */
+    *__lscov_area_ptr = 0xff;
   }
 }
 
@@ -77,10 +78,5 @@ void __lscov_fin(void) {
   if (__lscov_sema_rd) {
     /* Mark the end of recording, if there was no crash. */
     sem_post(__lscov_sema_rd);
-
-    /* Cleanup, if needed. */
-    sem_close(__lscov_sema_rd);
-    sem_close(__lscov_sema_dr);
-    shmdt(__lscov_area_ptr);
   }
 }

### 2024-02-28 lscov/lscov-daemon.c
lscov-daemon: fixed hashing bug

@@ -31,7 +31,7 @@ time_t      tallying_period = 10;           // Tallying period (in seconds)
 u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
 u8          num_hashes = 4;                 // Number of hashes
 const char* out_path = "lscov.csv";         // Output path
-u8          error_percent = 95;             // Error bound (0: disabled)
+u8          error_percent = 0;              // Error bound (0: disabled)
 
 /* State variables */
 
@@ -78,7 +78,7 @@ static inline int hcount_wait_until_ready() {
 }
 
 void hcount_bucket_to_lstate(u8* lstate) {
-  /* The bucket numbers are one-hot-encoded. In other words, Bucket 3 is encoded
+  /* The bucket numbers are one-hot-encoded. For example, Bucket 3 is encoded
    * as 0x04 (0b00000100). Hit count 0 goes to Bucket 0. Anything else will go
    * to Bucket [log_2(hit_count)] + 1, which is the previous power-of-2 integer
    * interpreted as a one-hot-encoded bit vector. */
@@ -212,7 +212,7 @@ u32 bfilter_get_hash_index(const u8 *lstate, u32 seed) {
   h *= 0xc2b2ae35;
   h ^= (h >> 16);
 
-  return h % len;
+  return h % (bloom_filter_size << 3);
 }
 
 void bfilter_set_1_by_index(u32 idx) {
@@ -226,7 +226,7 @@ void bfilter_set_1_by_index(u32 idx) {
   bloom_filter[byte_idx] |= (1 << bit_idx);
 }
 
-u32 bfilter_calc_cardinality() {
+u32 bfilter_calc_cardinality(u32 *_num_1s) {
 #ifdef DEBUG_CARDINALITY_TIME
   /* Overhead measuring */
   struct timespec t1, t2;
@@ -243,6 +243,9 @@ u32 bfilter_calc_cardinality() {
       _byte >>= 1;
     }
   }
+
+  if (_num_1s)
+    *_num_1s = num_1s;
 
   /* Estimate cardinality. */
   static int has_divisor = 0;
@@ -314,12 +317,13 @@ void lscov_report(int use_cur_time) {
   if (use_cur_time)
     prev_next_time = time(NULL);
 
+  u32 num_1s;
   u32 prev_time = prev_next_time - start_time;
-  u32 cov = bfilter_calc_cardinality(); 
[…]

### 2024-02-29 lscov/lscov-clang.cc
lscov-clang: directly calling wrapped compilers

@@ -17,7 +17,7 @@ int main(int argc, char** argv) {
   int cc_par_cnt = 1;
 
   char _exepath[512];
-  int _len = readlink("/proc/self/exe", _exepath, sizeof(_exepath));
+  int _len = readlink("/proc/self/exe", _exepath, sizeof(_exepath)-1);
   if (_len < 0) {
     std::cerr << "fatal: fail to resolve executable path.\n";
     abort();
@@ -29,11 +29,23 @@ int main(int argc, char** argv) {
   std::string exename = exepath.substr(_name_pos + 1); 
   std::string basepath = exepath.substr(0, _name_pos);
 
-  std::string real_exepath;
+  std::string wrap_exepath;
   if (exename.length() >= 2 && exename.substr(exename.length() - 2) == "++")
-    real_exepath = basepath + "/wrap-clang++";
+    wrap_exepath = basepath + "/wrap-clang++";
   else
-    real_exepath = basepath + "/wrap-clang";
+    wrap_exepath = basepath + "/wrap-clang";
+
+  std::string real_exepath;
+
+  char _buf[1024] = {0};
+  _len = readlink(wrap_exepath.c_str(), _buf, sizeof(_buf)-1);
+  if (_len >= 0) 
+    real_exepath = std::string(_buf);
+  else {
+    std::cerr << "fatal: invalid wrapped CC/CXX path.\n";
+    abort();
+  }
+  
   cc_params[0] = (char*)real_exepath.c_str();
 
   std::string clang_chk = "which " + real_exepath + " >/dev/null 2>&1";

### 2024-03-01 lscov/lscov-daemon.c
lscov-daemon.c, lscov-llvm-rt.a.c, lscov-llvm-pass.so.cc: fixed semaphore bug (initializer priority issue)

@@ -11,6 +11,7 @@
 #define USE_COLOR     // Yes, please.
 
 #include <fcntl.h>
+#include <locale.h>
 #include <math.h>
 #include <semaphore.h>
 #include <signal.h>
@@ -27,11 +28,11 @@
 
 /* Parameters */
 
-time_t      tallying_period = 10;           // Tallying period (in seconds) 
-u32         bloom_filter_size = 0x4000000;  // Bloom filter size (in bytes)
-u8          num_hashes = 4;                 // Number of hashes
-const char* out_path = "lscov.csv";         // Output path
-u8          error_percent = 0;              // Error bound (0: disabled)
+time_t      tallying_period = 10;      // Tallying period (in seconds) 
+u32         bfilter_size = 0x4000000;  // Bloom filter size, in bytes
+u8          num_hashes = 4;            // Number of hashes
+const char* out_path = "lscov.csv";    // Output path
+u8          error_percent = 0;         // Error bound (0: disabled)
 
 /* State variables */
 
@@ -41,12 +42,13 @@ sem_t*      sema_rd;              // (sema) RT to daemon - "que update"
 sem_t*      sema_dr;              // (sema) daemon to RT - "que execution"
 struct timespec loop_timeout;     // 'sema_rd' semaphore timeout
 
-u8*         bloom_filter;         // Bloom filter itself
+u8*         bfilter;              // Bloom filter itself
+u32         bfilter_size_bits;    // Bloom filter size, in bits
 time_t      start_time;           // Measurement start time (in unix time)
 time_t      next_tallying_time;   // Next tallying time (in unix time)
 
 
-// FIXME: bloom_filter --> limiting caching? other core?
+// FIXME: bfilter --> limiting caching? other core?
 
 void out_init() {
   FILE *fout = fopen(out_path, "w");
@@ -136,7 +138,7 @@ void hcount_init() {
   if (sema_rd == (void *)-1) 
     PFATAL("sem_open() for sema_rd failed");
 
[…]

### 2024-03-01 lscov/lscov-llvm-pass.so.cc

@@ -37,6 +37,18 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
 
   /* Show a banner */
   //SAYF(cCYA "lscov-llvm-pass " cBRI VERSION cRST " by <iss300@gmail.com>\n");
+  
+  Function *MainFn = M.getFunction("main");
+  if (MainFn) {
+    FunctionType *VoidVoidFTy = FunctionType::get(Type::getVoidTy(C), false);
+    Value *LSCovInit = M.getOrInsertFunction("__lscov_init", VoidVoidFTy).getCallee();
+
+    BasicBlock &BB = MainFn->getEntryBlock();
+    BasicBlock::iterator IP = BB.getFirstInsertionPt();
+    IRBuilder<> IRB(&(*IP));
+
+    IRB.CreateCall(VoidVoidFTy, LSCovInit);
+  }
 
   /* Get globals for the SHM region and the previous location */
   GlobalVariable *LSCovMapPtr = new GlobalVariable(

### 2024-03-01 lscov/lscov-daemon.c
checkpt

@@ -36,8 +36,13 @@ u8          error_percent = 0;         // Error bound (0: disabled)
 
 /* State variables */
 
-s32         shm_hcount_id;        // (SHM) ID for 'hit_count'
-u8*         hit_counts;           // (SHM) Branch hit counts
+#define HCOUNT_CAP (2)
+
+s32         shm_hcounts_1_id;     // (SHM) ID for 'hit_counts' (1)
+s32         shm_hcounts_2_id;     // (SHM) ID for 'hit_counts' (2)
+u8*         hit_counts_1;         // (SHM) Branch hit counts (1)
+u8*         hit_counts_2;         // (SHM) Branch hit counts (2)
+u8*         hit_counts;           // (SHM) Branch hit counts (current)
 sem_t*      sema_rd;              // (sema) RT to daemon - "que update"
 sem_t*      sema_dr;              // (sema) daemon to RT - "que execution"
 struct timespec loop_timeout;     // 'sema_rd' semaphore timeout
@@ -75,14 +80,14 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 }
 
 
-static inline int hcount_wait_until_ready() {
+static inline int hcounts_wait_until_ready() {
   return sem_timedwait(sema_rd, &loop_timeout);
 }
 
-void hcount_bucket_to_lstate(u8* lstate) {
+void hcounts_bucket_to_lstate(u8* lstate) {
   /* The bucket numbers are one-hot-encoded. For example, Bucket 3 is encoded
-   * as 0x04 (0b00000100). Hit count 0 goes to Bucket 0. Anything else will go
-   * to Bucket [log_2(hit_count)] + 1, which is the previous power-of-2 integer
+   * as 0x04 (0b00000100). Hit counts 0 goes to Bucket 0. Anything else will go
+   * to Bucket [log_2(hit_counts)] + 1, which is the previous power-of-2 integer
    * interpreted as a one-hot-encoded bit vector. */
 
   for (int i = 0; i < LSTATE_SIZE; i++) {
@@ -100,14 +105,23 @@ void hcount_bucket_to_lstate(u8* lstate) {
   }
 }
 
[…]

### 2024-03-01 lscov/lscov-llvm-rt.a.c

@@ -19,6 +19,9 @@
 
 /* Globals for instrumentation */
 
+u8*          __lscov_area_1_ptr;
+u8*          __lscov_area_2_ptr;
+
 u8           __lscov_area_initial[LSTATE_SIZE];
 u8*          __lscov_area_ptr = __lscov_area_initial;
 __thread u32 __lscov_prev_loc;
@@ -41,12 +44,19 @@ void __lscov_init(void) {
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
      daemon, of course. */
 
-  s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 0600);
+  s32 shm_hcount_1_id = shmget(LSCOV_SHM_HCOUNT_1_KEY, LSTATE_SIZE, 0600);
 
-  if (shm_hcount_id >= 0) {
-    __lscov_area_ptr = (u8 *)shmat(shm_hcount_id, NULL, 0);
-    if (__lscov_area_ptr == (void *)-1) 
+  if (shm_hcount_1_id >= 0) {
+    __lscov_area_1_ptr = (u8 *)shmat(shm_hcount_1_id, NULL, 0);
+    if (__lscov_area_1_ptr == (void *)-1) 
       PFATAL("shmat() for hit_count failed");
+
+    s32 shm_hcount_2_id = shmget(LSCOV_SHM_HCOUNT_2_KEY, LSTATE_SIZE, 0600);
+    __lscov_area_2_ptr = (u8 *)shmat(shm_hcount_2_id, NULL, 0);
+    if (__lscov_area_2_ptr == (void *)-1) 
+      PFATAL("shmat() for hit_count failed");
+
+    __lscov_area_ptr = __lscov_area_2_ptr;
 
     /* Initialize semaphores. */
     __lscov_sema_rd = sem_open(LSCOV_SEMA_RD_NAME, 0, 0644, 0);
@@ -70,6 +80,10 @@ void __lscov_init(void) {
 
     /* Wait until SHM is ready */
     sem_wait(__lscov_sema_dr);
+    if (__lscov_area_ptr == __lscov_area_1_ptr)
+      __lscov_area_ptr = __lscov_area_2_ptr;
+    else /* if (__lscov_area_ptr == __lscov_area_2_ptr) */
+      __lscov_area_ptr = __lscov_area_1_ptr;
 
     /* Signal the daemon that it's gonna start execution.
      * Let's use one unlikely bit at the beginning. All logic states will have

### 2024-03-01 lscov/stuff.h

@@ -261,6 +261,7 @@ typedef int64_t  s64;
 
 /* SHM parameters */
 
-#define LSCOV_SHM_HCOUNT_KEY  0xdead
+#define LSCOV_SHM_HCOUNT_1_KEY  0xdead
+#define LSCOV_SHM_HCOUNT_2_KEY  0xbeef
 #define LSCOV_SEMA_RD_NAME    "__lscov_sema_rd" 
 #define LSCOV_SEMA_DR_NAME    "__lscov_sema_dr"

### 2024-03-01 lscov/lscov-daemon.c
lscov-daemon.c, lscov-llvm-rt.a.c: improved (or 'stole') bucketing)

@@ -36,13 +36,8 @@ u8          error_percent = 0;         // Error bound (0: disabled)
 
 /* State variables */
 
-#define HCOUNT_CAP (2)
-
-s32         shm_hcounts_1_id;     // (SHM) ID for 'hit_counts' (1)
-s32         shm_hcounts_2_id;     // (SHM) ID for 'hit_counts' (2)
-u8*         hit_counts_1;         // (SHM) Branch hit counts (1)
-u8*         hit_counts_2;         // (SHM) Branch hit counts (2)
-u8*         hit_counts;           // (SHM) Branch hit counts (current)
+s32         shm_hcount_id;        // (SHM) ID for 'hit_count'
+u8*         hit_counts;           // (SHM) Branch hit counts
 sem_t*      sema_rd;              // (sema) RT to daemon - "que update"
 sem_t*      sema_dr;              // (sema) daemon to RT - "que execution"
 struct timespec loop_timeout;     // 'sema_rd' semaphore timeout
@@ -80,14 +75,53 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 }
 
 
-static inline int hcounts_wait_until_ready() {
+static inline int hcount_wait_until_ready() {
   return sem_timedwait(sema_rd, &loop_timeout);
 }
 
-void hcounts_bucket_to_lstate(u8* lstate) {
+static const u8 count_class_lookup8[256] = {
+  [0]           = 0,
+  [1]           = 1,
+  [2 ... 3]     = 2,
+  [4 ... 7]     = 4,
+  [8 ... 15]    = 8, 
+  [16 ... 31]   = 16,
+  [32 ... 63]   = 32,
+  [64 ... 127]  = 64,
+  [128 ... 255] = 128 
+};
+
+static u16 count_class_lookup16[65536];
+
+static inline void hcount_bucket_to_lstate(u8* lstate) {
+  u32 i = LSTATE_SIZE >> 3;
+  u64 *mem = (u64 *)hit_counts;
+  u64 *dest = (u64 *)lstate;
+
+  while (i--) {
+    /* Optimize for sparse bitmaps. */
+
+    if (unlikely(*mem)) {
+      u16* mem16 = (u16*)mem;
+      u16* dest16 = (u16*)dest;
[…]

### 2024-03-01 lscov/lscov-llvm-rt.a.c

@@ -19,9 +19,6 @@
 
 /* Globals for instrumentation */
 
-u8*          __lscov_area_1_ptr;
-u8*          __lscov_area_2_ptr;
-
 u8           __lscov_area_initial[LSTATE_SIZE];
 u8*          __lscov_area_ptr = __lscov_area_initial;
 __thread u32 __lscov_prev_loc;
@@ -31,6 +28,26 @@ sem_t*       __lscov_sema_dr;
 
 
 /* Initialization (per execution) */
+
+__attribute__((constructor(CONST_PRIO))) 
+void __lscov_iiiiiinit(void) {
+  s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 0600);
+
+  if (shm_hcount_id >= 0) {
+    __lscov_area_ptr = (u8 *)shmat(shm_hcount_id, NULL, 0);
+    if (__lscov_area_ptr == (void *)-1) 
+      PFATAL("shmat() for hit_count failed");
+
+    /* Initialize semaphores. */
+    __lscov_sema_rd = sem_open(LSCOV_SEMA_RD_NAME, 0, 0644, 0);
+    if (__lscov_sema_rd == (void *)-1) 
+      PFATAL("sem_open() for sema_rd failed");
+
+    __lscov_sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
+    if (__lscov_sema_dr == (void *)-1) 
+      PFATAL("sem_open() for sema_dr failed");
+  }
+}
 
 /* Some fuzzers (well, most of them) insert their initializer as a constuctor.
  * What's worse is that they put their initializer at the least priority,
@@ -44,29 +61,7 @@ void __lscov_init(void) {
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
      daemon, of course. */
 
-  s32 shm_hcount_1_id = shmget(LSCOV_SHM_HCOUNT_1_KEY, LSTATE_SIZE, 0600);
-
-  if (shm_hcount_1_id >= 0) {
-    __lscov_area_1_ptr = (u8 *)shmat(shm_hcount_1_id, NULL, 0);
-    if (__lscov_area_1_ptr == (void *)-1) 
-      PFATAL("shmat() for hit_count failed");
-
[…]

### 2024-03-01 lscov/stuff.h

@@ -261,7 +261,11 @@ typedef int64_t  s64;
 
 /* SHM parameters */
 
-#define LSCOV_SHM_HCOUNT_1_KEY  0xdead
-#define LSCOV_SHM_HCOUNT_2_KEY  0xbeef
+#define LSCOV_SHM_HCOUNT_KEY  0xdead
 #define LSCOV_SEMA_RD_NAME    "__lscov_sema_rd" 
 #define LSCOV_SEMA_DR_NAME    "__lscov_sema_dr"
+
+/* Likeliness */
+
+#define unlikely(_x)  __builtin_expect(!!(_x), 0)
+#define likely(_x)  __builtin_expect(!!(_x), 1)

### 2024-03-01 lscov/lscov-daemon.c
checkpt

@@ -10,6 +10,7 @@
 
 #define USE_COLOR     // Yes, please.
 
+#include <assert.h>
 #include <fcntl.h>
 #include <locale.h>
 #include <math.h>
@@ -32,6 +33,7 @@ time_t      tallying_period = 10;      // Tallying period (in seconds)
 u32         bfilter_size = 0x4000000;  // Bloom filter size, in bytes
 u8          num_hashes = 4;            // Number of hashes
 const char* out_path = "lscov.csv";    // Output path
+const char* stat_path = "lsstat.csv";  // Statistics path
 u8          error_percent = 0;         // Error bound (0: disabled)
 
 /* State variables */
@@ -46,6 +48,7 @@ u8*         bfilter;              // Bloom filter itself
 u32         bfilter_size_bits;    // Bloom filter size, in bits
 time_t      start_time;           // Measurement start time (in unix time)
 time_t      next_tallying_time;   // Next tallying time (in unix time)
+u32         last_exec_count;
 
 
 // FIXME: bfilter --> limiting caching? other core?
@@ -62,6 +65,12 @@ void out_init() {
   fclose(fout);
 }
 
+void stat_init() {
+  FILE *fout = fopen(stat_path, "w");
+  fprintf(fout, "Time,Coverage,Density,Rate(ins),Rate(per),Rate(avg)\n");
+  fclose(fout);
+}
+
 void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
   FILE *fout = fopen(out_path, "a");
 
@@ -74,8 +83,20 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
   fclose(fout);
 }
 
+void stat_append(u32 time, u32 cov, float density, u32 rate_ins, 
+    float rate_per, u32 rate_avg) {
+  FILE *fout = fopen(stat_path, "a");
+  fprintf(fout, "%u,%u,%3.2f,%u,%3.2f,%u\n", time, cov, density,
+      rate_ins, rate_per, rate_avg);
+  fclose(fout);
+}
+
 
 static inline int hcount_wait_until_ready() {
+  int _sema_rd_val;
+  sem_getvalue(sema_rd, &_sema_rd_val);
+  if (_sema_rd_val > 1)
+    FATAL("_sema_rd_val: %d", _sema_rd_val);
[…]

### 2024-03-01 lscov/lscov-llvm-rt.a.c

@@ -7,6 +7,7 @@
  * See "llvm_mode/afl-llvm-rt.o.c" for the reference implementation.
  */
 
+#include <assert.h>
 #include <semaphore.h>
 #include <signal.h>
 #include <sys/types.h>
@@ -27,6 +28,16 @@ sem_t*       __lscov_sema_rd;
 sem_t*       __lscov_sema_dr;
 
 
+/* Finalization (per execution) */
+
+__attribute__((destructor(CONST_PRIO))) 
+void __lscov_fin(void) {
+  if (__lscov_sema_rd) {
+    /* Mark the end of recording, if there was no crash. */
+    sem_post(__lscov_sema_rd);
+  }
+}
+
 /* Initialization (per execution) */
 
 __attribute__((constructor(CONST_PRIO))) 
@@ -46,6 +57,11 @@ void __lscov_iiiiiinit(void) {
     __lscov_sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
     if (__lscov_sema_dr == (void *)-1) 
       PFATAL("sem_open() for sema_dr failed");
+
+    /* Signal the daemon that it's gonna start execution.
+     * Let's use one unlikely bit at the beginning. All logic states will have
+     * this bit, so it has zero implication for the coverage. */
+    *__lscov_area_ptr = 0x80;
   }
 }
 
@@ -66,29 +82,13 @@ void __lscov_init(void) {
        crash), mark it finished and let the daemon do its job. This hack will
        make the daemon ignore the very last execution if it was a crash, but
        it's just only *one* execution. */
-    int _sema_rd_val, _sema_dr_val;
-    sem_getvalue(__lscov_sema_rd, &_sema_rd_val);
-    sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
 
-    if (!_sema_dr_val && !_sema_rd_val)
-      sem_post(__lscov_sema_rd);
+    int _sema_dr_val;
+    sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
+    if (_sema_dr_val > 1)
+      FATAL("_sema_dr_val: %d", _sema_dr_val);
 
     /* Wait until SHM is ready */
     sem_wait(__lscov_sema_dr);
-
-    /* Signal the daemon that it's gonna start execution.
-     * Let's use one unlikely bit at the beginning. All logic states will have
-     * this bit, so it has zero implication for the coverage. */
[…]

### 2024-03-01 lscov/lscov-daemon.c
lscov-llvm-rt.a.c, lscov-daemon.c: working crash handling? I guess

@@ -162,7 +162,7 @@ void hcount_bucket_to_lstate(u8* lstate) {
 #endif
 
 void hcount_nuke() {
-  memset(hit_counts, 0, LSTATE_SIZE);
+  memset(hit_counts+1, 0, LSTATE_SIZE-1);
   sem_post(sema_dr);
 }
 

### 2024-03-01 lscov/lscov-llvm-rt.a.c

@@ -35,6 +35,7 @@ void __lscov_fin(void) {
   if (__lscov_sema_rd) {
     /* Mark the end of recording, if there was no crash. */
     sem_post(__lscov_sema_rd);
+    (*__lscov_area_ptr)--;
   }
 }
 
@@ -57,11 +58,6 @@ void __lscov_iiiiiinit(void) {
     __lscov_sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
     if (__lscov_sema_dr == (void *)-1) 
       PFATAL("sem_open() for sema_dr failed");
-
-    /* Signal the daemon that it's gonna start execution.
-     * Let's use one unlikely bit at the beginning. All logic states will have
-     * this bit, so it has zero implication for the coverage. */
-    *__lscov_area_ptr = 0x80;
   }
 }
 
@@ -76,6 +72,10 @@ void __lscov_init(void) {
   /* Same as AFL. If we're running with logic state coverage measurement, attach
      to the appropriate region. SHM_ENV_VAR should be set in the measurement
      daemon, of course. */
+  if (*__lscov_area_ptr > 0x80) {
+    sem_post(__lscov_sema_rd);
+    (*__lscov_area_ptr)--;
+  }
 
   if (__lscov_sema_rd) {
     /* If the destructor was not called in the last execution (e.g., due to a
@@ -90,5 +90,10 @@ void __lscov_init(void) {
 
     /* Wait until SHM is ready */
     sem_wait(__lscov_sema_dr);
+
+    /* Signal the daemon that it's gonna start execution.
+     * Let's use one unlikely bit at the beginning. All logic states will have
+     * this bit, so it has zero implication for the coverage. */
+    *__lscov_area_ptr = 0x81;
   }
 }

### 2024-03-02 lscov/lscov-llvm-pass.so.cc
lscov-llvm-rt.a.c: some cleanups

@@ -41,13 +41,13 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
   Function *MainFn = M.getFunction("main");
   if (MainFn) {
     FunctionType *VoidVoidFTy = FunctionType::get(Type::getVoidTy(C), false);
-    Value *LSCovInit = M.getOrInsertFunction("__lscov_init", VoidVoidFTy).getCallee();
+    Value *LSCovMain = M.getOrInsertFunction("__lscov_main", VoidVoidFTy).getCallee();
 
     BasicBlock &BB = MainFn->getEntryBlock();
     BasicBlock::iterator IP = BB.getFirstInsertionPt();
     IRBuilder<> IRB(&(*IP));
 
-    IRB.CreateCall(VoidVoidFTy, LSCovInit);
+    IRB.CreateCall(VoidVoidFTy, LSCovMain);
   }
 
   /* Get globals for the SHM region and the previous location */

### 2024-03-02 lscov/lscov-llvm-rt.a.c

@@ -35,14 +35,16 @@ void __lscov_fin(void) {
   if (__lscov_sema_rd) {
     /* Mark the end of recording, if there was no crash. */
     sem_post(__lscov_sema_rd);
+
+    /* Mark that it notified this termination to the daemon. */
     (*__lscov_area_ptr)--;
   }
 }
 
-/* Initialization (per execution) */
+/* Initialization (upon starting) */
 
 __attribute__((constructor(CONST_PRIO))) 
-void __lscov_iiiiiinit(void) {
+void __lscov_init(void) {
   s32 shm_hcount_id = shmget(LSCOV_SHM_HCOUNT_KEY, LSTATE_SIZE, 0600);
 
   if (shm_hcount_id >= 0) {
@@ -61,28 +63,31 @@ void __lscov_iiiiiinit(void) {
   }
 }
 
-/* Some fuzzers (well, most of them) insert their initializer as a constuctor.
+/* Initialization (every execution)
+ *
+ * Some fuzzers (well, most of them) insert their initializer as a constuctor.
  * What's worse is that they put their initializer at the least priority,
- * so the forkserver happens before any other initializers. '__lscov_init'
+ * so the forkserver happens before any other initializers. '__lscov_main'
  * CANNOT be one of them because it should wait a semaphore ('__lscov_sema_dr')
- * every execution. Just insert a call to '__lscov_init' at the beginning of
+ * every execution. Just insert a call to '__lscov_main' at the beginning of
  * 'main' and that'll defeat all initializers. M-hwa-hwa-hwa. */
-//__attribute__((constructor(CONST_PRIO))) 
-void __lscov_init(void) {
-  /* Same as AFL. If we're running with logic state coverage measurement, attach
-     to the appropriate region. SHM_ENV_VAR should be set in the measurement
-     daemon, of course. */
-  if (*__lscov_area_ptr > 0x80) {
-    sem_post(__lscov_sema_rd);
-    (*__lscov_area_ptr)--;
-  }
+
+void __lscov_main(void) {
+  /* Similar to AFL, if we're running with logic state coverage measurement,
+   * attach to the appropriate region. */
 
   if (__lscov_sema_rd) {
     /* If the destructor was not called in the last execution (e.g., due to a
-       crash), mark it finished and let the daemon do its job. This hack will
-       make the daemon ignore the very last execution if it was a crash, but
-       it's just only *one* execution. */
[…]

### 2024-03-02 lscov/lscov-daemon.c
lscov-llvm-rt.a.c: some cleanups // lscov-daemon.c: sem_unlink() for exceptional start

@@ -95,24 +95,25 @@ void stat_append(u32 time, u32 cov, float density, u32 rate_ins,
 static inline int hcount_wait_until_ready() {
   int _sema_rd_val;
   sem_getvalue(sema_rd, &_sema_rd_val);
-  if (_sema_rd_val > 1)
+  if (_sema_rd_val > 1) {
+    assert(0 && "_sema_rd_val > 1");
     FATAL("_sema_rd_val: %d", _sema_rd_val);
+  }
   return sem_timedwait(sema_rd, &loop_timeout);
 }
 
-static const u8 count_class_lookup8[256] = {
-  [0]           = 0,
-  [1]           = 1,
-  [2 ... 3]     = 2,
-  [4 ... 7]     = 4,
-  [8 ... 15]    = 8, 
-  [16 ... 31]   = 16,
-  [32 ... 63]   = 32,
-  [64 ... 127]  = 64,
-  [128 ... 255] = 128 
+/* Bucketing excerpted from AFL. It was much faster than my implementation,
+ * unsurprisingly */
+
+/* Bucket = log2(log4(hit_count)+1) */
+static const u8 count_bucket_lookup8[256] = {
+  [0]           = 0,    // No hit
+  [1 ... 3]     = 1,    // Hit
+  [4 ... 63]    = 2,    // Revisit
+  [64 ... 255]  = 4,    // Repetition
 };
 
-static u16 count_class_lookup16[65536];
+static u16 count_bucket_lookup16[65536];
 
 static inline void hcount_bucket_to_lstate(u8* lstate) {
   u32 i = LSTATE_SIZE >> 3;
@@ -125,41 +126,16 @@ static inline void hcount_bucket_to_lstate(u8* lstate) {
     if (unlikely(*mem)) {
       u16* mem16 = (u16*)mem;
       u16* dest16 = (u16*)dest;
-      dest16[0] = count_class_lookup16[mem16[0]];
-      dest16[1] = count_class_lookup16[mem16[1]];
-      dest16[2] = count_class_lookup16[mem16[2]];
-      dest16[3] = count_class_lookup16[mem16[3]];
+      dest16[0] = count_bucket_lookup16[mem16[0]];
+      dest16[1] = count_bucket_lookup16[mem16[1]];
+      dest16[2] = count_bucket_lookup16[mem16[2]];
[…]

### 2024-03-02 lscov/lscov-llvm-rt.a.c

@@ -28,17 +28,32 @@ sem_t*       __lscov_sema_rd;
 sem_t*       __lscov_sema_dr;
 
 
+void __lscov_end_exec() {
+  /* Mark that it notified this termination to the daemon. */
+  *__lscov_area_ptr = 0x80;
+
+  /* Mark the end of recording, if there was no crash. */
+  int _sema_rd_val;
+  sem_getvalue(__lscov_sema_rd, &_sema_rd_val);
+  if (_sema_rd_val)
+    assert(0 && "non-zero _sema_rd_val");
+  sem_post(__lscov_sema_rd);
+}
+
+void __lscov_start_exec() {
+  /* Wait until SHM is ready */
+  sem_wait(__lscov_sema_dr);
+
+  /* Mark this hit count as unnotified yet to the daemon (0x01). */
+  *__lscov_area_ptr = 0x81;
+}
+
 /* Finalization (per execution) */
 
 __attribute__((destructor(CONST_PRIO))) 
 void __lscov_fin(void) {
-  if (__lscov_sema_rd) {
-    /* Mark the end of recording, if there was no crash. */
-    sem_post(__lscov_sema_rd);
-
-    /* Mark that it notified this termination to the daemon. */
-    (*__lscov_area_ptr)--;
-  }
+  if (__lscov_sema_rd) 
+    __lscov_end_exec();
 }
 
 /* Initialization (upon starting) */
@@ -60,6 +75,11 @@ void __lscov_init(void) {
     __lscov_sema_dr = sem_open(LSCOV_SEMA_DR_NAME, 0, 0644, 0);
     if (__lscov_sema_dr == (void *)-1) 
       PFATAL("sem_open() for sema_dr failed");
+
+    /* Signal the daemon to start an execution. For convenience's sake, just use
+     * one unlikely bit at the beginning. All logic states will have this bit,
+     * so it has zero implication for the coverage. */
+    *__lscov_area_ptr = 0x80;
   }
 }
 
@@ -82,24 +102,22 @@ void __lscov_main(void) {
      * make the daemon ignore the very last execution if it was a crash, but
      * it's just only *one* execution. */
 
-    if (*__lscov_area_ptr > 0x80) {
-      sem_post(__lscov_sema_rd);
-      (*__lscov_area_ptr)--;
-    }
+    if (*__lscov_area_ptr > 0x80) 
+      __lscov_end_exec();
 
-    /* Sanity check. Should be a lock-step. */
[…]

### 2024-03-03 lscov/lscov-daemon.c
lscov-daemon.c: restored to log2 bucketing

@@ -105,13 +105,33 @@ static inline int hcount_wait_until_ready() {
 /* Bucketing excerpted from AFL. It was much faster than my implementation,
  * unsurprisingly */
 
-/* Bucket = log2(log4(hit_count)+1) */
+//#define BUCKET_1
+
+#ifdef BUCKET_1
+static const u8 count_bucket_lookup8[256] = {
+  [0]           = 0,
+  [1 ... 255]   = 1,
+};
+#elif defined BUCKET_LOG2_LOG4
 static const u8 count_bucket_lookup8[256] = {
   [0]           = 0,    // No hit
   [1 ... 3]     = 1,    // Hit
   [4 ... 63]    = 2,    // Revisit
   [64 ... 255]  = 4,    // Repetition
 };
+#else // BUCKET_LOG2
+static const u8 count_bucket_lookup8[256] = {
+  [0]           = 0,    // No hit
+  [1]           = 1,    // Hit
+  [2 ... 3]     = 2,    
+  [4 ... 7]     = 4,    
+  [8 ... 15]    = 8,    
+  [16 ... 31]   = 16,    
+  [32 ... 63]   = 32,    
+  [64 ... 127]  = 64,   // Repetition
+  [128 ... 255] = 128,
+};
+#endif
 
 static u16 count_bucket_lookup16[65536];
 

### 2024-03-03 paper/main.tex
interestingness: removed 1/n remark
paper: revised interestingness

@@
 (i) investigating as many \emph{new} program behaviors as possible and (ii)
-keeping the new behaviors \emph{more interesting} (i.e., more likely revealing
-unknown abnormal behaviors).
+keeping the mutation base input \emph{interesting} (i.e., more likely revealing
+unknown abnormal behaviors after mutation).
+
+\pp{New vs. unknown behaviors}
+%
+We first make a clear distinction between \emph{new} and \emph{unknown} 
+behaviors. \emph{New} behaviors are, as the name suggests, simply the behaviors 
+that have not been observed until now. On the other hand, \emph{unknown}
+behaviors are a subset of the \emph{new} behaviors \emph{not equivalent} to any
+observed behaviors. In particular, an abnormal behavior is \emph{unknown} if it
+is not equivalent to any observed abnormal behaviors (e.g., a unique root
+cause). Formally, if $\mathrm{U}$ and $\mathrm{N}$ are the sets of
+\underline{\textbf{u}}nknown and \underline{\textbf{n}}ew behaviors,
+respectively, $\mathrm{U} \subset \mathrm{N}$.
 
@@
 %
-The approach can be described formally as follows. Let the
-\emph{interestingness} of a program behavior be $P(\mathrm{abnormal})$, the
-expectation of a certain program behavior being abnormal before observing
-it.\footnote{See \autoref{s:disc} for the compatibility of this definition and
-the conventional meaning of interestingness in untargeted fuzzing.} Furthermore,
-let $P(\mathrm{new})$ be the probability of a new behavior in the next
-execution.  Then, the probability of discovering unknown abnormal behavior in
-the next execution is
-%
-\begin{equation}
-  P(\mathrm{new} \cap \mathrm{abnormal}) = P(\mathrm{new}) \times P(\mathrm{abnormal} \mid \mathrm{new}).
-\end{equation}
-
-In this formulation, untargeted fuzzing attempts to (i) increase
-$P(\mathrm{new})$ to investigate more program behaviors while (ii) keep 
-$P(\mathrm{abnormal} \mid \mathrm{new})$ as high as possible to ensure new
-behaviors interesting.
-%
-Notice that executing more inputs is not the same as observing more distinct
-behaviors, as inputs can exhibit the same behavior (e.g., the same
-early-termination).
+The approach of untargeted fuzzing can be described formally as follows. Upon
+executing a mutated input, let $P(\mathrm{N})$ be the probability of observing a
+\underline{\textbf{n}}ew behavior as a result of execution. Then, the
+probability of discovering \underline{\textbf{u}}nknown
+\underline{\textbf{a}}bnormal behavior $P(\mathrm{UA}) := P(\mathrm{U} \cap
+\mathrm{A})$ is
+%
+\begin{align}
+  P(\mathrm{UA}) 
+      &= P(\mathrm{N} \cap \mathrm{UA}) \tag{by $\mathrm{U} \subset \mathrm{N}$} \\
+      &= P(\mathrm{N}) \times P(\mathrm{UA} \mid \mathrm{N}) \tag{by chain rule}. 
+\end{align}
+
+Here, the second term $P(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
+revealing an unknown abnormal behavior given a new behavior, which can be
+interpreted as the \emph{interestingness} of the mutation base. In other words,
+untargeted fuzzing attempts to (i) increase $P(\mathrm{N})$ to investigate more
+program behaviors while (ii) keeping the interestingness $P(\mathrm{UA} \mid
+\mathrm{N})$ as high as possible.
+%
+%Notice that executing more inputs is not the same as observing more distinct
+%behaviors, as inputs can exhibit the same behavior (e.g., the same
+%early-termination).
 
@@
 %
-As the interestingness $P(\mathrm{abnormal})$ depends on the expectation of an
-\emph{unobserved} behavior, there is no direct way to measure or formalize
-interestingness. However, the practice of untargeted fuzzing in recent years
-suggests that abnormal behaviors get increasingly unlikely to require a
-larger number of branch hit.
-%
-The prime example is the branch hit count bucketing in AFL \cite{afl}, where the
-bucket size gets larger roughly by the power of 2 (i.e., 1, 2, 3, 4-7, 8-15,
-...).
+As the interestingness $P(\mathrm{UA} \mid \mathrm{N})$ is the expectation of an
+\emph{unobserved} behavior, there is no direct way to measure interestingness. 
+%
+However, the practice of untargeted fuzzing suggests that
+the resulting program behavior is unlikely to be \emph{unknown abnormal} if the
+mutation base is highly repetitive, as it commonly incorporates corpus
+minimization \cite{} and branch hit count buckets \cite{}.
+%
+The rationales are: (i) abnormal behaviors might have been already observed with
+fewer branch repetitions (i.e., unlikely \emph{abnormal}) and (ii) if so, it may
+correspond to pre-observed less-repetition counterparts (i.e., unlikely
+\emph{unknown}).
+
+%The prime example is the branch hit count bucketing in AFL \cite{afl}, where
+%the bucket size gets larger roughly by the power of 2 (i.e., 1, 2, 3, 4-7,
+%8-15, ...).
+
+%However, the practice of untargeted fuzzing in recent years suggests that
+%abnormal behaviors get increasingly unlikely to require a larger number of
+%branch hit.
+%
+%The prime example is the branch hit count bucketing in AFL \cite{afl}, where
+%the bucket size gets larger roughly by the power of 2 (i.e., 1, 2, 3, 4-7,
+%8-15, ...).
 %; all hit counts are treated the same within a bucket.
@@
 
-To formalize this, let $X=n$ denote when a program behavior takes a 
-branch $X$ $n$ times ($n \ge 1$). Then, the interestingness of a program
-behavior when $X=n$ is;
-%
-\begin{equation}
-  P(\mathrm{abnormal} \mid X=n) \propto 1/n.
-\end{equation}
+%To formalize this, let $X=n$ denote when a program behavior takes a 
+%branch $X$ $n$ times ($n \ge 1$). Then, the interestingness of a program
+%behavior when $X=n$ is;
+%%
+%\begin{equation}
+%  P(\mathrm{abnormal} \mid X=n) \propto 1/n.
+%\end{equation}
 

### 2024-03-03 paper/main.tex
paper: de-bucketing..

@@
 coverage} as a feasible proxy metric of interesting behaviors. A logic state is
-a set of all satisfied branches during one execution, bucketed by their hit
-counts (larger buckets for higher hit counts). Logic state coverage then
-\emph{individually counts} all observed distinct logic states.  One logic state
-represents \emph{fewer} program behaviors if they are \emph{more interesting}
-(i.e., likely relating to unknown abnormal behaviors), meaning that observing
-more interesting behaviors is strongly reflected on larger logic state coverage.
+a set of all satisfied branches during one execution, where logic state coverage
+is defined as the \emph{individual count} of all observed distinct logic states.
+One logic state represents \emph{fewer} behaviors if they are \emph{more
+interesting} (i.e., likely relating to unknown abnormal behaviors), meaning that
+observing more interesting behaviors is strongly reflected on larger logic state
+coverage.
 
@@
 mutation base is highly repetitive, as it commonly incorporates corpus
-minimization \cite{} and branch hit count buckets \cite{}.
+minimization \cite{todo} and branch hit count buckets \cite{todo}.
 %
@@
 \emph{unknown}).
-
-%The prime example is the branch hit count bucketing in AFL \cite{afl}, where
-%the bucket size gets larger roughly by the power of 2 (i.e., 1, 2, 3, 4-7,
-%8-15, ...).
 
@@
 A \emph{logic state} $l$ is a set of all satisfied branches during execution,
-each of which is paired with the integer logarithm of the corresponding branch
-hit count. Formally, given a branch history $\mathcal{T}_b$ of an execution,
+which is essentially the order-ignored version of a branch history. Formally,
+given a branch history $\mathcal{T}_b$ of an execution,
 %
@@
 \label{e:ls}
-  l := \{(b, n(b)) \mid b \in \mathcal{T}_b\},
+  l := \{b \mid b \in \mathcal{T}_b\},
 \end{equation}
-
-\noindent where $n(b) = \lfloor \log_2{m(b)} \rfloor$ and $m(b)$ is the hit
-count of a branch $b$ in $\mathcal{T}_b$.  Notice that, as it gets larger, a
-branch hit count $m(b)$ shares the same integer "bucket" $n(b)$ with
-exponentially more hit counts (i.e., $n(b)=x \iff m(b) \in \{2^x, ...,
-2^{x+1}-1\}$).
 
@@
 single covered logic state may encompass several different behaviors. However,
-in \autoref{s:prop}, we argue that a logic state is representative of
-interesting program behaviors as it (i) weighs interesting program behaviors
-over uninteresting ones and (ii) only contains the program behaviors of the same
-normality.
+in \autoref{s:prop}, we explain that a logic state is representative of
+interesting program behaviors as it (i) reflects the interestingness of
+underlying program behaviors and (ii) only contains the program behaviors of the
+same normality.
 

### 2024-03-03 paper/main.tex
paper: de-bucketed

@@
   (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
-  of the branch $b$. Dotted lines demarcate the start of a new power-of-2 branch
-  hit count.}
+  of the branch $b$. Dotted lines demarcate whether the corresponding branch is
+  hit or not (i.e., presence in a logic state).}
   % Each region surrounded by dotted lines constitutes one logic state.}
@@
 
-Logic states distinguish the program behaviors with smaller branch hit counts
-in finer details (i.e., distinguishing \emph{interesting} behaviors) but
-coalesce the behaviors with larger hit counts (i.e., avoiding
-over-representation of \emph{uninteresting} behaviors). This results in a larger
-number of covered logic states (i.e., larger logic state coverage) when the
-observed program behaviors are more interesting.
+Logic states distinguish the program behaviors with less branch repetitions in a
+finer granularity, resulting in a higher number of covered logic states (i.e.,
+larger coverage) as the observed program behaviors are more interesting.
 
@@
 program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
-count of the branch $b$. For example, there are 
-two possible program behaviors, $b_2$ after $b_1$ or $b_1$ after
-$b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
+count of the branch $b$. For example, there are two possible program behaviors,
+$b_2$ after $b_1$ or $b_1$ after $b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
 %Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
 %
-The dotted lines demarcate the beginning of a new power-of-2 branch hit count
-(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
-bucket. Each region surrounded by dotted lines constitutes \emph{one logic
-state}, as all contained program behaviors fall into the same integer bucket
-in every branch.
-
-%Notice that a program behavior is deemed more interesting as it exhibits
-%smaller branch hit counts (\autoref{s:fuzz:unfuzz}). 
-As shown, a logic state distinguishes more interesting program behaviors in a
-finer granularity, representing fewer behaviors with smaller branch hit counts
-(i.e., bottom left). On the other hand, it coalesces more behaviors when
-the branch hit counts get larger, where individual behaviors are deemed less
-interesting. 
-%
-This results in a larger number of covered logic states when the observed
-behaviors are more interesting (e.g., three program behaviors result in
-three different logic states when $m(b_3)<2$) while the opposite happens when
-they are not (e.g., a total of 11,950 behaviors fall into \emph{one} logic state
-when $4 \le m(b_1) < 8$ and $4 \le m(b_2) < 8$).
-
-%\autoref{f:repr} reveals two important properties of logic states. First, a
-%logic state distinguishes interesting program behaviors with smaller branch hit
-%counts in a finer granularity. For example, a logic state represents
-%exponentially fewer program behaviors as $m(b_1)$ and $m(b_2)$ approach to 1.
-%Second, a logic state coalesces less interesting program behaviors that require
-%high branch hit counts or exhibit specific branch ordering, avoiding
-%over-representation of them. For example, all 11,950 program behaviors
-%exhibiting different branch ordering with $4 \le m(A) \le 7$ and $4 \le m(B) \le
-%7$ are lumped into \emph{one} logic state.
+The dotted lines demarcate whether the corresponding branch is hit or not, which
+also corresponds to the presence of the branch in a logic state.
+%the beginning of a new power-of-2 branch hit count
+%(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
+%bucket. 
+The surrounded region has the same set of satisfied branches, constituting
+\emph{one logic state}.
+
+As shown, the program behaviors with more repetitive branches are grouped with
+more program behaviors as one logic state.  For example, a program behavior
+having only one repetitive branch (either $b_1$ or $b_2$) falls into the slim
+logic states adjacent to axis (bottom right and top left), while a behavior
+having two repetitive branches (both $b_1$ and $b_2$) falls into the large logic
+state (top right). This results in observing repetitive (i.e., less interesting)
+program states represented by fewer logic states, leading to smaller logic state
+coverage.
+
+%%Notice that a program behavior is deemed more interesting as it exhibits
+%%smaller branch hit counts (\autoref{s:fuzz:unfuzz}). 
+%As shown, a logic state distinguishes more interesting program behaviors in a
+%finer granularity, representing fewer behaviors with smaller branch hit counts
+%(i.e., bottom left). On the other hand, it coalesces more behaviors when
+%the branch hit counts get larger, where individual behaviors are deemed less
+%interesting. 
+%%
+%This results in a larger number of covered logic states when the observed
+%behaviors are more interesting (e.g., three program behaviors result in
+%three different logic states when $m(b_3)<2$) while the opposite happens when
+%they are not (e.g., a total of 11,950 behaviors fall into \emph{one} logic state
+%when $4 \le m(b_1) < 8$ and $4 \le m(b_2) < 8$).
 
@@
 \autoref{f:design} illustrates the workflow of logic state coverage
-measurement. Similar to edge coverage, it first records and buckets the branch
-hit counts of every execution, yielding a \emph{logic state} as a result 
-(\autoref{s:design:rec}). Then, it adds the recorded logic state to a 
-\emph{bloom filter} that represents a set of observed logic states, by setting
-the hash indices (\autoref{s:design:up}).  Finally, the measurement periodically
-reads off the bloom filter to count the number of observed logic states
-(\autoref{s:design:count}).
+measurement. Similar to edge coverage, it first records the \emph{logic state}
+of each execution via instrumentation (\autoref{s:design:rec}). Then, it adds
+the recorded logic state to a \emph{bloom filter} that represents a set of
+observed logic states, by setting the hash indices (\autoref{s:design:up}).
+Finally, the measurement periodically reads off the bloom filter to count the
+number of observed logic states (\autoref{s:design:count}).
 

### 2024-03-03 paper/main.tex
paper: pass

@@
   In this work, we propose \emph{logic state coverage} as a proxy metric to
-  count observed interesting behaviors. A logic state distinguishes interesting
-  behaviors in a finer granularity than the less interesting ones, making the
-  amount of logic state coverage (i.e., observed logic states) directly
+  count observed interesting behaviors. A logic state is a set of satisfied
+  branches during one execution, where logic state coverage is the count of
+  \emph{individual} observed logic states during a fuzzing campaign. A logic
+  state distinguishes less repetitive (i.e., more interesting) behaviors in a
+  finer granularity, making the amount of logic state coverage reliably 
   proportional to the number of observed interesting behaviors.
@@
 a set of all satisfied branches during one execution, where logic state coverage
-is defined as the \emph{individual count} of all observed distinct logic states.
-One logic state represents \emph{fewer} behaviors if they are \emph{more
-interesting} (i.e., likely relating to unknown abnormal behaviors), meaning that
-observing more interesting behaviors is strongly reflected on larger logic state
+is the \emph{individual count} of all observed distinct logic states during a
+fuzzing campaign. Logic states represent more \emph{interesting} behaviors
+(i.e., relating to unknown abnormal behaviors) in a finer granularity, meaning
+that observing more interesting behaviors is reliably reflected to larger
 coverage.
@@
 that have not been observed until now. On the other hand, \emph{unknown}
-behaviors are a subset of the \emph{new} behaviors \emph{not equivalent} to any
-observed behaviors. In particular, an abnormal behavior is \emph{unknown} if it
-is not equivalent to any observed abnormal behaviors (e.g., a unique root
-cause). Formally, if $\mathrm{U}$ and $\mathrm{N}$ are the sets of
+behaviors are a subset of the \emph{new} behaviors that are \emph{not
+equivalent} to any observed behaviors. In particular, an abnormal behavior is
+\emph{unknown} if it is not equivalent to any observed abnormal behaviors (e.g.,
+a unique root cause). Formally, if $\mathrm{U}$ and $\mathrm{N}$ are the sets of
 \underline{\textbf{u}}nknown and \underline{\textbf{n}}ew behaviors,
-respectively, $\mathrm{U} \subset \mathrm{N}$.
+$\mathrm{U} \subset \mathrm{N}$.
 
@@
 %
-The approach of untargeted fuzzing can be described formally as follows. Upon
+The approach of untargeted fuzzing can be formally described as follows. Upon
 executing a mutated input, let $P(\mathrm{N})$ be the probability of observing a
@@
 the resulting program behavior is unlikely to be \emph{unknown abnormal} if the
-mutation base is highly repetitive, as it commonly incorporates corpus
+mutation base is highly repetitive, as fuzzers commonly incorporate corpus
 minimization \cite{todo} and branch hit count buckets \cite{todo}.
 %
-The rationales are: (i) abnormal behaviors might have been already observed with
-fewer branch repetitions (i.e., unlikely \emph{abnormal}) and (ii) if so, it may
-correspond to pre-observed less-repetition counterparts (i.e., unlikely
-\emph{unknown}).
+The rationales are: (i) if a fewer repetition was normal, more repetition is
+also likely normal (i.e., unlikely \emph{abnormal}) and (ii) even if it was
+abnormal, it may correspond to pre-observed less-repetition counterparts (i.e.,
+unlikely \emph{unknown}).
 
@@
 states during fuzzing}, where a logic state is called \emph{covered} when
-fuzzing observed a program behavior from the logic state (i.e., triggering all
-and only the branches in the logic state). 
+fuzzing observed a program behavior that belongs to such a logic state (i.e.,
+triggering all and only the branches in the logic state). 
 %

### 2024-03-04 lscov/lscov-daemon.c
lscov-daemon.c: fixed a nasty bug in buckting

@@ -105,14 +105,19 @@ static inline int hcount_wait_until_ready() {
 /* Bucketing excerpted from AFL. It was much faster than my implementation,
  * unsurprisingly */
 
-//#define BUCKET_1
-
+#ifdef LSCOV_BUCKET
 #ifdef BUCKET_1
 static const u8 count_bucket_lookup8[256] = {
   [0]           = 0,
   [1 ... 255]   = 1,
 };
-#elif defined BUCKET_LOG2_LOG4
+#elif defined BUCKET_LOG2_LOG3p2
+static const u8 count_bucket_lookup8[256] = {
+  [0]           = 0,    // No hit
+  [1 ... 8]     = 1,    // Hit
+  [9 ... 255]   = 2,    // Repetition
+};
+#elif defined BUCKET_LOG2_LOG4p1_p1
 static const u8 count_bucket_lookup8[256] = {
   [0]           = 0,    // No hit
   [1 ... 3]     = 1,    // Hit
@@ -134,8 +139,10 @@ static const u8 count_bucket_lookup8[256] = {
 #endif
 
 static u16 count_bucket_lookup16[65536];
+#endif
 
 static inline void hcount_bucket_to_lstate(u8* lstate) {
+#ifdef LSCOV_BUCKET
   u32 i = LSTATE_SIZE >> 3;
   u64 *mem = (u64 *)hit_counts;
   u64 *dest = (u64 *)lstate;
@@ -150,11 +157,16 @@ static inline void hcount_bucket_to_lstate(u8* lstate) {
       dest16[1] = count_bucket_lookup16[mem16[1]];
       dest16[2] = count_bucket_lookup16[mem16[2]];
       dest16[3] = count_bucket_lookup16[mem16[3]];
+    } else {
+      *dest = 0;
     }
 
     mem++;
     dest++;
   }
+#else
+  memcpy(lstate, hit_counts, LSTATE_SIZE);
+#endif
 }
 
 void hcount_nuke() {
@@ -204,12 +216,14 @@ void hcount_init() {
   /* Initialize 'hit_counts'. */
   memset(hit_counts, 0, LSTATE_SIZE);
 
+#ifdef LSCOV_BUCKET
   /* Initialize 'count_bucket_lookup16' */
   for (u32 b1 = 0; b1 < 256; b1++) 
     for (u32 b2 = 0; b2 < 256; b2++)
       count_bucket_lookup16[(b1 << 8) + b2] = 
[…]

### 2024-03-04 lscov/lscov-llvm-pass.so.cc

@@ -92,12 +92,19 @@ PreservedAnalyses LSCovPass::run(Module &M, ModuleAnalysisManager &MAM) {
       Value *MapPtrIdx = IRB.CreateGEP(Int8Ty, MapPtr, 
           IRB.CreateXor(PrevLocCasted, CurLoc));
 
+#ifdef LSCOV_BUCKET
       /* Update bitmap */
       LoadInst *Counter = IRB.CreateLoad(Int8Ty, MapPtrIdx);
       Counter->setMetadata(M.getMDKindID("nosanitize"), MDNode::get(C, None));
       Value *Incr = IRB.CreateAdd(Counter, ConstantInt::get(Int8Ty, 1));
       IRB.CreateStore(Incr, MapPtrIdx)
           ->setMetadata(M.getMDKindID("nosanitize"), MDNode::get(C, None));
+#else
+      /* Set bitmap */
+      Constant *ConstOne = ConstantInt::get(Int8Ty, 1);
+      IRB.CreateStore(ConstOne, MapPtrIdx)
+          ->setMetadata(M.getMDKindID("nosanitize"), MDNode::get(C, None));
+#endif
 
       /* Set prev_loc to cur_loc >> 1 */
       StoreInst *Store =

### 2024-03-04 lscov/lscov-llvm-rt.a.c

@@ -32,20 +32,23 @@ void __lscov_end_exec() {
   /* Mark that it notified this termination to the daemon. */
   *__lscov_area_ptr = 0x80;
 
-  /* Mark the end of recording, if there was no crash. */
   int _sema_rd_val;
   sem_getvalue(__lscov_sema_rd, &_sema_rd_val);
-  if (_sema_rd_val)
+  if (_sema_rd_val) {
+    SAYF("_sema_rd_val: %d\n", _sema_rd_val);
     assert(0 && "non-zero _sema_rd_val");
+  }
+
+  /* Mark the end of recording. */
   sem_post(__lscov_sema_rd);
 }
 
 void __lscov_start_exec() {
-  /* Wait until SHM is ready */
-  sem_wait(__lscov_sema_dr);
-
   /* Mark this hit count as unnotified yet to the daemon (0x01). */
   *__lscov_area_ptr = 0x81;
+
+  /* Wait until SHM is ready */
+  sem_wait(__lscov_sema_dr);
 }
 
 /* Finalization (per execution) */

### 2024-03-04 lscov/stuff.h

@@ -269,3 +269,8 @@ typedef int64_t  s64;
 
 #define unlikely(_x)  __builtin_expect(!!(_x), 0)
 #define likely(_x)  __builtin_expect(!!(_x), 1)
+
+/* Use buckets? */
+
+//#define LSCOV_BUCKET
+#define BUCKET_1

### 2024-03-04 paper/main.tex

@@
   To establish a more reliable quality metric, we first note that fuzzing 
-  aims to reduce the number of unknown \emph{abnormal} behaviors by observing
+  aims to reduce the number of \emph{unknown abnormal} behaviors by observing
   more \emph{interesting} (i.e., relating to unknown abnormal) behaviors. The
@@
 is the \emph{individual count} of all observed distinct logic states during a
-fuzzing campaign. Logic states represent more \emph{interesting} behaviors
-(i.e., relating to unknown abnormal behaviors) in a finer granularity, meaning
-that observing more interesting behaviors is reliably reflected to larger
-coverage.
+fuzzing campaign. Logic states represent \emph{interesting} behaviors (i.e.,
+relating to unknown abnormal behaviors) in a finer granularity, meaning that
+observing more interesting behaviors is reliably reflected to larger coverage.
 
@@
 The approach of untargeted fuzzing can be formally described as follows. Upon
-executing a mutated input, let $P(\mathrm{N})$ be the probability of observing a
+executing a mutated input, let $\Pr(\mathrm{N})$ be the probability of observing a
 \underline{\textbf{n}}ew behavior as a result of execution. Then, the
 probability of discovering \underline{\textbf{u}}nknown
-\underline{\textbf{a}}bnormal behavior $P(\mathrm{UA}) := P(\mathrm{U} \cap
+\underline{\textbf{a}}bnormal behavior $\Pr(\mathrm{UA}) := \Pr(\mathrm{U} \cap
 \mathrm{A})$ is
@@
 \begin{align}
-  P(\mathrm{UA}) 
-      &= P(\mathrm{N} \cap \mathrm{UA}) \tag{by $\mathrm{U} \subset \mathrm{N}$} \\
-      &= P(\mathrm{N}) \times P(\mathrm{UA} \mid \mathrm{N}) \tag{by chain rule}. 
+  \Pr(\mathrm{UA}) 
+      &= \Pr(\mathrm{N} \cap \mathrm{UA}) \tag{by $\mathrm{U} \subset \mathrm{N}$} \\
+      &= \Pr(\mathrm{N}) \cdot \Pr(\mathrm{UA} \mid \mathrm{N}) \tag{by chain rule}. 
 \end{align}
 
-Here, the second term $P(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
+Here, the second term $\Pr(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
 revealing an unknown abnormal behavior given a new behavior, which can be
 interpreted as the \emph{interestingness} of the mutation base. In other words,
-untargeted fuzzing attempts to (i) increase $P(\mathrm{N})$ to investigate more
-program behaviors while (ii) keeping the interestingness $P(\mathrm{UA} \mid
-\mathrm{N})$ as high as possible.
+untargeted fuzzing attempts to (i) increase $\Pr(\mathrm{N})$ to investigate
+more program behaviors while (ii) keeping the interestingness $\Pr(\mathrm{UA}
+\mid \mathrm{N})$ high.
 %
@@
 %
-As the interestingness $P(\mathrm{UA} \mid \mathrm{N})$ is the expectation of an
-\emph{unobserved} behavior, there is no direct way to measure interestingness. 
-%
-However, the practice of untargeted fuzzing suggests that
-the resulting program behavior is unlikely to be \emph{unknown abnormal} if the
-mutation base is highly repetitive, as fuzzers commonly incorporate corpus
-minimization \cite{todo} and branch hit count buckets \cite{todo}.
-%
-The rationales are: (i) if a fewer repetition was normal, more repetition is
-also likely normal (i.e., unlikely \emph{abnormal}) and (ii) even if it was
-abnormal, it may correspond to pre-observed less-repetition counterparts (i.e.,
-unlikely \emph{unknown}).
+As the interestingness $\Pr(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
+an \emph{unobserved} behavior, there is no direct way to measure
+interestingness. 
+%
+However, the common usage of corpus minimization \cite{todo} and branch hit
+count buckets \cite{todo} in untargeted fuzzing suggests that a program behavior
+is less likely to be \emph{unknown abnormal} (i.e., less interesting) if its
+mutation base input is highly repetitive.
+%in modern untargeted fuzzing.
+%
+The rationales are: (i) if a fewer repetition was normal,
+more repetition is also likely normal and (ii) even if it was abnormal, it is 
+not unknown if it corresponds to pre-observed less-repetition counterparts.
+
+To generalize this practice from mutation base inputs to all inputs (i.e., all
+their program behaviors), a program behavior can be deemed less interesting if
+it include more repetitions.
 
@@
 %\begin{equation}
-%  P(\mathrm{abnormal} \mid X=n) \propto 1/n.
+%  \Pr(\mathrm{abnormal} \mid X=n) \propto 1/n.
 %\end{equation}
@@
 \label{e:ls}
-  l := \{b \mid b \in \mathcal{T}_b\},
+  l := \{b \mid b \in \mathcal{T}_b\}.
 \end{equation}
@@
 
-\pp{Interestingness: definition vs. convention}
-%
-Although the \emph{interestingness} has been widely discussed in recent
-untargeted fuzzing, it has never been clearly defined. The conventional
-understanding is a property of an \emph{input} having \emph{new
-execution paths} in its resulting behavior. In comparison, this work
-defines interestingness as a property of a \emph{program behavior} indicating 
-the \emph{expectation} of being an abnormal behavior.
-
-Despite an apparent difference between them, the definition \emph{subsumes} the
-convention because if an input discovered a new path (conventional
-interesting), its behavior would have a higher expectation to be abnormal than
-the ones only exhibiting previously checked paths (defined interesting). 
-%
-Still, there are some disagreements between the definition and the convention,
-such as when a behavior \emph{contains} another known abnormal behavior without
-discovering any new path. The definition may be refined to resolve such
-disagreements.
+%\pp{Interestingness: definition vs. convention}
+%%
+%Although the \emph{interestingness} has been widely discussed in recent
+%untargeted fuzzing, it has never been clearly defined. The conventional
+%understanding is a property of an \emph{input} having \emph{new
+%execution paths} in its resulting behavior. In comparison, this work
+%defines interestingness as a property of a \emph{program behavior} indicating 
+%the \emph{expectation} of being an abnormal behavior. 
+%
+%Despite an apparent difference between them, the definition \emph{subsumes} the
+%convention because if an input discovered a new path (conventional
+%interesting), its behavior would have a higher expectation to be abnormal than
+%the ones only exhibiting previously checked paths (defined interesting). 
+%%
+%Still, there are some disagreements between the definition and the convention,
+%such as when a behavior \emph{contains} another known abnormal behavior without
+%discovering any new path. The definition may be refined to resolve such
+%disagreements.
 
@@
 program behavior it checks, the less abnormal program behaviors are expected to
-be left. This roughly translates to $P(\mathrm{abnormal} \mid \mathrm{new})$
+be left. This roughly translates to $\Pr(\mathrm{abnormal} \mid \mathrm{new})$
 being equal throughout a fuzzing campaign.
-%, whereby $P(\mathrm{new} \cap
-%\mathrm{abnormal})$ then majorly depends on how high $P(\mathrm{new})$ is;
+%, whereby $\Pr(\mathrm{new} \cap
+%\mathrm{abnormal})$ then majorly depends on how high $\Pr(\mathrm{new})$ is;
 %proportional to the number of observed program behaviors per time.
@@
 \emph{prioritizes} code that likely leads to abnormal behaviors, which may result
-in a larger $P(\mathrm{abnormal} \mid \mathrm{new})$ at the beginning that slowly
+in a larger $\Pr(\mathrm{abnormal} \mid \mathrm{new})$ at the beginning that slowly
 decreases over time.
@@
 One possible remedy is refining interestingness to incorporate a complete set of
-factors that affects $P(\mathrm{abnormal})$ (e.g., freshness of code).  A
+factors that affects $\Pr(\mathrm{abnormal})$ (e.g., freshness of code).  A
 further investigation on interestingness is required.

### 2024-03-04 lscov/lscov-daemon.c
lscov-daemon.c: replaced tallying with __builtin_popcountll

@@ -165,6 +165,10 @@ static inline void hcount_bucket_to_lstate(u8* lstate) {
     dest++;
   }
 #else
+  /* It feels wasteful as 7/8 of the bits are 0, but it may be better than
+   * compacting bits as it requires one load operation and one shift operations
+   * during execution. We'll see which is better tho. */ 
+
   memcpy(lstate, hit_counts, LSTATE_SIZE);
 #endif
 }
@@ -312,12 +316,11 @@ u32 bfilter_get_num_1s() {
   /* Tally 1s in the filter. */
   u32 num_1s = 0;
 
-  for (int i = 0; i < bfilter_size; i++) {
-    u8 _byte = bfilter[i];
-    while (_byte) {
-      num_1s += (_byte & 0x01);
-      _byte >>= 1;
-    }
+  u64 *bfilter64 = (u64 *)bfilter;
+  u32 rem_size = bfilter_size >> 3;
+  while (rem_size--) {
+    num_1s += __builtin_popcountll(*bfilter64);
+    bfilter64++;
   }
 
   return num_1s;

### 2024-03-04 lscov/lscov-llvm-rt.a.c

@@ -118,8 +118,8 @@ void __lscov_main(void) {
 
     /* Sanity check: should have a clear '__lscov_area_ptr'. */
     u8 _test_hc = 0;
-    for (int i = 1; i < (LSTATE_SIZE >> 4); i++)
-      _test_hc |= __lscov_area_ptr[i << 4];
+    for (int i = 1; i < (LSTATE_SIZE >> 6); i++)
+      _test_hc |= __lscov_area_ptr[i << 6];
     if (_test_hc) 
       assert(0 && "tainted hit counts");
   }

### 2024-03-04 lscov/lscov-daemon.c
lscov-llvm-rt.a.c: sema_rd can indeed be 1 before _end_ posts it (if the previous execution is a crash or a timeout and the daemon is too busy to accept the first post for a crash cleanup)

@@ -99,7 +99,8 @@ static inline int hcount_wait_until_ready() {
     assert(0 && "_sema_rd_val > 1");
     FATAL("_sema_rd_val: %d", _sema_rd_val);
   }
-  return sem_timedwait(sema_rd, &loop_timeout);
+  //return sem_timedwait(sema_rd, &loop_timeout);
+  return sem_wait(sema_rd);
 }
 
 /* Bucketing excerpted from AFL. It was much faster than my implementation,
@@ -166,8 +167,8 @@ static inline void hcount_bucket_to_lstate(u8* lstate) {
   }
 #else
   /* It feels wasteful as 7/8 of the bits are 0, but it may be better than
-   * compacting bits as it requires one load operation and one shift operations
-   * during execution. We'll see which is better tho. */ 
+   * compacting bits as it requires two additional operations (i.e., load and
+   * shift) during execution. I need to check which is better soon tho. */ 
 
   memcpy(lstate, hit_counts, LSTATE_SIZE);
 #endif
@@ -336,7 +337,6 @@ u32 bfilter_calc_cardinality(u32 num_1s) {
     has_divisor = 1;
   }
 
-  // FIXME: replacing 'log' with a faster one?
   double dividend = log(1.0 - (double)num_1s/bfilter_size_bits);
   u32 cov = (u32)(dividend / divisor);
 
@@ -453,6 +453,7 @@ void sem_print_val(const char *when) {
   sem_getvalue(sema_dr, &_sema_dr_val);
   SAYF("[%s] rd:%d, dr:%d\n", when, _sema_rd_val, _sema_dr_val);
 }
+/* Debug */
 
 void lscov_loop() {
   while (1) {
@@ -460,9 +461,6 @@ void lscov_loop() {
 
     /* Update the filter. */
     if (!sem_rd_ret) {
-#ifdef DEBUG_RECEIVE_HCOUNT
-      ACTF("Received new hit counts.");
-#endif
       last_exec_count++;
 
       /* Bucketize the hit counts, making a logic state. */

### 2024-03-04 lscov/lscov-llvm-rt.a.c

@@ -28,36 +28,33 @@ sem_t*       __lscov_sema_rd;
 sem_t*       __lscov_sema_dr;
 
 
+void __lscov_start_exec() {
+  /* Mark this hit count as unnotified yet to the daemon (0x01). */
+  *__lscov_area_ptr = 0x81;
+
+  int _sema_dr_val;
+  sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
+  if (_sema_dr_val > 1) {
+    SAYF("_sema_dr_val: %d\n", _sema_dr_val);
+    assert(0 && "_sema_dr_val > 1");
+  }
+
+  /* Wait until SHM is ready */
+  sem_wait(__lscov_sema_dr);
+}
+
 void __lscov_end_exec() {
   /* Mark that it notified this termination to the daemon. */
   *__lscov_area_ptr = 0x80;
 
   int _sema_rd_val;
   sem_getvalue(__lscov_sema_rd, &_sema_rd_val);
-  if (_sema_rd_val) {
-    SAYF("_sema_rd_val: %d\n", _sema_rd_val);
-    assert(0 && "non-zero _sema_rd_val");
+  if (!_sema_rd_val) {
+    /* Mark the end of recording. */
+    sem_post(__lscov_sema_rd);
   }
-
-  /* Mark the end of recording. */
-  sem_post(__lscov_sema_rd);
 }
 
-void __lscov_start_exec() {
-  /* Mark this hit count as unnotified yet to the daemon (0x01). */
-  *__lscov_area_ptr = 0x81;
-
-  /* Wait until SHM is ready */
-  sem_wait(__lscov_sema_dr);
-}
-
-/* Finalization (per execution) */
-
-__attribute__((destructor(CONST_PRIO))) 
-void __lscov_fin(void) {
-  if (__lscov_sema_rd) 
-    __lscov_end_exec();
-}
 
 /* Initialization (upon starting) */
 
@@ -123,4 +120,12 @@ void __lscov_main(void) {
     if (_test_hc) 
       assert(0 && "tainted hit counts");
   }
+}
+
+/* Finalization (per execution) */
+
+__attribute__((destructor(CONST_PRIO))) 
+void __lscov_fin(void) {
+  if (__lscov_sema_rd) 
+    __lscov_end_exec();
 }

### 2024-03-04 lscov/lscov-daemon.c
lscov-daemon.c: parallelized report()

@@ -14,6 +14,7 @@
 #include <fcntl.h>
 #include <locale.h>
 #include <math.h>
+#include <pthread.h>
 #include <semaphore.h>
 #include <signal.h>
 #include <stdio.h>
@@ -48,7 +49,10 @@ u8*         bfilter;              // Bloom filter itself
 u32         bfilter_size_bits;    // Bloom filter size, in bits
 time_t      start_time;           // Measurement start time (in unix time)
 time_t      next_tallying_time;   // Next tallying time (in unix time)
-u32         last_exec_count;
+
+u32         exec_count;
+u32         exec_count_in_period;
+u8          stop_soon;
 
 
 // FIXME: bfilter --> limiting caching? other core?
@@ -84,10 +88,10 @@ void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
 }
 
 void stat_append(u32 time, u32 cov, float density, u32 rate_ins, 
-    float rate_per, u32 rate_avg) {
+    float rate_per, u32 rate_avg, float rate_per_avg) {
   FILE *fout = fopen(stat_path, "a");
-  fprintf(fout, "%u,%u,%3.2f,%u,%3.2f,%u\n", time, cov, density,
-      rate_ins, rate_per, rate_avg);
+  fprintf(fout, "%u,%u,%3.2f,%u,%3.2f,%u,%3.2f\n", time, cov, density,
+      rate_ins, rate_per, rate_avg, rate_per_avg);
   fclose(fout);
 }
 
@@ -390,16 +394,16 @@ void lscov_init() {
 #endif
 }
 
-void lscov_report(int use_cur_time) {
+void* lscov_report(void * _unused) {
   if (!start_time)
-    return;
+    return NULL;
 
 #ifdef PRINT_STAT
   static u32 prev_cov = 0;
 #endif
 
   time_t prev_next_time = tally_update_next_time();
-  if (use_cur_time)
+  if (stop_soon)
     prev_next_time = time(NULL);
 
 #ifdef DEBUG_CARDINALITY_TIME
@@ -427,13 +431,18 @@ void lscov_report(int use_cur_time) {
 #ifdef PRINT_STAT
   float density = (float)num_1s / bfilter_size_bits * 100;
   u32 rate_ins = (u32)((cov - prev_cov) / tallying_period);
-  float rate_per = (float)(cov - prev_cov) / last_exec_count * 100;
+  float rate_per = (float)(cov - prev_cov) / exec_count_in_period * 100;
[…]

### 2024-03-04 lscov/lscov-daemon.c
lscov-llvm-rt.a.c, lscov-daemon.c: sema_rd --> read signal. clear area in llvm-rt.

@@ -178,9 +178,11 @@ static inline void hcount_bucket_to_lstate(u8* lstate) {
 #endif
 }
 
-void hcount_nuke() {
-  memset(hit_counts+1, 0, LSTATE_SIZE-1);
-  sem_post(sema_dr);
+void hcount_mark_read() {
+  int _sema_dr_val;
+  sem_getvalue(sema_dr, &_sema_dr_val);
+  if (!_sema_dr_val) 
+    sem_post(sema_dr);
 }
 
 void hcount_stop() {
@@ -480,7 +482,7 @@ void lscov_loop() {
             MAP_PRIVATE | MAP_ANONYMOUS, -1, 0);
 
       hcount_bucket_to_lstate(lstate);
-      hcount_nuke();
+      hcount_mark_read();
 
       /* Set the hash indices of the logic state to 1 in the filter. */
       for (int h = 0; h < num_hashes; h++) {

### 2024-03-04 lscov/lscov-llvm-rt.a.c

@@ -7,7 +7,6 @@
  * See "llvm_mode/afl-llvm-rt.o.c" for the reference implementation.
  */
 
-#include <assert.h>
 #include <semaphore.h>
 #include <signal.h>
 #include <sys/types.h>
@@ -32,15 +31,11 @@ void __lscov_start_exec() {
   /* Mark this hit count as unnotified yet to the daemon (0x01). */
   *__lscov_area_ptr = 0x81;
 
-  int _sema_dr_val;
-  sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
-  if (_sema_dr_val > 1) {
-    SAYF("_sema_dr_val: %d\n", _sema_dr_val);
-    assert(0 && "_sema_dr_val > 1");
-  }
-
   /* Wait until SHM is ready */
   sem_wait(__lscov_sema_dr);
+
+  /* Clear area. */
+  memset(__lscov_area_ptr+1, 0, LSTATE_SIZE-1);
 }
 
 void __lscov_end_exec() {
@@ -109,7 +104,7 @@ void __lscov_main(void) {
     int _sema_dr_val;
     sem_getvalue(__lscov_sema_dr, &_sema_dr_val);
     if (_sema_dr_val > 1)
-      assert(0 && "_sema_dr_val > 1");
+      LSCOV_ABORT("(lscov) _sema_dr_val (=%d) > 1", _sema_dr_val);
 
     __lscov_start_exec();
 
@@ -118,7 +113,7 @@ void __lscov_main(void) {
     for (int i = 1; i < (LSTATE_SIZE >> 6); i++)
       _test_hc |= __lscov_area_ptr[i << 6];
     if (_test_hc) 
-      assert(0 && "tainted hit counts");
+      LSCOV_ABORT("(lscov) tainted hit counts");
   }
 }
 

### 2024-03-04 lscov/stuff.h

@@ -255,6 +255,15 @@ typedef int64_t  s64;
     if (res < 0) PFATAL(x); else FATAL(x); \
   } while (0)
 
+/* Custom FATAL() for debugging. */
+
+#define LSCOV_ABORT(x...) do { \
+    printf(x); \
+    FILE *fout = fopen(".lscov", "a"); \
+    fprintf(fout, x); \
+    abort(); \
+  } while (0)
+
 /* Random number */
 
 #define RANDOM(x) (random() % (x))

### 2024-03-04 lscov/cov-to-fig.py
cov-to-fig.py: draw figures // lscov-daemon.c: lsstat.csv to lscov.csv

@@ -1,0 +1,65 @@
+import sys
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Load CSV.
+
+data = {}
+
+raw_data = []
+with open(sys.argv[1], "r") as f:
+    raw_data = f.readlines()
+
+idx_to_label = []
+labels = raw_data[0].strip().split(',')
+for label in labels:
+    idx_to_label += [label]
+    data[label] = []
+
+raw_data = raw_data[1:]
+
+for raw_datum in raw_data:
+    raw_datum_split = raw_datum.strip().split(',')
+    for i, d in enumerate(raw_datum_split):
+        if ('.' in d):
+            data[idx_to_label[i]] += [float(d)]
+        else:
+            data[idx_to_label[i]] += [int(d)]
+
+# Draw figures.
+
+fig, ax = plt.subplots(ncols=3, figsize=(10, 3))
+
+#ax[0].set_box_aspect(0.75)
+#ax[1].set_box_aspect(0.75)
+#ax[2].set_box_aspect(0.75)
+
+ax[0].plot(data['Time'], data['Coverage'], color='C0')
+ax[0].fill_between(data['Time'], data['Coverage'], color='C0', alpha=0.2)
+ax[0].set_xlabel("Time (sec)")
+ax[0].set_ylabel("Logic State Coverage")
+ax[0].set_xlim([data['Time'][0], data['Time'][-1]])
+ax[0].set_ylim(bottom=0)
+
+ax[1].plot(data['Time'], data['RateS(ins)'], color='C1', alpha=0.5)
+ax[1].plot(data['Time'], data['RateS(avg)'], color='C1', linewidth=2)
+ax[1].set_xlabel("Time (sec)")
+ax[1].set_ylabel("New Coverage (/sec)")
+ax[1].set_xlim([data['Time'][0], data['Time'][-1]])
+ax[1].legend(["Instantaneous", "Average"], loc="upper right")
+
+ax[2].plot(data['Time'], data['RateE(ins)'], color='C2', alpha=0.5)
+ax[2].plot(data['Time'], data['RateE(avg)'], color='C2', linewidth=2)
+ax[2].set_xlabel("Time (sec)")
+ax[2].set_ylabel("New Coverage (/exec)")
+ax[2].set_xlim([data['Time'][0], data['Time'][-1]])
+ax[2].set_ylim([0, 100])
[…]

### 2024-03-04 lscov/lscov-daemon.c

@@ -34,7 +34,6 @@ time_t      tallying_period = 10;      // Tallying period (in seconds)
 u32         bfilter_size = 0x4000000;  // Bloom filter size, in bytes
 u8          num_hashes = 4;            // Number of hashes
 const char* out_path = "lscov.csv";    // Output path
-const char* stat_path = "lsstat.csv";  // Statistics path
 u8          error_percent = 0;         // Error bound (0: disabled)
 
 /* State variables */
@@ -55,43 +54,27 @@ u32         exec_count_in_period;
 u8          stop_soon;
 
 
-// FIXME: bfilter --> limiting caching? other core?
-
 void out_init() {
   FILE *fout = fopen(out_path, "w");
 
   fprintf(fout, "Time,Coverage");
   if (error_percent > 0)
-    fprintf(fout, ",(Lower),(Upper)\n");
-  else
-    fprintf(fout, "\n");
+    fprintf(fout, ",(Lower),(Upper)");
+  fprintf(fout, ",Density,RateS(ins),RateE(per),RateS(avg),RateE(avg)\n");
 
   fclose(fout);
 }
 
-void stat_init() {
-  FILE *fout = fopen(stat_path, "w");
-  fprintf(fout, "Time,Coverage,Density,Rate(ins),Rate(per),Rate(avg)\n");
-  fclose(fout);
-}
-
-void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err) {
+void out_append(u32 time, u32 cov, u32 lower_err, u32 upper_err, float density,
+    u32 rate_ins, float rate_per, u32 rate_avg, float rate_per_avg) {
   FILE *fout = fopen(out_path, "a");
 
   fprintf(fout, "%u,%u", time, cov);
   if (error_percent > 0)
-    fprintf(fout, ",%u,%u\n", lower_err, upper_err);
-  else
-    fprintf(fout, "\n");
-
-  fclose(fout);
-}
-
-void stat_append(u32 time, u32 cov, float density, u32 rate_ins, 
-    float rate_per, u32 rate_avg, float rate_per_avg) {
-  FILE *fout = fopen(stat_path, "a");
-  fprintf(fout, "%u,%u,%3.2f,%u,%3.2f,%u,%3.2f\n", time, cov, density,
[…]

### 2024-03-05 lscov/cov-to-fig.py
fancy fig generator

@@ -1,6 +1,10 @@
+#!/usr/bin/python3
+
 import sys
 import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
 import numpy as np
+import math
 
 # Load CSV.
 
@@ -28,36 +32,74 @@ for raw_datum in raw_data:
 
 # Draw figures.
 
-fig, ax = plt.subplots(ncols=3, figsize=(10, 3))
+fig, ax = plt.subplots(ncols=3, figsize=(10, 3), layout="tight")
 
-#ax[0].set_box_aspect(0.75)
-#ax[1].set_box_aspect(0.75)
-#ax[2].set_box_aspect(0.75)
+ax[0].set_box_aspect(0.75)
+ax[1].set_box_aspect(0.75)
+ax[2].set_box_aspect(0.75)
+
+fig.subplots_adjust(bottom=0.27, wspace=0.4)
+
+cov_unit_pow10 = 0 
+_max_cov = data['Coverage'][-1]
+while (True):
+    _max_cov //= 1000 
+    if (_max_cov <= 0): break
+    cov_unit_pow10 += 3 
+
+cov_unit_str = ""
+if (cov_unit_pow10 > 0):
+    cov_unit_str = " (x$10^{}$)".format(cov_unit_pow10)
+
+time_unit = 1
+_max_time = data['Time'][-1]
+while (True):
+    if (time_unit == 1):
+        next_time_unit = 10
+    elif (time_unit == 10):
+        next_time_unit = 60
+    elif (round(math.log(time_unit // 6, 10), 3).is_integer()):
+        next_time_unit = time_unit * 2
+    elif (round(math.log(time_unit // 12, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 2) * 5
+    elif (round(math.log(time_unit // 30, 10), 3).is_integer()):
+        next_time_unit = time_unit * 2
+    _num_time_ticks = _max_time // next_time_unit
+    if (_num_time_ticks <= 2): break
+    time_unit = next_time_unit
+
+time_fmt = ticker.FuncFormatter(lambda ms, x: int(ms / 60))
+cov_fmt = ticker.FuncFormatter(lambda ms, x: int(ms / (10 ** cov_unit_pow10)))
 
 ax[0].plot(data['Time'], data['Coverage'], color='C0')
[…]

### 2024-03-05 paper/main.tex
paper: enhanced visual aid for interestingness

@@
   \centering
-  \includegraphics[width=\columnwidth]{images/repr.pdf}
-  \caption{Example control flow graph and the number of program behaviors
-  (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
-  of the branch $b$. Dotted lines demarcate whether the corresponding branch is
-  hit or not (i.e., presence in a logic state).}
+  \vspace{-1em}
+  \includegraphics[height=4.5cm]{images/repr-cfg.pdf}
+  \includegraphics[height=4.5cm]{images/repr-grid.pdf}
+  \vspace{-.5em}
+  \caption{Example control flow graph and its logic states (colored box) that
+  the program behaviors with different branch hit counts belong to. $m(b)$
+  denotes the hit count of branch $b$.}
   % Each region surrounded by dotted lines constitutes one logic state.}
@@
 
-\autoref{f:repr} shows an example control-flow graph and the number of possible
-program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
-count of the branch $b$. For example, there are two possible program behaviors,
-$b_2$ after $b_1$ or $b_1$ after $b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
-%Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
-%
-The dotted lines demarcate whether the corresponding branch is hit or not, which
-also corresponds to the presence of the branch in a logic state.
-%the beginning of a new power-of-2 branch hit count
-%(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
-%bucket. 
-The surrounded region has the same set of satisfied branches, constituting
-\emph{one logic state}.
-
-As shown, the program behaviors with more repetitive branches are grouped with
-more program behaviors as one logic state.  For example, a program behavior
-having only one repetitive branch (either $b_1$ or $b_2$) falls into the slim
-logic states adjacent to axis (bottom right and top left), while a behavior
-having two repetitive branches (both $b_1$ and $b_2$) falls into the large logic
-state (top right). This results in observing repetitive (i.e., less interesting)
-program states represented by fewer logic states, leading to smaller logic state
-coverage.
+\autoref{f:repr} shows an example control-flow graph and its logic states
+(colored boxes) that the program behaviors with different sets of satisfied
+branches belong to.
+%, where $m(b)$ denotes the hit count of a branch $b$. 
+For example, a program behavior that does not hit any colored branches (i.e.,
+$m(b_1)=m(b_2)=m(b_3)=0$) belongs to \cbox{black}, and a program
+behavior that only hits one of them (e.g., $m(b_i)>1$ and $m(b_j)=0$ for $i \in
+\{1,2,3\}$ and $j \ne i$) belongs to the logic state of the corresponding color
+(\cbox{red}, \cbox{green}, and \cbox{blue}).
+%The dotted lines demarcate whether the corresponding branch is hit or not, which
+%also corresponds to the presence of the branch in a logic state.
+%The surrounded region has the same set of satisfied branches, constituting
+%\emph{one logic state}.
+
+The figure shows the increasing size of logic states as their constituent
+program behaviors involve more repetitive branches. For example, a program
+behavior with two repetitive branches (i.e., $b_1$ and $b_2$, $b_2$ and $b_3$,
+or $b_1$ and $b_3$) falls into a larger logic state (e.g., \cbox{yellow},
+\cbox{cyan}, and \cbox{magenta}), and a behavior with three repetitive branches
+(i.e., all $b_1$, $b_2$, and $b_3$) falls into the largest logic state (i.e.,
+\cbox{gray}).
+%
+This results in observing repetitive (i.e., less interesting) program states
+represented by fewer logic states, leading to smaller logic state
+coverage.\footnote{It is worth noting that a coordinate in the grid does
+\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
+represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
+However, it does not affect the relative size of visualized logic states because
+a coordinate only has more program behaviors as it gets further from the
+origin.}
 

### 2024-03-05 paper/images/repr-grid.py

@@ -1,0 +1,58 @@
+#!/usr/bin/python3
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+AXIS_MAX=7
+
+fig = plt.figure(figsize=(5,4.9))
+ax = fig.add_subplot(projection='3d')
+
+vols = {}
+colors = {}
+for h1, p1, o1, c1 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (1, 0, 0))]:
+    for h2, p2, o2, c2 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (0, 1, 0))]:
+        for h3, p3, o3, c3 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (0, 0, 1))]:
+            vols[h1, h2, h3] = [*(p1, p2, p3), *(o1, o2, o3)]
+            colors[h1, h2, h3] = tuple(map(sum, zip(c1, c2, c3))) 
+
+ax.bar3d(*vols[0, 0, 0], color=(*colors[0, 0, 0], 0.6), linewidth=2, edgecolor=(1, 1, 1, 0.3))
+for key in [(1, 0, 0), (0, 1, 0), (0, 0, 1)]:
+    ax.bar3d(*vols[key], color=(*colors[key], 0.45), linewidth=2, edgecolor=(1, 1, 1, 0.3))
+for key in [(1, 1, 0), (0, 1, 1), (1, 0, 1)]:
+    ax.bar3d(*vols[key], color=(*colors[key], 0.25), linewidth=2, edgecolor=(1, 1, 1, 0.3))
+ax.bar3d(*vols[1, 1, 1], color=(*colors[1, 1, 1], 0.1), linewidth=2, edgecolor=(1, 1, 1, 0.3))
+
+ax.set_aspect('equal', 'box')
+
+ax.xaxis.line.set_color((0.9, 0.3, 0.3))
+ax.yaxis.line.set_color((0.3, 0.9, 0.3))
+ax.zaxis.line.set_color((0.3, 0.3, 0.9))
+ax.xaxis.line.set_linewidth(5)
+ax.yaxis.line.set_linewidth(5)
+ax.zaxis.line.set_linewidth(5)
+ax.set_xlabel("$m(b_1)$", fontsize=15)
+ax.set_ylabel("$m(b_2)$", fontsize=15)
[…]

### 2024-03-05 lscov/lscov-daemon.c
lscov-daemon.c: handling 0-execution periods

@@ -395,9 +395,11 @@ void* lscov_report(void * _unused) {
   
   float density = (float)num_1s / bfilter_size_bits * 100;
   u32 rate_ins = (u32)((cov - prev_cov) / tallying_period);
-  float rate_per = (float)(cov - prev_cov) / exec_count_in_period * 100;
+  float rate_per = !exec_count_in_period ? 
+    (float)(cov - prev_cov) / exec_count_in_period * 100 : 0;
   u32 rate_avg = (u32)(cov / prev_time); 
-  float rate_per_avg = (float)cov / exec_count * 100;
+  float rate_per_avg = !exec_count ? 
+    (float)cov / exec_count * 100 : 0;
 
 #ifdef PRINT_STAT
   SAYF("    density: %3.2f%%, rate: (ins) %'u ls/sec [%3.2f%%], (avg) %'u ls/sec [%3.2f%%]\n",

### 2024-03-05 paper/main.tex
paper: discussion: quality metric for general fuzzing (revisemake) --> replacing 'completeness of targeted fuzzing'

@@
 abnormal behavior (Behavior C) follows the same control flow to a normal
-behavior (Behavior B) until a use-after-free happens, which makes the behavior
-eventually abnormal unlike its normal counterpart. This means that, even though
-a behavior is known to be normal, it does not suggest much about the normality
-of other behaviors \emph{on course for} such.
+behavior (Behavior B) until use-after-free, which makes the behavior eventually
+abnormal unlike its normal counterpart. 
+%
+What it implies is that the executions that do not contribute to the growth of
+logic state coverage are not entirely wasteful executions because they are still
+possible to reveal abnormal behaviors. However, they are unlikely to do so, let
+alone revealing \emph{unknown} ones (\autoref{s:fuzz:unfuzz}).
+
+%This means that, even though a behavior is known to be normal, it does not
+%suggest much about the normality of other behaviors \emph{on course for} such.
 
@@
 
-\pp{Completeness of targeted fuzzing}
-%
-The completeness of untargeted fuzzing hinges on the observation that the more
-program behavior it checks, the less abnormal program behaviors are expected to
-be left. This roughly translates to $\Pr(\mathrm{abnormal} \mid \mathrm{new})$
-being equal throughout a fuzzing campaign.
-%, whereby $\Pr(\mathrm{new} \cap
-%\mathrm{abnormal})$ then majorly depends on how high $\Pr(\mathrm{new})$ is;
-%proportional to the number of observed program behaviors per time.
-%
-However, targeted fuzzing (e.g., directed or regression fuzzing)
-\emph{prioritizes} code that likely leads to abnormal behaviors, which may result
-in a larger $\Pr(\mathrm{abnormal} \mid \mathrm{new})$ at the beginning that slowly
-decreases over time.
-
-This affects the fundamental observation for completeness because targeted
-fuzzers may reveal more abnormal behaviors even after observing fewer program
-behaviors.
-%
-One possible remedy is refining interestingness to incorporate a complete set of
-factors that affects $\Pr(\mathrm{abnormal})$ (e.g., freshness of code).  A
-further investigation on interestingness is required.
+%\pp{Completeness of targeted fuzzing}
+%%
+%The completeness of untargeted fuzzing hinges on the observation that the more
+%interesting program behavior it checks, the less unknown abnormal program
+%behaviors are expected to be left. This roughly translates to $\Pr(\mathrm{UA}
+%\mid \mathrm{N})$ being equal throughout a fuzzing campaign.
+%%, whereby $\Pr(\mathrm{new} \cap
+%%\mathrm{abnormal})$ then majorly depends on how high $\Pr(\mathrm{new})$ is;
+%%proportional to the number of observed program behaviors per time.
+%%
+%However, targeted fuzzing (e.g., directed or regression fuzzing)
+%\emph{prioritizes} code that likely leads to abnormal behaviors, which may result
+%in a larger $\Pr(\mathrm{UA} \mid \mathrm{N})$ at the beginning that slowly
+%decreases over time. 
+%
+%This affects the fundamental observation for completeness because targeted
+%fuzzers may reveal more abnormal behaviors even after observing fewer program
+%behaviors.
+%%
+%One possible remedy is refining interestingness to incorporate a complete set of
+%factors that affects $\Pr(\mathrm{UA})$ (e.g., freshness of code).  A
+%further investigation on interestingness is required.
+
+% FIXME: revise!
+\pp{Quality metric for general fuzzing}
+%
+The legitimacy of logic state coverage hinges on the current conventional
+understanding of interesting program behaviors in \emph{untargeted} fuzzing,
+namely the behaviors with less repetition. However, recent findings 
+\cite{regression,risk,root-causes-age} suggest that various code characteristics
+(e.g., the age of code) make some code likelier to cause bugs,
+which makes the program behaviors executing such a portion of code have a higher
+expectation to reveal unknown abnormal behaviors (i.e., more interesting).
+%
+\emph{Targeted} fuzzing \cite{regression,directed,risk} attempts to capitalize
+the findings by prioritizing such code, while logic state coverage would
+under-estimate their quality by only considering less repetition as more
+interesting.
+
+For a quality metric that encompasses general (i.e., both untargeted and
+targeted) fuzzing, future research needs to address two issues around
+interestingness. First, it should refine the interestingness of program
+behaviors. Not only should it systemize the factors that decide interestingness,
+but also it should assess which factor affects \emph{more} than others by
+\emph{how much}.  Second, it should incorporate such refined interestingness
+into the quality metric. If it would follow the philisophy of logic state
+coverage (i.e., more uninteresting behavior in fewer logic states),
+\emph{grouping} uninteresting branches can be an approach as it makes the
+program behaviors with uninteresting branches occupy fewer logic states.
 

### 2024-03-05 paper/images/repr-grid.py

@@ -21,7 +21,7 @@ for key in [(1, 0, 0), (0, 1, 0), (0, 0, 1)]:
     ax.bar3d(*vols[key], color=(*colors[key], 0.45), linewidth=2, edgecolor=(1, 1, 1, 0.3))
 for key in [(1, 1, 0), (0, 1, 1), (1, 0, 1)]:
     ax.bar3d(*vols[key], color=(*colors[key], 0.25), linewidth=2, edgecolor=(1, 1, 1, 0.3))
-ax.bar3d(*vols[1, 1, 1], color=(*colors[1, 1, 1], 0.1), linewidth=2, edgecolor=(1, 1, 1, 0.3))
+ax.bar3d(*vols[1, 1, 1], color=(*colors[1, 1, 1], 0.25), linewidth=2, edgecolor=(1, 1, 1, 0.3))
 
 ax.set_aspect('equal', 'box')
 

### 2024-03-06 lscov/cov-to-fig.py
cov-to-fig.py: finer-grained x-ticks

@@ -51,6 +51,7 @@ cov_unit_str = ""
 if (cov_unit_pow10 > 0):
     cov_unit_str = " (x$10^{}$)".format(cov_unit_pow10)
 
+# FIXME: there must be a better algorithm for this kind of stuff.
 time_unit = 1
 _max_time = data['Time'][-1]
 while (True):
@@ -59,13 +60,23 @@ while (True):
     elif (time_unit == 10):
         next_time_unit = 60
     elif (round(math.log(time_unit // 6, 10), 3).is_integer()):
-        next_time_unit = time_unit * 2
+        next_time_unit = (time_unit // 2) * 3
+    elif (round(math.log(time_unit // 9, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 3) * 4 
     elif (round(math.log(time_unit // 12, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 2) * 5
+        next_time_unit = (time_unit // 4) * 5
+    elif (round(math.log(time_unit // 15, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 5) * 6 
+    elif (round(math.log(time_unit // 18, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 3) * 4 
+    elif (round(math.log(time_unit // 24, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 4) * 5 
     elif (round(math.log(time_unit // 30, 10), 3).is_integer()):
-        next_time_unit = time_unit * 2
+        next_time_unit = (time_unit // 2) * 3
+    elif (round(math.log(time_unit // 45, 10), 3).is_integer()):
+        next_time_unit = (time_unit // 3) * 4 
     _num_time_ticks = _max_time // next_time_unit
-    if (_num_time_ticks <= 2): break
+    if (_num_time_ticks <= 3): break
     time_unit = next_time_unit
 
 time_fmt = ticker.FuncFormatter(lambda ms, x: int(ms / 60))
@@ -86,6 +97,7 @@ ax[1].plot(data['Time'], data['RateS(avg)'], color='C1', linewidth=2)
 ax[1].set_xlabel("Time (min)")
 ax[1].set_ylabel("New Coverage (/sec)")
 ax[1].set_xlim([data['Time'][0], data['Time'][-1]])
+ax[1].set_ylim(bottom=0)
 ax[1].legend(["Inst", "Avg"], loc="upper right")
[…]

### 2024-03-06 lscov/cov-to-fig.py
paper: discussion: quality metric for general fuzzing (revise./cov-to-fig.py lscov.csv) --> replacing 'completeness of targeted fuzzing'

@@ -51,67 +51,96 @@ cov_unit_str = ""
 if (cov_unit_pow10 > 0):
     cov_unit_str = " (x$10^{}$)".format(cov_unit_pow10)
 
-# FIXME: there must be a better algorithm for this kind of stuff.
-time_unit = 1
-_max_time = data['Time'][-1]
-while (True):
-    if (time_unit == 1):
-        next_time_unit = 10
-    elif (time_unit == 10):
-        next_time_unit = 60
-    elif (round(math.log(time_unit // 6, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 2) * 3
-    elif (round(math.log(time_unit // 9, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 3) * 4 
-    elif (round(math.log(time_unit // 12, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 4) * 5
-    elif (round(math.log(time_unit // 15, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 5) * 6 
-    elif (round(math.log(time_unit // 18, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 3) * 4 
-    elif (round(math.log(time_unit // 24, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 4) * 5 
-    elif (round(math.log(time_unit // 30, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 2) * 3
-    elif (round(math.log(time_unit // 45, 10), 3).is_integer()):
-        next_time_unit = (time_unit // 3) * 4 
-    _num_time_ticks = _max_time // next_time_unit
-    if (_num_time_ticks <= 3): break
-    time_unit = next_time_unit
+# Decide time unit.
 
-time_fmt = ticker.FuncFormatter(lambda ms, x: int(ms / 60))
+# FIXME: there must be a better algorithm for this kind of stuff.
+time_unit_in_str = 'sec'
+time_unit_in_fmt = 1
+time_unit_in_sec = 1
+_max_time = data['Time'][-1]
+
+if (_max_time > 4*60*60):
+    time_unit_in_str = 'hr'
+    time_unit_in_fmt = 3600
+elif (_max_time > 4*60):
+    time_unit_in_str = 'min'
+    time_unit_in_fmt = 60
+
+while (True):
[…]

### 2024-03-10 paper/main.tex
paper: discussion: quality metric for general fuzzing

@@
 %
-The legitimacy of logic state coverage hinges on the current conventional
-understanding of interesting program behaviors in \emph{untargeted} fuzzing,
-namely the behaviors with less repetition. However, recent findings 
-\cite{regression,risk,root-causes-age} suggest that various code characteristics
-(e.g., the age of code) make some code likelier to cause bugs,
-which makes the program behaviors executing such a portion of code have a higher
-expectation to reveal unknown abnormal behaviors (i.e., more interesting).
-%
-\emph{Targeted} fuzzing \cite{regression,directed,risk} attempts to capitalize
-the findings by prioritizing such code, while logic state coverage would
-under-estimate their quality by only considering less repetition as more
+Logic state coverage evaluates the quality of \emph{untargeted} fuzzing, where
+the program behaviors with less repetition are generally deemed more
 interesting. 
-
-For a quality metric that encompasses general (i.e., both untargeted and
-targeted) fuzzing, future research needs to address two issues around
-interestingness. First, it should refine the interestingness of program
-behaviors. Not only should it systemize the factors that decide interestingness,
-but also it should assess which factor affects \emph{more} than others by
-\emph{how much}.  Second, it should incorporate such refined interestingness
-into the quality metric. If it would follow the philisophy of logic state
-coverage (i.e., more uninteresting behavior in fewer logic states),
-\emph{grouping} uninteresting branches can be an approach as it makes the
-program behaviors with uninteresting branches occupy fewer logic states.
+%
+However, \emph{targeted} fuzzing
+\cite{aflchurn,chen2020savior,osterlund2020parmesan,lee2024syzrisk} attempts to
+capitalize the recent findings \cite{aflchurn,zhai2022ndss,nikolaos2022longvuln}
+that some code such as recent patches are potentially \emph{more interesting}
+(i.e., likelier to cause abnormal behaviors), which may render logic state
+coverage to under-estimate targeted fuzzing by overlooking potentially
+interesting behaviors.
+
+To devise a quality metric that is also compatible to targeted fuzing, future
+research may need to address two issues revolving around interestingness. First,
+it should accurately describe the interestingness in an unpartial way (i.e., not
+favoring a certain fuzzer or setting). To do so, it should assess which factor
+affects interestingness and how much more than one another. Second, it should
+incorporate such a description into the quality metric. Should it follow the
+philisophy of logic state coverage, grouping uninteresting behaviors may be a
+possible approach to make them less significant.
 

### 2024-06-02 paper/main.tex
paper: discussion: quality metric for general fuzzing
intro, representativeness/normality

@@
 
-\title{A Comparative Quality Metric for Fuzzing with Logic State Coverage}
+\title{A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage}
 \author{
-  {\rm Gwangmu Lee} \\ {EPFL}
+  {\rm Gwangmu Lee} \\ {iss300@gmail.com}
 }
@@
 often leads to indecisive measurements; it is common to see the edge coverage
-comparisons offering little difference (e.g., equally saturated edge coverage in
-hypervisor virtual devices \cite{myung2022mundofuzz,sergej2021nyx}) or
-influenced by initial inputs (e.g., different requirements for initial inputs in
-grammar fuzzing \cite{chen2021polyglot}).
+comparisons offering little difference (e.g., equally saturated edge coverage 
+%in hypervisor virtual devices 
+\cite{myung2022mundofuzz,sergej2021nyx}) or
+influenced by initial inputs (e.g., different requirements for initial inputs 
+%in grammar fuzzing 
+\cite{chen2021polyglot}).
 %, in which cases researchers should resort to another way for demonstrating effectiveness.  
 Furthermore, some experiments yield counter-intuitive results where a code
-coverage increment does not necessarily translate to more discovered bugs so
-well \cite{google-ai}.
-
-The number of discovered bugs, on the other hand, is a direct metric as it
-counts the very objects (i.e., bugs) that fuzzing aims to reveal. However, it is
-commonly known to be heavily sensitive to side factors such as bug
-deduplication, initial inputs, and the implementation details of both the fuzzer
-and the software under test \cite{klees2018evaluating}. It gets worse because
-the number of total bugs is usually only a handful,
+coverage increment does not translate to more discovered bugs so well
+\cite{google-ai}.
+
+The number of discovered bugs, on the other hand, is a much more direct metric
+because it counts the very objects (i.e., bugs) that fuzzing aims to reveal.
+However, it is highly sensitive to side factors such as bug deduplicatation
+method, initial inputs, or the implementation details of both the fuzzer and the
+software under test \cite{klees2018evaluating}. Even worse, the number of total
+bugs is usually only a handful,
 %regardless of the software under test, 
-where unclear factors can introduce a measurement bias that significantly
+making unclear factors easily introduce a measurement bias that significantly
 exaggerates the result in certain software.
@@
 coverage} as a feasible proxy metric of interesting behaviors. A logic state is
-a set of all satisfied branches during one execution, where logic state coverage
-is the \emph{individual count} of all observed distinct logic states during a
-fuzzing campaign. Logic states represent \emph{interesting} behaviors (i.e.,
-relating to unknown abnormal behaviors) in a finer granularity, meaning that
-observing more interesting behaviors is reliably reflected to larger coverage.
+a set of all satisfied branches during one execution, encoding the
+exhibited program behavior without branch repetition information.
+As a consequence, less repetitive (i.e., more \emph{interesting}) program
+behaviors are reflected as more \emph{distinct} logic states. Logic state
+coverage counts all distinct observed logic states during a fuzzing campaign,
+which means that a larger coverage suggests more observed interesting behaviors.
 
@@
   \caption{Example control flow graph and program behaviors. The exceptional
-  condition $e$ is satisfied when $\mathrm{mem}(q)$ is a freed memory. $l(X)$
-  denotes the logic state of a program behavior $X$ (hit count omitted).}
+  condition $e$ is satisfied when the memory pointed by $q$ is a freed
+  memory. $l(X)$ denotes the logic state of a program behavior $X$.}
   % Each region surrounded by dotted lines constitutes one logic state.}
@@
 
-In one logic state, \emph{all} program behaviors are either normal or abnormal
-altogether. 
-%
-This is because normal behaviors trigger \emph{exit branches} before
-reaching program exit points, while abnormal behaviors do not. Since the logic
-states of two behaviors differ by exit branches, they cannot have the same set
-of satisfied branches, hence the same logic state.
+As long as a program does not exhibit an exception at the program exit basic
+block, all program behaviors in one logic state have the same normality,
+namely either normal or abnormal altogether.
+%
+This is because normal behaviors always trigger the \emph{exit branches} that
+lead to the exit blocks, while abnormal behaviors do not. Since the logic
+states of two behaviors are always distinguished by exit branches, they cannot
+have the same set of satisfied branches (i.e., the same logic state).
 
 \autoref{f:local} shows an example program that contains a use-after-free
-exception $e$, which is satisfied when $\mathrm{mem}(q)$ belongs to freed
-memories. Three example program behaviors and their logic states are shown on
-the side. Since normal behaviors (Behaviors A and B) terminate at the program
+exception $e$, which is satisfied when the memory pointed by $q$ belongs to
+freed memories. Three example program behaviors and their logic states are shown
+on the side. Since normal behaviors (Behaviors A and B) terminate at the program
 exit, their logic states contain the exit branch $b_x$ that directly leads to
@@
 
-To devise a quality metric that is also compatible to targeted fuzing, future
+To devise a quality metric that also encompasses targeted fuzing, future
 research may need to address two issues revolving around interestingness. First,

### 2024-06-02 paper/main.tex
sec2

@@
 
-%\pp{Normality of program behaviors}
-%
-Program behaviors can be divided into two classes depending on their
-\emph{normality}: normal and abnormal. Normal program behaviors are determined
-by a regular control flow and terminate at program exit points.  Abnormal
-program behaviors, on the other hand, are terminated unexpectedly by
-exceptions.\footnote{Sanitization can be seen as bringing (potentially) silent
-\emph{unintended} behaviors (e.g., integer-overflow or use-after-free) to the
-\emph{abnormal} territory.}
-
-\pp{Special case: single-thread programs}
-%
-For a single-thread program where every basic block always executes the
-contained instructions atomically, program behaviors are exclusively
-determined by the history of two kinds of conditions: branch and exceptional.
-Branch conditions (or \emph{branches}) decide the regular control flow between
-basic blocks. Exceptional conditions (or \emph{exceptions}), on the other hand,
-interrupt the control flow and abnormally terminate the
+\pp{Program conditions}
+%
+Program conditions are the instructions that affect the control flow and
+transform the program behavior accordingly. They are further
+broken down to two kinds: branch and exceptional.
+Branch conditions (or \emph{branches}) decide the regular control
+flow between basic blocks. Exceptional conditions (or \emph{exceptions}), on the
+other hand, interrupt the control flow and abnormally terminate the
 program.\footnote{C++-style exceptions, despite its name, can be regarded as a
 form of branch conditions as they transfer the control flow to another basic
-block.} Notice that exceptions may be implicit and not specified in the
-program (e.g., $\mathrm{divisor}=0$ in divide-by-zero).
-
-%Notice that exceptions may be implicit, unlike branches that are always explicit
-%in the program; exceptions such as assertions are explicitly specified in
-%the program, but others such as divide-by-zero (i.e., $\mathrm{divisor}=0$) or
-%buffer-overflow (i.e., $\mathrm{offset} \ge \mathrm{size}$) are implicit and
-%only enforced by the system.
+block.} 
+%Notice that exceptions may be implicit and not specified in the program
+%(e.g., $\mathrm{divisor}=0$ in divide-by-zero).
+
+\pp{Normality of program behaviors}
+%
+Program behaviors can be divided into two classes depending on the satisfied
+program conditions: normal and abnormal. Normal program behaviors only satisfy
+regular branches and terminate at program exit points. Abnormal
+program behaviors, on the other hand, satisfy at least one exception and
+terminate at non-exit points. Sanitization
+\cite{yun2016apisan,serebryany2012asan,kasan,ktsan,kubsan,stepanov2015msan,ubsan} can be seen as bringing
+\emph{unintended} behaviors (e.g., integer-overflow or use-after-free) to the
+\emph{abnormal} territory by adding exceptions.
+
+\pp{Uniqueness of program behaviors}
+%
+For a single-thread program, 
+%where every basic block always executes the contained instructions atomically, 
+program behaviors are exclusively determined by the history of program
+conditions. This is because a single-thread program always executes the 
+instructions sequentially until the next program condition, making every
+portion of the instruction stream \emph{implied} by terminating program
+conditions.
 
@@
 exceptions. Then, for a single-thread program, there exists a function
-$f(\mathcal{T}_b, \mathcal{T}_e) = h$ that one-to-one maps a pair
+$f(\mathcal{T}_b, \mathcal{T}_e) = h$ that uniquely maps a pair
 $(\mathcal{T}_b, \mathcal{T}_e)$ to a certain program behavior $h$.
@@
 
-\pp{Completeness of untargeted fuzzing}
+\pp{Quality of untargeted fuzzing}
 %
@@
 interesting behaviors in the program behavior space, the portion of such 
-behaviors in the space directly indicates the \emph{completeness} of the
+behaviors in the space directly indicates the \emph{quality} of the
 procedure: the more it checks such behaviors, the less the unknown
@@
 
-Based on this, we can define the \emph{relative completeness} between
+Based on this, we can define the \emph{comparative quality} between
 different untargeted fuzzing techniques as follows: given the same amount of
 time and computing resource, \textbf{how many more interesting program behaviors
-has it observed than others?} We argue that relative completeness is a
-\emph{strong quality metric} for untargeted fuzzing as it closely indicates how
-much more a fuzzer reduces the expectation of unknown abnormal behaviors than
-others.
+can it observe than others?} We argue that this is a \emph{strong quality
+metric} for untargeted fuzzing as it directly compares the reduced expectation
+of unknown abnormal behaviors.
 

### 2024-06-02 paper/main.tex
checkpt

@@
 
-In theory, relative completeness can be naively measured by counting distinctive
-program behaviors. However, this naive approach is infeasible as fuzzing
-produces hundreds of arbitrarily long instruction streams \emph{every second}.
-%
-In this section, we propose \emph{logic state coverage} as a proxy of relative
-completeness that indirectly counts interesting program behaviors.
+In theory, interesting behaviors can be naively counted by investigating
+every program behavior. However, this naive approach is infeasible as
+fuzzing produces hundreds of arbitrarily long instruction streams \emph{every
+second}.
+%
+In this section, we propose \emph{logic state coverage} as an indirect proxy of
+counting interesting behaviors.
 

### 2024-06-03 paper/main.tex
sec4.2, discussion

@@
 %
-In this section, we propose \emph{logic state coverage} as an indirect proxy of
+In this section, we propose \emph{logic state coverage} as an indirean indirectt proxy of
 counting interesting behaviors.
@@
 
-Logic states distinguish the program behaviors with less branch repetitions in a
-finer granularity, resulting in a higher number of covered logic states (i.e.,
-larger coverage) as the observed program behaviors are more interesting.
+Logic states coalesce the program behaviors in a fewer logic states as the
+behaviors contain more branch repetitions, resulting in a smaller (or larger)
+logic state coverage as it observes more uninteresting (or interesting) program
+behaviors.
 
@@
 
-\autoref{f:repr} shows an example control-flow graph and its logic states
-(colored boxes) that the program behaviors with different sets of satisfied
-branches belong to.
+\autoref{f:repr} shows an example control-flow graph and its logic space,
+gridded up by the different hit counts of the branch $b_1$, $b_2$, and $b_3$.
 %, where $m(b)$ denotes the hit count of a branch $b$. 
-For example, a program behavior that does not hit any colored branches (i.e.,
-$m(b_1)=m(b_2)=m(b_3)=0$) belongs to \cbox{black}, and a program
-behavior that only hits one of them (e.g., $m(b_i)>1$ and $m(b_j)=0$ for $i \in
-\{1,2,3\}$ and $j \ne i$) belongs to the logic state of the corresponding color
-(\cbox{red}, \cbox{green}, and \cbox{blue}).
-%The dotted lines demarcate whether the corresponding branch is hit or not, which
-%also corresponds to the presence of the branch in a logic state.
-%The surrounded region has the same set of satisfied branches, constituting
-%\emph{one logic state}.
-
-The figure shows the increasing size of logic states as their constituent
-program behaviors involve more repetitive branches. For example, a program
-behavior with two repetitive branches (i.e., $b_1$ and $b_2$, $b_2$ and $b_3$,
-or $b_1$ and $b_3$) falls into a larger logic state (e.g., \cbox{yellow},
-\cbox{cyan}, and \cbox{magenta}), and a behavior with three repetitive branches
-(i.e., all $b_1$, $b_2$, and $b_3$) falls into the largest logic state (i.e.,
-\cbox{gray}).
-%
-This results in observing repetitive (i.e., less interesting) program states
-represented by fewer logic states, leading to smaller logic state
-coverage.\footnote{It is worth noting that a coordinate in the grid does
-\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
-represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
-However, it does not affect the relative size of visualized logic states because
-a coordinate only has more program behaviors as it gets further from the
-origin.}
+Each colored box represents one logic state that includes all program
+behaviors that exhibit the branch hit counts at the enclosed grid points.
+For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
+(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) falls into the \cbox{black} logic state, while
+all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
+$m(b_2)=m(b_3)=0$) fall into the \cbox{red} logic state.
+%, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
+%$m(b_1)>1$, $m(b_2)>1$, and $m(b_3)=0$) fall into the \cbox{cyan} logic state.
+
+The colored boxes in \autoref{f:repr} suggest the increasing size of logic
+states as their constituent program behaviors involve more repetitive branches.
+To be specific, a logic state covers a progressively larger volume in the logic
+space (i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
+$\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$
+\cbox{gray}) as it contains more repetitive branches (i.e., 0 $\rightarrow$ 1
+$\rightarrow$ 2 $\rightarrow$ 3 repetitive branches). 
+%
+This results in repetitive (i.e., less interesting) program states coalesced to
+fewer logic states, suppressing logic state coverage as it observes
+uninteresting behaviors more.
+%\footnote{It is worth noting that a coordinate in the grid does
+%\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
+%represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
+%However, it does not affect the relative size of visualized logic states because
+%a coordinate only has more program behaviors as it gets further from the
+%origin.}
 
@@
 
-As long as a program does not exhibit an exception at the program exit basic
-block, all program behaviors in one logic state have the same normality,
-namely either normal or abnormal altogether.
-%
-This is because normal behaviors always trigger the \emph{exit branches} that
-lead to the exit blocks, while abnormal behaviors do not. Since the logic
+Given that a program does not exhibit an exception exactly at the program exit
+point, all program behaviors in one logic state have the same normality, namely
+either normal or abnormal altogether.
+%
+This is because normal behaviors trigger the \emph{exit branches} that
+lead to the exit point, while abnormal behaviors do not. Since the logic
 states of two behaviors are always distinguished by exit branches, they cannot
@@
 
-\pp{Absolute completeness of untargeted fuzzing}
-%
-Unlike relative completeness, it is difficult to measure the \emph{absolute}
-completeness of untargeted fuzzing because the total number of program behaviors
-is unknown: if it can be known, then we would already know which abnormal
-behaviors are possible, precluding the necessity of fuzzing in the first place.
+\pp{Completeness of untargeted fuzzing}
+%
+Unlike comparative quality that only requires to compare the number of observed
+distinct program behaviors, it is difficult to measure the absolute
+\emph{completeness} of untargeted fuzzing that requires to measure how much a
+program has been completely verified. This is because the total number of
+program behaviors is unknown: if it can be known, then we would already know
+which abnormal behaviors are possible, precluding the necessity of fuzzing in
+the first place.
 
@@
 However, it would pose a potential problem that the estimated 100\% completeness
-does not necessarily mean the actual 100\% completeness, which would defeat the
-major benefit of absolute completeness.
+does not necessarily mean the actual 100\% completeness, which may compromise
+the very purpose of measuring absolute completeness.
 
@@
 properties of a logic space (i.e., interestingness and normality).
-An alternative proxy of relative completeness may be proposed by either
+An alternative proxy of comparative quality may be proposed by either
 extending logic state coverage or devising yet another coverage metric.
@@
 research may need to address two issues revolving around interestingness. First,
-it should accurately describe the interestingness in an unpartial way (i.e., not
+it should accurately describe the interestingness in an impartial way (i.e., not
 favoring a certain fuzzer or setting). To do so, it should assess which factor
@@
 incorporate such a description into the quality metric. Should it follow the
-philisophy of logic state coverage, grouping uninteresting behaviors may be a
+philosophy of logic state coverage, grouping uninteresting behaviors may be a
 possible approach to make them less significant.

### 2024-06-03 paper/main.tex
sec4.2, discussion

@@
 \autoref{f:repr} shows an example control-flow graph and its logic space,
-gridded up by the different hit counts of the branch $b_1$, $b_2$, and $b_3$.
+gridded up by the different hit counts $m(b)$ of the branch $b_1$, $b_2$, and $b_3$.
 %, where $m(b)$ denotes the hit count of a branch $b$. 

### 2024-06-03 paper/main.tex
sec4.2, discussion

@@
 Logic states coalesce the program behaviors in a fewer logic states as the
-behaviors contain more branch repetitions, resulting in a smaller (or larger)
-logic state coverage as it observes more uninteresting (or interesting) program
+behaviors contain more branch repetitions, resulting in a smaller (larger)
+logic state coverage as it observes more uninteresting (interesting) program
 behaviors.
@@
 %
-This results in repetitive (i.e., less interesting) program states coalesced to
-fewer logic states, suppressing logic state coverage as it observes
-uninteresting behaviors more.
+This results in repetitive (i.e., uninteresting) program states packed
+to fewer logic states, suppressing (boosting) logic state coverage as it observes more
+uninteresting (interesting) behaviors.
 %\footnote{It is worth noting that a coordinate in the grid does

### 2024-06-03 paper/main.tex
sec4.2, discussion

@@
 Logic states coalesce the program behaviors in a fewer logic states as the
-behaviors contain more branch repetitions, resulting in a smaller (larger)
+behaviors contain more branch repetitions, resulting in smaller (larger)
 logic state coverage as it observes more uninteresting (interesting) program

### 2024-06-06 paper/main.tex
checkpt

@@
 %
-However, the common usage of corpus minimization \cite{todo} and branch hit
-count buckets \cite{todo} in untargeted fuzzing suggests that a program behavior
+However, the common usage of corpus minimization
+\cite{libfuzzer,efffuzz,herrera2021seedsel,herrera2021seedsel} and branch hit
+count buckets \cite{afl,libfuzzer} in untargeted fuzzing suggests that a program behavior
 is less likely to be \emph{unknown abnormal} (i.e., less interesting) if its
@@
 
-Logic states coalesce the program behaviors in a fewer logic states as the
-behaviors contain more branch repetitions, resulting in smaller (larger)
-logic state coverage as it observes more uninteresting (interesting) program
+Logic states coalesce less interesting program behaviors that exhibit more
+branch repetitions in a fewer logic states, resulting in smaller (larger) logic
+state coverage as it observes more uninteresting (interesting) program
 behaviors.
@@
 states as their constituent program behaviors involve more repetitive branches.
-To be specific, a logic state covers a progressively larger volume in the logic
-space (i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
+To be specific, a logic state covers a progressively larger volume 
+%in the logic space 
+(i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
 $\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$

### 2024-06-06 paper/main.tex
checkpt

@@
 %, where $m(b)$ denotes the hit count of a branch $b$. 
-Each colored box represents one logic state that includes all program
-behaviors that exhibit the branch hit counts at the enclosed grid points.
+Each colored box represents one logic state, which includes all program
+behaviors that fall into the box.
 For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
-(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) falls into the \cbox{black} logic state, while
+(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) belongs to the \cbox{black} logic state, while
 all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
-$m(b_2)=m(b_3)=0$) fall into the \cbox{red} logic state.
+$m(b_2)=m(b_3)=0$) fall into \cbox{red}.
 %, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
@@
 To be specific, a logic state covers a progressively larger volume 
-%in the logic space 
+in the logic space 
 (i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}

### 2024-08-18 paper/main.tex
checkpt
Adding the mention about the preliminary evaluation

@@
 
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.8\textwidth]{images/aflpp-xmllint-epfl.pdf}
+  \caption{24-hour fuzzing campaign of XMLLint on AFL++. (Ins: instantaneous,
+    Avg: average)}
+  \label{f:aflpp-xmllint-epfl}
+\end{figure*}
+
 \section{Experiment}
 
-\subsection{Experiment Setup}
-
-\subsection{Measurement Overheads}
-
-\subsection{General-purpose Fuzzing}
-
-\subsection{Hypervisor Fuzzing}
-
+\subsection{Preliminary Result}
+
+\autoref{f:aflpp-xmllint-epfl} shows the preliminary evaluation result
+using XMLLint and AFL++. The evaluation was done on a Intel Core i7-8665U CPU
+machine with 16 GB of memory. The logic state coverage (left) shows the covered
+distinctive logic states over time. The new coverage per second (middle) shows
+the number of newly discovered logic states per time, while the new coverage per
+execution (right) shows the percentage of executions that discovered new logic
+states per execution. \textsc{Avg} indicates the average new coverage per second
+or per execution, and \textsc{Ins} indicates the instantaneous new coverage
+during the last 10-second measurement frame.
+
+The logic state coverage increases steadily over time, but it gradually slows
+down toward the 24-hour mark. This trend is also reflected in the new coverage
+plot, where the average new coverage slowly decreases to a steady point toward
+the end of the fuzzing campaign.
+
+The sporadic peaks in the instantaneous new coverage plot (\textsc{Ins}) are
+mainly due to the favorable in-flight seeds at the moment, which allowed AFL++
+to execute XMLLint quicker. This results in more peaks in the "per second" plot
+than in the "per execution" plot, where the discovered new logic states were
+bigger than the average but the percentage of new logic states per execution
+remained low.
+
+%\subsection{Experiment Plan}
+%
+%\subsection{Measurement Overheads}
+%\subsection{General-purpose Fuzzing}
+%\subsection{Hypervisor Fuzzing}
   % same cov: what can we learn more from logic state cov?
-
-\subsection{Grammar Fuzzing}
-
+%\subsection{Grammar Fuzzing}
   % init corpus cov: what can we learn more from logic state cov?

### 2024-08-18 lscov/cov-to-fig.py
cov-to-fig.py: pdf creation (commented)

@@ -32,7 +32,7 @@ for raw_datum in raw_data:
 
 # Draw figures.
 
-fig, ax = plt.subplots(ncols=3, figsize=(10, 3), layout="tight")
+fig, ax = plt.subplots(ncols=3, figsize=(10, 2.6), layout="tight")
 
 ax[0].set_box_aspect(0.75)
 ax[1].set_box_aspect(0.75)
@@ -144,5 +144,5 @@ ax[2].xaxis.set_major_locator(ticker.MultipleLocator(time_unit_in_sec))
 
 # Save.
 
+#plt.savefig('lscov.pdf')
 plt.show()
-#plt.savefig('lscov.png')

### 2024-09-15 paper/main.tex
Add evaluation plan

@@
   count observed interesting behaviors. A logic state is a set of satisfied
-  branches during one execution, where logic state coverage is the count of
+  branches during one execution, where its coverage is the count of
   \emph{individual} observed logic states during a fuzzing campaign. A logic
@@
   % 
-  We implemented logic state coverage using a bloom filter and reevaluated
-  \textsc{FuzzBench} and indecisive-to-subjective fuzzer comparisons in
-  hypervisor and grammar fuzzing. 
+  We implemented logic state coverage using a bloom filter and performed a
+  preliminary evaluation with AFL++ and XMLLint.
+  % reevaluated \textsc{FuzzBench} and indecisive-to-subjective fuzzer
+  % comparisons in hypervisor and grammar fuzzing. 
   % TODO: (The result summary will come here)
@@
 
-\section{Experiment}
+\section{Evaluation}
 
@@
 \autoref{f:aflpp-xmllint-epfl} shows the preliminary evaluation result
-using XMLLint and AFL++. The evaluation was done on a Intel Core i7-8665U CPU
-machine with 16 GB of memory. The logic state coverage (left) shows the covered
-distinctive logic states over time. The new coverage per second (middle) shows
-the number of newly discovered logic states per time, while the new coverage per
-execution (right) shows the percentage of executions that discovered new logic
-states per execution. \textsc{Avg} indicates the average new coverage per second
-or per execution, and \textsc{Ins} indicates the instantaneous new coverage
-during the last 10-second measurement frame.
-
-The logic state coverage increases steadily over time, but it gradually slows
+using XMLLint and AFL++. The evaluation was done on an Intel Core i7-8665U CPU
+machine with 16 GB of memory. The logic state coverage (left) shows the
+distinctive logic states covered over time. The new coverage per second (middle)
+shows the number of newly discovered logic states per time, while the new
+coverage per execution (right) shows the percentage of executions that
+discovered new logic states per execution. \textsc{Avg} indicates the average
+new coverage per second or per execution, and \textsc{Ins} indicates the
+instantaneous new coverage during the last 10-second measurement frame.
+
+The logic state coverage increases steadily over time but gradually slows
 down toward the 24-hour mark. This trend is also reflected in the new coverage
@@
 the end of the fuzzing campaign.
-
-The sporadic peaks in the instantaneous new coverage plot (\textsc{Ins}) are
-mainly due to the favorable in-flight seeds at the moment, which allowed AFL++
-to execute XMLLint quicker. This results in more peaks in the "per second" plot
-than in the "per execution" plot, where the discovered new logic states were
-bigger than the average but the percentage of new logic states per execution
-remained low.
-
-%\subsection{Experiment Plan}
-%
+%
+Notice that the sporadic spikes in the instantaneous new coverage (\textsc{Ins})
+are more in the per-second plot than in the per-execution plot, suggesting that
+these sudden new coverage surges were primarily caused by quicker execution.
+
+\subsection{Research Questions}
+
+Some of the prime research questions that further evaluation should answer
+include the following.
+
+\begin{itemize}
+  \item \textbf{RQ1} Can logic state coverage be implemented with all
+    requirements in \autoref{s:measure:req} satisfied?
+  \item \textbf{RQ2} How does logic state coverage measure the comparative
+    quality of popular untargeted fuzzers?
+  \item \textbf{RQ3} Can logic state coverage distinguish the quality of the
+    fuzzers indistinguishable from conventional edge coverage?
+\end{itemize}
+
+For \textbf{RQ1}, the evaluation may evaluate the computation and memory
+overhead added by the logic state coverage measurement. It should not perturb
+the execution speed of measured fuzzers to minimize the measurement bias. For
+\textbf{RQ2}, the evaluation may compare the logic state coverage of popular
+untargeted fuzzers \cite{afl,fioraldi2020aflpp,libfuzzer,honggfuzz} with a
+set of standard fuzzing targets (e.g., FuzzBench \cite{metzman2021fuzzbench}).
+For \textbf{RQ3}, the evaluation may compare the logic state coverage of
+specialized fuzzers (e.g., hypervisor fuzzers
+\cite{liu2023videzzo,myung2022mundofuzz,sergej2021nyx,schumilo2020hypercube} and
+grammar fuzzers
+\cite{wang2023fuzzjit,wu2023jitfuzz,gross2023fuzzilli,srivastava2021gramatron,chen2021polyglot}),
+whose quality has not been well-distinguished by a conventional edge coverage
+metric.
+
 %\subsection{Measurement Overheads}

### 2024-09-18 paper/main.tex
Draft for arXiv

@@
 In this section, we first present the design overview (\autoref{s:design:over})
-and elaborate on details (\autoref{s:design:rec} and \ref{s:design:count}).
+and elaborate on details (\autoref{s:design:rec} and
+\ref{s:design:count}). The implementation in progress can be found at
+\url{https://github.com/gwangmu/LogicStateCoverage}.
 
@@
 
+Recording a logic state is equivalent to tracing executed edges in conventional
+edge coverage. Specifically, a taken edge is calculated by combining the
+hashes of two consecutively executed basic blocks, which is then added to the
+logic state of the current execution. Notice that a logic state is \textit{per
+execution} and is not merged throughout multiple executions as in edge
+coverage. We implemented logic state recoding based on the LLVM pass for
+\cc{afl-clang-fast} \cite{afl}.
+
 \subsection{Updating Logic State Coverage}
@@
 
-\subsection{Counting Logic State Coverage}
-\label{s:design:count}
+The recorded logic state is updated to the bloom filter at the end of every
+execution. In particular, a number of hashes are calculated from the entire
+logic state (i.e., \cc{A}, \cc{B}, \cc{C}, and \cc{D} in \autoref{f:design}) and
+are used as bloom filter indices to be set. We used MurMurHash3
+\cite{murmurhash3} to hash a logic state.
 
@@
 \end{figure*}
+
+\subsection{Counting Logic State Coverage}
+\label{s:design:count}
+
+Finally, the logic state coverage of the fuzzing campaign is measured by
+periodically reading off the bloom filter, where the number of 1s in the filter
+is fed to \autoref{e:count} to count the distinctive number of observed logic
+states. We implemented logic state coverage measurement as a separate process,
+which a measurer should launch before starting a fuzzing campaign.
 
@@
     quality of popular untargeted fuzzers?
-  \item \textbf{RQ3} Can logic state coverage distinguish the quality of the
-    fuzzers indistinguishable from conventional edge coverage?
+  \item \textbf{RQ3} Can logic state coverage distinguish the fuzzers
+    indistinguishable from conventional edge coverage?
 \end{itemize}
@@
 However, it would pose a potential problem that the estimated 100\% completeness
-does not necessarily mean the actual 100\% completeness, which may compromise
-the very purpose of measuring absolute completeness.
+does not necessarily mean the actual 100\% completeness, defeating the very
+purpose of measuring \textit{completeness}.
 
@@
 
+While fuzzing is widely accepted as an efficient program testing technique, 
+it still lacks the metric to comparatively measure the quality of various
+designs and implementations. To establish a reliable quality metric, we
+note that the more interesting behaviors a fuzzer has observed, the stronger
+guarantee it can provide about the absence of unknown abnormal behaviors. Based
+on this, we propose \emph{logic state coverage} as a proxy metric to count
+observed interesting behaviors. A logic state is a set of satisfied branches
+during one execution, where its coverage is the count of \emph{individual}
+observed logic states during a fuzzing campaign. We implemented logic state
+coverage using a bloom filter and performed a preliminary evaluation with AFL++
+and XMLLint.
+
 %-------------------------------------------------------------------------------

### 2024-09-18 paper/images/repr-grid.py
Separate paper to another repo

@@ -1,58 +1,0 @@
-#!/usr/bin/python3
-
-import matplotlib.pyplot as plt
-import numpy as np
-
-AXIS_MAX=7
-
-fig = plt.figure(figsize=(5,4.9))
-ax = fig.add_subplot(projection='3d')
-
-vols = {}
-colors = {}
-for h1, p1, o1, c1 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (1, 0, 0))]:
-    for h2, p2, o2, c2 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (0, 1, 0))]:
-        for h3, p3, o3, c3 in [(0, 0, 1, (0, 0, 0)), (1, 1, AXIS_MAX-1, (0, 0, 1))]:
-            vols[h1, h2, h3] = [*(p1, p2, p3), *(o1, o2, o3)]
-            colors[h1, h2, h3] = tuple(map(sum, zip(c1, c2, c3))) 
-
-ax.bar3d(*vols[0, 0, 0], color=(*colors[0, 0, 0], 0.6), linewidth=2, edgecolor=(1, 1, 1, 0.3))
-for key in [(1, 0, 0), (0, 1, 0), (0, 0, 1)]:
-    ax.bar3d(*vols[key], color=(*colors[key], 0.45), linewidth=2, edgecolor=(1, 1, 1, 0.3))
-for key in [(1, 1, 0), (0, 1, 1), (1, 0, 1)]:
-    ax.bar3d(*vols[key], color=(*colors[key], 0.25), linewidth=2, edgecolor=(1, 1, 1, 0.3))
-ax.bar3d(*vols[1, 1, 1], color=(*colors[1, 1, 1], 0.25), linewidth=2, edgecolor=(1, 1, 1, 0.3))
-
-ax.set_aspect('equal', 'box')
-
-ax.xaxis.line.set_color((0.9, 0.3, 0.3))
-ax.yaxis.line.set_color((0.3, 0.9, 0.3))
-ax.zaxis.line.set_color((0.3, 0.3, 0.9))
-ax.xaxis.line.set_linewidth(5)
-ax.yaxis.line.set_linewidth(5)
-ax.zaxis.line.set_linewidth(5)
-ax.set_xlabel("$m(b_1)$", fontsize=15)
-ax.set_ylabel("$m(b_2)$", fontsize=15)
[…]

### 2024-09-18 setup.sh

@@ -14,3 +14,7 @@ wget $LLVM_URL && \
   mkdir llvm && \
   tar -xvf $LLVM_TAR_NAME -C llvm --strip-component 1 && \
   rm $LLVM_TAR_NAME
+
+# Install some dependencies
+
+sudo apt install cmake
